### 2012-03-14 paper.tex
Adapted the template from RevSciIntr to a compileable document

%% ****** Start of file aiptemplate.tex ****** %
%%
%%   This file is part of the files in the distribution of AIP substyles for REVTeX4.
%%   Version 4.1 of 9 October 2009.
%%
%
% This is a template for producing documents for use with 
% the REVTEX 4.1 document class and the AIP substyles.
% 
% Copy this file to another name and then work on that file.
% That way, you always have this original template file to use.

\documentclass[aip,rsi,graphicx]{revtex4-1}
%\documentclass[aip,reprint]{revtex4-1}

%\draft % marks overfull lines with a black rule on the right

\begin{document}

% Use the \preprint command to place your local institutional report number 
% on the title page in preprint mode.
% Multiple \preprint commands are allowed.
%\preprint{}

\title{High Resolution Time of Flight Mass Spectrometer for Measuring Products in Heterogenous Catalysis in Higly Sensitive Microreactors} %Title of paper

% repeat the \author .. \affiliation  etc. as needed
% \email, \thanks, \homepage, \altaffiliation all apply to the current author.
% Explanatory text should go in the []'s, 
% actual e-mail address or url should go in the {}'s for \email and \homepage.
% Please use the appropriate macro for the type of information

% \affiliation command applies to all authors since the last \affiliation command. 
% The \affiliation command should follow the other information.

\author{T. Andersen}
\author{R. Jensen}
\author{....}
\affiliation{CINF, Department of Physics...}
\author{O. Hansen}
\affiliation{CINF, Department of Micro- and Nanotechnology}
\author{I. Chorkendorff}
\email[]{ibchork@fysik.dtu.dk}
\affiliation{CINF, Department of Physics...}
%\homepage[]{Your web page}
%\thanks{}
%\altaffiliation{}
%\affiliation{}

% Collaboration name, if desired (requires use of superscriptaddress option in \documentclass). 
% \noaffiliation is required (may also be used with the \author command).
%\collaboration{}
%\noaffiliation

\date{\today}

\begin{abstract}
We demonstrate that high resolution time of flight mass spectrometry can be successfully applied to detect gas-phase product in hetrogeneous catalysis. Combining the instrument with the highly sensitive microreactors opens the possibility to measure on system that are otherwise difficult due to ....
\end{abstract}

\pacs{}% insert suggested PACS numbers in braces on next line

\maketitle %\maketitle must follow title, authors, abstract and \pacs

% Body of paper goes here. Use proper sectioning commands. 
% References should be done using the \cite, \ref, and \label commands
\section{Introduction}
Ever since, yada yada... \cite{WILEY1955} ...yada yada.....

\section{Experimental Setup}
%\label{}
\subsection{Microreactors}
%\subsubsection{}
\subsection{Time Of Flight Mass Spectrometer}

\section{Results}

\section{Conclusion}

% If in two-column mode, this environment will change to single-column format so that long equations can be displayed. 
% Use only when necessary.
%\begin{widetext}
%$$\mbox{put long equation here}$$
%\end{widetext}

% Figures should be put into the text as floats. 
% Use the graphics or graphicx packages (distributed with LaTeX2e).
% See the LaTeX Graphics Companion by Michel Goosens, Sebastian Rahtz, and Frank Mittelbach for examples. 
%
% Here is an example of the general form of a figure:
% Fill in the caption in the braces of the \caption{} command. 
% Put the label that you will use with \ref{} command in the braces of the \label{} command.
%
% \begin{figure}
% \includegraphics{}%
% \caption{\label{}}%
% \end{figure}

% Tables may be be put in the text as floats.
% Here is an example of the general form of a table:
% Fill in the caption in the braces of the \caption{} command. Put the label
% that you will use with \ref{} command in the braces of the \label{} command.
% Insert the column specifiers (l, r, c, d, etc.) in the empty braces of the
% \begin{tabular}{} command.
%
% \begin{table}
% \caption{\label{} }
% \begin{tabular}{}
% \end{tabular}
% \end{table}

% If you have acknowledgments, this puts in the proper section head.
%\begin{acknowledgments}
% Put your acknowledgments here.
%\end{acknowledgments}

% Create the reference section using BibTeX:
\bibliographystyle{abbrv}
%\bibliographystyle{alpha}
%\bibliographystyle{plain}
\bibliography{literature}

\end{document}
%
% ****** End of file aiptemplate.tex ******

### 2012-03-14 python_figures/tof_raw.py
Started figure showing raw data of methanol + air system

@@ -1,0 +1,92 @@
+import matplotlib
+#matplotlib.use('svg')
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+import matplotlib.gridspec as gridspec
+import numpy as np
+import MySQLdb
+
+matplotlib.rc('text',usetex=True) # Magic fix for the font warnings
+
+try:
+    db = MySQLdb.connect(host="servcinf", user="cinf_reader",passwd = "cinf_reader", db = "cinfdata")
+except:
+    db = MySQLdb.connect(host="127.0.0.1", port=9995, user="cinf_reader",passwd = "cinf_reader", db = "cinfdata")
+
+
+cursor = db.cursor()
+
+data = {}
+#Methanol + oxygen
+cursor.execute("SELECT x*1000000,y*1000 FROM xy_values_tof where measurement = 170")
+data['ch'] = np.array(cursor.fetchall())
+
+axis_array = []
+fig = plt.figure()
+fig.subplots_adjust(bottom=0.15) # Make room for x-label
+
+LINEWIDTH = 0.5
+
+ratio = 0.4                     # This figure should be very wide to span two columns
+fig_width = 17
+fig_width = fig_width /2.54     # width in cm converted to inches
+fig_height = fig_width*ratio
+fig.set_size_inches(fig_width,fig_height)
+
+gs = gridspec.GridSpec(2, 3)
+gs.update(wspace=0.2,hspace=0.2)
+
+axis = plt.subplot(gs[0, :])
+
+axis.plot(data['ch'][:,0], data['ch'][:,1], 'r-',linewidth=LINEWIDTH)
+axis.set_ylim(0,20)
+axis.set_xlim(0,20)
+
+p = axis.axvspan(0, 1, facecolor='#26aaf7', alpha=0.25)
+p = axis.axvspan(12, 13, facecolor='#b6fa77', alpha=0.25)
+p = axis.axvspan(16.9, 17, facecolor='#4599a7', alpha=0.25)
+
+axis.tick_params(direction='in', length=6, width=1, colors='k',labelsize=8,axis='both',pad=3)
+axis.set_ylabel('Response / mV', fontsize=8)
+#axis.set_xlabel('Flight Time / $\mu$s', fontsize=8)
+axis.set_xlabel('')
+
+
+
+axis = plt.subplot(gs[1,0])
[…]

### 2012-03-14 python_figures/ammonia_OH_gauss_fit.py
Started to adapt the rather large TOF-processing program to the much simpler case of making a figure showing a gauss-double fit of OH and NH3

@@ -1,0 +1,108 @@
+import matplotlib
+from scipy import optimize
+import math
+#matplotlib.use('svg')
+#matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+import numpy as np
+import MySQLdb
+import sys
+
+matplotlib.rc('text',usetex=True) # Magic fix for the font warnings
+
+try:
+    db = MySQLdb.connect(host="servcinf", user="cinf_reader",passwd = "cinf_reader", db = "cinfdata")
+except:
+    db = MySQLdb.connect(host="127.0.0.1", port=9995, user="cinf_reader",passwd = "cinf_reader", db = "cinfdata")
+
+
+cursor = db.cursor()
+
+#Relevant time, OH: 12.418, NH3: 12.427
+data = {}
+cursor.execute("SELECT x*1000000,y*1000 FROM xy_values_tof where measurement = 245")
+data['tof'] = np.array(cursor.fetchall())
+
+masses = []
+masses.append(['OH',12.418,6])
+masses.append(['NH3',12.427,6])
+
+
+for mass in masses:
+    i = i + 1
+    axis = pdffig.add_subplot(4,3,i)
+    center = (int)(mass[1] * 2000) ## Notice... 
+    center_mass = mass[1]
+    Start = center -40 #Display range
+    End = center + 40
+    start = center - mass[2] #Fitting range
+    end = center + mass[2]
+
+    offset = min(Data[Start:End,1])
+    x_values = Data[start:end,0]
+    y_values = Data[start:end,1]-offset
+    X_values = Data[Start:End,0]
+    Y_values = Data[Start:End,1]-offset
+    
+    # Fit the first set
+    fitfunc = lambda p, x: p[0]*math.e**(-1*((x-center_mass-p[2])**2)/p[1])       # Target function
+    errfunc = lambda p, x, y: fitfunc(p, x) - y # Distance to the target function
+    p0 = [50,0.00001,0] # Initial guess for the parameters
+    p1, success = optimize.leastsq(errfunc, p0[:], args=(x_values, y_values),maxfev=1000)        
+
+    if (success > 4) or p1[1]>0.01:
+        p0 = [5,0.00001,0]
+        p1, success = optimize.leastsq(errfunc, p0[:], args=(x_values[2:5], y_values[2:5]))
+   
[…]

### 2012-03-14 paper_styleless.tex
Initial writing on the article

\documentclass[12pt]{article}

\title{High Resolution Time of Flight Mass Spectrometer for Measuring Products in Heterogeneous Catalysis in Highly Sensitive Microreactors}
\author{Thomas, Robert, etc.}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
We demonstrate that high resolution time of flight mass spectrometry can be successfully applied to detect gas-phase product in heterogeneous catalysis. Combining the instrument with the highly sensitive microreactors opens the possibility to measure on system that are otherwise difficult due to ....
\end{abstract}

\section{Introduction}
Something about the relevance of this system. Catalysis is interesting because... Typical problems with QMS approach.

\section{System design}
The system consists of a TOF, microreactor and gas handling. Complete system suitable for measurements of small amounts of catalyst with high sensitivity.

\subsection{Microreactor and gas handling}

\subsubsection{Gas handling}
Something about the gas inlet...

\subsubsection{The microreactor platform}
A microreactor platform is used for testing catalyst with high sensitivity. The microreactor is fabricated in silicon and measures 20x15 mm. The reactor consists of two gas inlets, an outlet, a reactor volume and a capillary used for probing the gas from the reactor volume. The reactor volume is 3 $\mu$m deep and 1 cm in diameter resulting in a 240 nL volume. The two gas inlets are combined on the chip where the gases mix by diffusion. The capillary is designed such that approximately $10^{15}$ molecules/s is probed from the reactor volume. Any surplus of gas from the two inlets that does not enter the reactor volume is directed through the outlet into a turbo pump. The design ensures that all molecules entering the reactor volume hence exposed to the catalyst under investigation is detected giving the system high sensitivity.

\subsection{Time of flight}

\subsubsection{Ionization of gas}

\section{Test system}
Ammonia oxidation

\section{Summary}

\section{Acknowledgements}

\end{document}

### 2012-03-15 paper_styleless.tex
Wrote some more on the experimental section

@@
 \documentclass[12pt]{article}
+\usepackage{graphicx}
+\usepackage{caption}
 
@@
 \section{System design}
-The system consists of a TOF, microreactor and gas handling. Complete system suitable for measurements of small amounts of catalyst with high sensitivity.
+The complete system enables high sensitivity reactivity measurements of the catalyst under investigation combined with high resolution mass spectrometry.
+The catalyst under investigation is deposited in a microcreactor from where the products are detected with time of flight mass spectrometry.
+A schematic of the entire setup is shown in Figure \ref{fig:TOF_microreactor}
+\begin{center}
+	\includegraphics[scale=0.60]{TOF_microreactor.png}
+	\captionof{figure}{Schematic of the total system (not to scale)}
+	\label{fig:TOF_microreactor}
+\end{center}
 
@@
 
-\subsubsection{Gas handling}
-Something about the gas inlet...
-
 \subsubsection{The microreactor platform}
-A microreactor platform is used for testing catalyst with high sensitivity.
-The microreactor is fabricated in silicon and measures 20x15 mm.
-The reactor consists of two gas inlets, an outlet, a reactor volume and a capillary used for probing the gas from the reactor volume.
-The reactor volume is 3 $\mu$m deep and 1 cm in diameter resulting in a 240 nL volume.
-The two gas inlets are combined on the chip where the gases mix by diffusion.
-The capillary is designed such that approximately $10^{15}$ molecules/s is probed from the reactor volume.
+Catalysts testing were performed in a microreactor platform \cite{Henriksen2009}.
+The microreactors are fabricated in silicon and measures 20x15\,mm.
+The reactor consists of two gas inlets, a gas outlet, a reactor volume and a capillary used for probing the gas from the reactor volume.
+The reactor volume is 3\,$\mu$m deep and 1 cm in diameter resulting in a 240\,nL volume.
+The two gas inlets are combined on the chip where the inlet gases mix by diffusion.
+The capillary is designed such that approximately $3\cdot10^{14}$\,molecules$\cdot$s$^{-1}$ is probed from the reactor volume.
 Any surplus of gas from the two inlets that does not enter the reactor volume is directed through the outlet into a turbo pump.
@@
 
+The microreactor is heated by joule heating of a 50 nm platinum strip evaporated through a shadow mask on the backside of the chip.
+The heating element is contacted by two pogo pins which is connected to a power supply.
+Additionally, two extra contacts are placed on the chip which facilitates 4 wire measurement of the resistance of the heating element.
+The heating strip is hence used as a resistance temperature detector (RTD) to monitor the temperature of the chip.
+At the current configuration temperatures from room temperature to approximately 450\,$^{\circ}$C can be reached.
+
+\subsubsection{Gas handling}
+The two gas inlets on the microreactor chip is connected to a gas handling system.
+A total of 6 gases with accompanying flow controllers are used to control the inlet gas.
+Currently, the system is configured in a 4+2 setup where 4 gases are connected to the one inlet and to gases on the other inlet.
+All valves and flow controllers are interfaced to computer enabling remote control of the system and the possibility to run experiments over several days without human intervention.
+
 \subsection{Time of flight}
+The time of flight equipment used for detection of gas molecules flowed through the capillary of the microreactor is designed as an orthogonal mass spectrometer.
+Ionized ions enter the source through a series of Einzel lenses used for focusing the beam minimizing divergence.
+In the source they are pushed into the flight tube by an the initial push voltage, V$_p$.
+The ions are further accelerated from ground potential to the liner potential, V$_L$, which is the drift voltage of the flight tube.
+At the end of the flight tube a reflectron is installed which have two primary purposes.
+The effective drift length is increased hence increasing resolution of the equipment.
+The reflectron also works as a focusing lens compensating for any initial velocity dispersion of the ions, i.e.
+ions with an initial higher velocity will have an increased flight length compared to slower ions.
+The microchannel plate (MCP) used for detection is placed in the focal point of the reflectron giving maximum compensation for initial velocity dispersion.
+The theoretical resolution of the equipment is $\Delta$m/m$\sim$4000.
 
 \subsubsection{Ionization of gas}
+As ionization source of the gas flow from the microreactor capillary an modified Bayard-Alpert ion gauge is used.
 
@@
 
+\bibliographystyle{unsrt}
+\bibliography{literature}
+
 \end{document}

### 2012-03-15 paper_styleless.tex
Started on the introduction

@@
-\documentclass[12pt]{article}
+\documentclass[11pt]{article}
 \usepackage{graphicx}
@@
 \section{Introduction}
-Something about the relevance of this system. Catalysis is interesting because... Typical problems with QMS approach.
+In heterogeneous catalysis the optimization and development of equipment is important both to minimize the cost of equipment but also to be able to study complicated systems.
+As a platform for testing heterogeneous catalysts microfabricated reactors or microreactors have been found suitable due to both the high surface-to-volume ratio, the fast temperature response and minimization of thermal and concentration gradients.
+Such a platform have among other places been developed in our department \cite{Henriksen2009}.
+However, a suitable reactor platform is only part of the task.
+Typically, quadrupole mass spectrometers (QMSs) are used in low pressure regimes to analyze gas composition while gas chromatographs are used for high pressure measurements.
+The QMS, however, suffer from a low mass resolution ($\Delta$m/m$\sim$200) which makes analysis of complicated spectra difficult and cumbersome and a low mass range (typically up to $\sim$500\,amu).
+Furthermore, QMSs are typically operated by logging a single (or a few) masses as a function of time to increase the time resolution.
+This in turn is on the expense of being unable to acquire full mass spectra continuously.
+Something negative about chromatographs...
+As an alternative time of flight mass spectrometers (TOF-MS) offer both high mass resolution ($\Delta$m/m$>$400) and fast acquisition of full mass spectra ($>$1\,Hz) along with mass range only limited by the detector.
+For a typical microchannel plate (MCP) a mass range of (0--5000\,amu) can be obatined Until now, to our knowlegde, the testing of catalysts in a microreactor with subsequent gas analysis by a TOF-MS have not been demonstrated.
+Here we desribe a microreactor and TOF-MS system which combines the high sensitivity of microreactors and the high mass resolution TOF-MSs for use in heterogeneous catalysis.
 
@@
 The complete system enables high sensitivity reactivity measurements of the catalyst under investigation combined with high resolution mass spectrometry.
-The catalyst under investigation is deposited in a microcreactor from where the products are detected with time of flight mass spectrometry.
+The catalyst under investigation is deposited in a microreactor from where the products are detected with time of flight mass spectrometry.
 A schematic of the entire setup is shown in Figure \ref{fig:TOF_microreactor}
@@
 \end{center}
+Three setup consists of three main components.
+The microreactor where the catalyst under investigation is deposited, an ionization source which ionizes the gas from the microreactor and the TOF equipment used for gas analysis.
 
@@
 \subsubsection{Ionization of gas}
-As ionization source of the gas flow from the microreactor capillary an modified Bayard-Alpert ion gauge is used.
+As ionization source of the gas flow from the microreactor capillary an modified nude UHV Bayard-Alpert ion gauge is used.
+Approximately 3\,A is run through the filament resulting in approximately 10\,mA emission current.
+The grid is biased approximately 40\,V negative compared to the filament to accelerate electrons emitted from the filament towards the grid.
+Contrary to standard operation of a ion gauge the collector in the center of the grid is short-circuited to grid to ensure homogeneous field distribution within the grid.
+To allow ionized ions to escape from the grid the lid of the grid have been removed.
+Using this configuration approximately half of the ionized ions are expected to leave the ionization gauge.
+The entire construction is placed in a nozzle which is differentially pumped.
+Large amounts of gases can hence be dosed locally around the ion gauge while still maintaining a low pressure in the source region of the TOF.
+The nozzle is essential in the setup to avoid high pressure in the source region resulting in a increase in dead counts on the MCP thus decreasing the noise to signal ratio of the recorded signal.
 

### 2012-03-15 paper.tex
Added a reference
Initial writing on the article
Merged two versions. Now only in RevTex

@@
 
-\documentclass[aip,rsi,graphicx]{revtex4-1}
+\documentclass[aip,rsi]{revtex4-1}
+\usepackage{graphicx}
 %\documentclass[aip,reprint]{revtex4-1}
@@
 \section{Introduction}
-Ever since, yada yada... \cite{WILEY1955} ...yada yada.....
+In heterogeneous catalysis the optimization and development of equipment is important both to minimize the cost of equipment but also to be able to study complicated systems.
+As a platform for testing heterogeneous catalysts microfabricated reactors or microreactors have been found suitable due to both the high surface-to-volume ratio, the fast temperature response and minimization of thermal and concentration gradients.
+Such a platform have among other places been developed in our department \cite{Henriksen2009}.
+However, a suitable reactor platform is only part of the task.
+Typically, quadrupole mass spectrometers (QMSs) are used in low pressure regimes to analyze gas composition while gas chromatographs are used for high pressure measurements.
+The QMS, however, suffer from a low mass resolution ($\Delta$m/m$\sim$200) which makes analysis of complicated spectra difficult and cumbersome and a low mass range (typically up to $\sim$500\,amu).
+Furthermore, QMSs are typically operated by logging a single (or a few) masses as a function of time to increase the time resolution.
+This in turn is on the expense of being unable to acquire full mass spectra continuously.
+Something negative about chromatographs...
+As an alternative time of flight mass spectrometers (TOF-MS) offer both high mass resolution ($\Delta$m/m$>$400) and fast acquisition of full mass spectra ($>$1\,Hz) along with mass range only limited by the detector.
+For a typical microchannel plate (MCP) a mass range of (0--5000\,amu) can be obatined Until now, to our knowlegde, the testing of catalysts in a microreactor with subsequent gas analysis by a TOF-MS have not been demonstrated.
+Here we desribe a microreactor and TOF-MS system which combines the high sensitivity of microreactors and the high mass resolution TOF-MSs for use in heterogeneous catalysis.
 
-\section{Experimental Setup}
-%\label{}
-\subsection{Microreactors}
-%\subsubsection{}
-\subsection{Time Of Flight Mass Spectrometer}
+\section{System design}
+The complete system enables high sensitivity reactivity measurements of the catalyst under investigation combined with high resolution mass spectrometry.
+The catalyst under investigation is deposited in a microreactor from where the products are detected with time of flight mass spectrometry.
+A schematic of the entire setup is shown in Figure \ref{fig:TOF_microreactor}
+\begin{figure}
+ \includegraphics[width=14cm]{TOF_microreactor.png}%
+ \caption{Schematic of the total system (not to scale)\label{fig:TOF_microreactor}}%
+\end{figure}
+Three setup consists of three main components.
+The microreactor where the catalyst under investigation is deposited, an ionization source which ionizes the gas from the microreactor and the TOF equipment used for gas analysis.
 
-\section{Results}
+\subsection{Microreactor and gas handling}
 
-\section{Conclusion}
+\subsubsection{The microreactor platform}
+Catalysts testing were performed in a microreactor platform \cite{Henriksen2009}.
+The microreactors are fabricated in silicon and measures 20x15\,mm.
+The reactor consists of two gas inlets, a gas outlet, a reactor volume and a capillary used for probing the gas from the reactor volume.
+The reactor volume is 3\,$\mu$m deep and 1 cm in diameter resulting in a 240\,nL volume.
+The two gas inlets are combined on the chip where the inlet gases mix by diffusion.
+The capillary is designed such that approximately $3\cdot10^{14}$\,molecules$\cdot$s$^{-1}$ is probed from the reactor volume.
+Any surplus of gas from the two inlets that does not enter the reactor volume is directed through the outlet into a turbo pump.
+The design ensures that all molecules entering the reactor volume hence exposed to the catalyst under investigation is detected giving the system high sensitivity.
+
+The microreactor is heated by joule heating of a 50 nm platinum strip evaporated through a shadow mask on the backside of the chip.
+The heating element is contacted by two pogo pins which is connected to a power supply.
+Additionally, two extra contacts are placed on the chip which facilitates 4 wire measurement of the resistance of the heating element.
+The heating strip is hence used as a resistance temperature detector (RTD) to monitor the temperature of the chip.
+At the current configuration temperatures from room temperature to approximately 450\,$^{\circ}$C can be reached.
+
+\subsubsection{Gas handling}
+The two gas inlets on the microreactor chip is connected to a gas handling system.
+A total of 6 gases with accompanying flow controllers are used to control the inlet gas.
+Currently, the system is configured in a 4+2 setup where 4 gases are connected to the one inlet and to gases on the other inlet.
+All valves and flow controllers are interfaced to computer enabling remote control of the system and the possibility to run experiments over several days without human intervention.
+
+\subsection{Time of flight}
+The time of flight equipment used for detection of gas molecules flowed through the capillary of the microreactor is designed as an orthogonal mass spectrometer.
+Ionized ions enter the source through a series of Einzel lenses used for focusing the beam minimizing divergence.
+In the source they are pushed into the flight tube by an the initial push voltage, V$_p$.
+The ions are further accelerated from ground potential to the liner potential, V$_L$, which is the drift voltage of the flight tube.
+At the end of the flight tube a reflectron is installed which have two primary purposes.
+The effective drift length is increased hence increasing resolution of the equipment.
+The reflectron also works as a focusing lens compensating for any initial velocity dispersion of the ions, i.e.
+ions with an initial higher velocity will have an increased flight length compared to slower ions.
+The microchannel plate (MCP) used for detection is placed in the focal point of the reflectron giving maximum compensation for initial velocity dispersion.
+The theoretical resolution of the equipment is $\Delta$m/m$\sim$4000.
+
+\subsubsection{Ionization of gas}
+As ionization source of the gas flow from the microreactor capillary an modified nude UHV Bayard-Alpert ion gauge is used.
+Approximately 3\,A is run through the filament resulting in approximately 10\,mA emission current.
+The grid is biased approximately 40\,V negative compared to the filament to accelerate electrons emitted from the filament towards the grid.
+Contrary to standard operation of a ion gauge the collector in the center of the grid is short-circuited to grid to ensure homogeneous field distribution within the grid.
+To allow ionized ions to escape from the grid the lid of the grid have been removed.
+Using this configuration approximately half of the ionized ions are expected to leave the ionization gauge.
+The entire construction is placed in a nozzle which is differentially pumped.
+Large amounts of gases can hence be dosed locally around the ion gauge while still maintaining a low pressure in the source region of the TOF.
+The nozzle is essential in the setup to avoid high pressure in the source region resulting in a increase in dead counts on the MCP thus decreasing the noise to signal ratio of the recorded signal.
+
+\section{Test system}
+Ammonia oxidation
+
+\section{Summary}
+
+\section{Acknowledgements}
 

### 2012-03-15 python_figures/ammonia_reactivity.py
Started new figure and included two figures in the manuscript

@@ -1,0 +1,130 @@
+import matplotlib
+from scipy import optimize
+import math
+#matplotlib.use('svg')
+#matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+import numpy as np
+import MySQLdb
+import sys
+from matplotlib.backends.backend_pdf import PdfPages
+
+matplotlib.rc('text',usetex=True) # Magic fix for the font warnings
+
+try:
+    db = MySQLdb.connect(host="servcinf", user="cinf_reader",passwd = "cinf_reader", db = "cinfdata")
+except:
+    db = MySQLdb.connect(host="127.0.0.1", port=9995, user="cinf_reader",passwd = "cinf_reader", db = "cinfdata")
+
+
+cursor = db.cursor()
+
+import thin_film_config as config
+
+data = {}
+
+#Get all data from the db
+for i in range(0,len(config.temperatures)):
+    print config.temperatures[i]
+    cursor.execute("SELECT x*1000000,y*1000 FROM xy_values_tof where measurement = " + str(i + config.initial_db))
+    data[i] = np.array(cursor.fetchall())
+
+
+treated_data = {}
+#Prepare the list that will hold the (temp,intensity) values
+for mass in config.masses:
+    treated_data[mass[0]] = np.zeros((len(config.temperatures),2))
+
+
+pp = PdfPages('multipage.pdf')
+for j in range(0,len(config.temperatures)):
+    print j
+    pdffig = plt.figure()
+    i = 0
+    Data = data[j]
+    for mass in config.masses:
+        i = i + 1
+        axis = pdffig.add_subplot(4,3,i)
+        center = (int)(mass[1] * 2000) ## Notice... 
+        center_mass = mass[1]
+        Start = center -40 #Display range
+        End = center + 40
+        start = center - mass[2] #Fitting range
+        end = center + mass[2]
+
+        offset = min(Data[Start:End,1])
+        x_values = Data[start:end,0]
+        y_values = Data[start:end,1]-offset
+        X_values = Data[Start:End,0]
+        Y_values = Data[Start:End,1]-offset
+        
+        # Fit the first set
+        fitfunc = lambda p, x: p[0]*math.e**(-1*((x-center_mass-p[2])**2)/p[1])       # Target function
[…]

### 2012-03-15 python_figures/thin_film_config.py

@@ -1,0 +1,31 @@
+temperatures = []
+
+"""
+temperatures = temperatures + [40,60,80]
+
+for i in range(100,195,5): #Note last value is not included
+    temperatures = temperatures + [i]
+
+for i in range(180,105,-5): #Note last value is not included
+    temperatures = temperatures + [i]
+
+print len(temperatures)
+"""
+for i in range(100,185,5): #Note last value is not included
+    temperatures = temperatures + [i]
+
+
+for i in range(180,95,-5): #Note last value is not included
+    temperatures = temperatures + [i]
+
+initial_db = 189+38
+
+masses = []
+#masses.append(['H2',4.387,8])
+masses.append(['OH',12.418,6])
+masses.append(['NH3',12.427,6])
+masses.append(['H2O',12.777,8])
+masses.append(['N2',15.89,8])
+masses.append(['O2',16.972,8])
+#masses.append(['N2O',19.874,10])
+

### 2012-03-15 python_figures/ammonia_reactivity.py
End-of-day commit, nothing fancy

@@ -84,7 +84,7 @@ for j in range(0,len(config.temperatures)):
         charge = 0
         treated_data[mass[0]][j][0] = config.temperatures[j]
         treated_data[mass[0]][j][1] = math.sqrt(math.pi)*p1[0] * math.sqrt(p1[1])
-    plt.savefig(pp, format='pdf')
+    #plt.savefig(pp, format='pdf')
     plt.close()
 pp.close()
 
@@ -98,19 +98,7 @@ fig_height = fig_width*ratio
 fig.set_size_inches(fig_width,fig_height)
 
 
-axis = fig.add_subplot(2,1,1)
-fig.subplots_adjust(hspace=0.3)
-
-i = 0
-for mass in config.masses:    
-    axis.plot(treated_data[mass[0]][:,0],treated_data[mass[0]][:,1], colors[i],label=mass[0])
-    i = i + 1
-    
-    
-axis.set_ylabel('Response / mV$\cdot$s', fontsize=14)
-axis.set_xlabel('Temperature', fontsize=14)
-axis.legend()
-axis = fig.add_subplot(2,1,2)
+axis = fig.add_subplot(1,1,1)
 i = 0
 for mass in config.masses:    
     axis.plot(treated_data[mass[0]][:,1], colors[i],label=mass[0])

### 2012-03-15 python_figures/ammonia_reactivity.py
Reactivity graph almost finished

@@ -2,7 +2,7 @@ import matplotlib
 from scipy import optimize
 import math
 #matplotlib.use('svg')
-#matplotlib.use('Agg')
+matplotlib.use('Agg')
 import matplotlib.pyplot as plt
 import numpy as np
 import MySQLdb
@@ -25,7 +25,7 @@ data = {}
 
 #Get all data from the db
 for i in range(0,len(config.temperatures)):
-    print config.temperatures[i]
+    print str(config.temperatures[i]) + " " + str(i + config.initial_db)
     cursor.execute("SELECT x*1000000,y*1000 FROM xy_values_tof where measurement = " + str(i + config.initial_db))
     data[i] = np.array(cursor.fetchall())
 
@@ -90,9 +90,10 @@ pp.close()
 
 colors = ['ro-','bo-','go-','co-','mo-','yo-','r*-','b*-','g*-']
 fig = plt.figure()
-fig.subplots_adjust(bottom=0.2) # Make room for x-label
-ratio = 0.4                     # This figure should be very wide to span two columns
-fig_width = 10
+fig.subplots_adjust(bottom=0.15) # Make room for x-label
+fig.subplots_adjust(right=0.85) # Make room for x-label
+ratio = 0.7                     # This figure should be very wide to span two columns
+fig_width = 9
 fig_width = fig_width /2.54     # width in cm converted to inches
 fig_height = fig_width*ratio
 fig.set_size_inches(fig_width,fig_height)
@@ -101,18 +102,34 @@ fig.set_size_inches(fig_width,fig_height)
 axis = fig.add_subplot(1,1,1)
 i = 0
 for mass in config.masses:    
-    axis.plot(treated_data[mass[0]][:,1], colors[i],label=mass[0])
+    axis.plot(treated_data[mass[0]][:,1], colors[i],label=mass[0],markersize=0.75)
     i = i + 1
 
-axis.set_xlabel('Measurement number', fontsize=14)
-axis.set_ylabel('Response / mV$\cdot$s', fontsize=14)
+axis.set_xlabel('Measurement number', fontsize=8)
+axis.set_ylabel('Response / mV$\cdot$s', fontsize=8)
+
+
+axis.set_yticks((0.5,1,1.5,2,2.5))
+
+arrow = dict(facecolor='black',arrowstyle='->')
+font = 8
[…]

### 2012-03-15 python_figures/thin_film_config.py

@@ -11,9 +11,11 @@ for i in range(180,105,-5): #Note last value is not included
 
 print len(temperatures)
 """
+
 for i in range(100,185,5): #Note last value is not included
     temperatures = temperatures + [i]
 
+temperatures = temperatures + [190]
 
 for i in range(180,95,-5): #Note last value is not included
     temperatures = temperatures + [i]

### 2012-03-15 python_figures/ammonia_OH_gauss_fit.py
Much improved figure of the double peak fit

@@ -8,6 +8,12 @@ import numpy as np
 import MySQLdb
 import sys
 
+def TimeToMass(time):
+    #time = 2.97277909899 * mass^0.499352719883
+    corr_time = time - 0.183  #Approximate delay
+    mass = (corr_time / 2.97277909899)**(1.0/0.499352719883)
+    return mass
+
 matplotlib.rc('text',usetex=True) # Magic fix for the font warnings
 
 try:
@@ -20,6 +26,7 @@ cursor = db.cursor()
 
 fig = plt.figure()
 fig.subplots_adjust(bottom=0.2) # Make room for x-label
+fig.subplots_adjust(top=0.8) # Make room for extra x-label
 ratio = 0.4                     # This figure should be very wide to span two columns
 fig_width = 10
 fig_width = fig_width /2.54     # width in cm converted to inches
@@ -80,13 +87,30 @@ for mass in masses:
 
 axis.plot(X_range,fit[0]+fit[1],'g-',linewidth=0.5)
 axis.plot(X_values,Y_values,'b.',markersize=1.5)
-axis.tick_params(direction='in', length=2, width=1, colors='k',labelsize=8,axis='both',pad=5)
+axis.tick_params(direction='in', length=2, width=1, colors='k',labelsize=8,axis='both',pad=3)
 axis.set_yticks((20,40,60))    
 axis.set_xticks((12.41,12.42,12.43,12.44))    
 axis.ticklabel_format(useOffset=False)
 axis.set_xlim(12.405,12.44)
 axis.set_ylabel('Response / mV', fontsize=8)
 axis.set_xlabel('Flight Time / $\mu$s', fontsize=8)
+
+
+arrow = dict(facecolor='black',arrowstyle='->')
+font = 8
+axis.annotate('OH', xy=(12.416, 60),  xycoords='data', xytext=(12.41, 50), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='top',fontsize=font,)
+axis.annotate('NH$_3$', xy=(12.428, 40),  xycoords='data', xytext=(12.433, 50), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='top',fontsize=font,)
+
+
+
+axis3 = axis.twiny()
+axis3.plot(TimeToMass(X_range),X_range*0,'w-',linewidth=0) #Hack to create an invisible set on the extra x-axis
[…]

### 2012-03-15 python_figures/tof_raw.py
Improvements on the raw-data figure. Something wrong with x-scale...

@@ -16,6 +16,18 @@ except:
 
 cursor = db.cursor()
 
+#SOMETHING WRONG WITH THE X-SCALE!!!!
+
+#Mass of methanol: 32.0262147
+#Mass of oxygen: 31.9898292
+def TimeToMass(time):
+    #time = 2.9870925856 * mass^0.497621653202
+    #corr_time = time - 0.183  #Approximate delay - not optimized for this spectrum
+    mass = (time / 2.9870925856)**(1.0/0.497621653202)
+    #mass = mass - 0.413085820678 # Approximate value, not optimized for this spectrum
+    return mass
+
+print TimeToMass(20)
 data = {}
 #Methanol + oxygen
 cursor.execute("SELECT x*1000000,y*1000 FROM xy_values_tof where measurement = 170")
@@ -24,8 +36,11 @@ data['ch'] = np.array(cursor.fetchall())
 axis_array = []
 fig = plt.figure()
 fig.subplots_adjust(bottom=0.15) # Make room for x-label
+fig.subplots_adjust(top=0.8) # Make room for extra x-label
 
 LINEWIDTH = 0.5
+arrow = dict(facecolor='black',arrowstyle='->')
+font = 8
 
 ratio = 0.4                     # This figure should be very wide to span two columns
 fig_width = 17
@@ -39,8 +54,26 @@ gs.update(wspace=0.2,hspace=0.2)
 axis = plt.subplot(gs[0, :])
 
 axis.plot(data['ch'][:,0], data['ch'][:,1], 'r-',linewidth=LINEWIDTH)
+#xticks = range(0,20,4)
+#axis.set_xticks((xticks))
 axis.set_ylim(0,20)
 axis.set_xlim(0,20)
+
+
+
+axis3 = axis.twiny()
+axis3.plot(TimeToMass(data['ch'][:,0]),data['ch'][:,0]*0,'w-',linewidth=0) #Hack to create an invisible set on the extra x-axis
+axis3.set_xlim(TimeToMass(0),TimeToMass(20))
+#axis3.set_xticks((12.41,12.42,12.43,12.44))    
+axis3.set_xlabel('Mass / AMU', fontsize=8)
+axis3.tick_params(direction='in', length=2, width=1, colors='k',labelsize=8,axis='both',pad=3)
+#xticks = range(0,50,5)
+#axis3.set_xticks((xticks))
[…]

### 2012-03-16 tick_example.py
Added example code to help implement non-uniform x-ticks

@@ -1,0 +1,24 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+
+N = 5
+menMeans   = (20, 35, 30, 35, 27)
+womenMeans = (25, 32, 34, 20, 25)
+menStd     = (2, 3, 4, 1, 2)
+womenStd   = (3, 5, 2, 3, 3)
+ind = np.arange(N)    # the x locations for the groups
+ind2 = np.arange(N)+2
+width = 0.35       # the width of the bars: can also be len(x) sequence
+
+p1 = plt.bar(ind, menMeans,   width, color='r', yerr=womenStd)
+p2 = plt.bar(ind, womenMeans, width, color='y',
+             bottom=menMeans, yerr=menStd)
+
+plt.ylabel('Scores')
+plt.title('Scores by group and gender')
+plt.xticks(ind2+width/2., ('G1', 'G2', 'G3', 'G4', 'G5') )
+plt.yticks(np.arange(0,81,10))
+plt.legend( (p1[0], p2[0]), ('Men', 'Women') )
+
+plt.show()

### 2012-03-16 python_figures/tof_raw.py
Fixed the x-axis and added more arrows

@@ -20,14 +20,12 @@ cursor = db.cursor()
 
 #Mass of methanol: 32.0262147
 #Mass of oxygen: 31.9898292
-def TimeToMass(time):
-    #time = 2.9870925856 * mass^0.497621653202
-    #corr_time = time - 0.183  #Approximate delay - not optimized for this spectrum
-    mass = (time / 2.9870925856)**(1.0/0.497621653202)
-    #mass = mass - 0.413085820678 # Approximate value, not optimized for this spectrum
-    return mass
+def MassToTime(mass):
+    time = 2.9870925856 * (mass**0.497621653202)
+    corr_time = time + 0.207
+    return corr_time
 
-print TimeToMass(20)
+
 data = {}
 #Methanol + oxygen
 cursor.execute("SELECT x*1000000,y*1000 FROM xy_values_tof where measurement = 170")
@@ -54,22 +52,21 @@ gs.update(wspace=0.2,hspace=0.2)
 axis = plt.subplot(gs[0, :])
 
 axis.plot(data['ch'][:,0], data['ch'][:,1], 'r-',linewidth=LINEWIDTH)
-#xticks = range(0,20,4)
-#axis.set_xticks((xticks))
 axis.set_ylim(0,20)
 axis.set_xlim(0,20)
+axis.set_xticks([2.5,5,7.5,10,12.5,15,17.5,20])
 
-
+mass_ticks = np.array([1,5,10,15,20,25,30,35,40])
 
 axis3 = axis.twiny()
-axis3.plot(TimeToMass(data['ch'][:,0]),data['ch'][:,0]*0,'w-',linewidth=0) #Hack to create an invisible set on the extra x-axis
-axis3.set_xlim(TimeToMass(0),TimeToMass(20))
-#axis3.set_xticks((12.41,12.42,12.43,12.44))    
+#axis3.plot(data['ch'][:,0],data['ch'][:,0]*0,'w-',linewidth=0) #Hack to create an invisible set on the extra x-axis
+axis3.set_xlim(0,20)
+print MassToTime(32.0262147)
+axis3.set_xticks(MassToTime(mass_ticks))
+axis3.set_xticklabels(mass_ticks)
 axis3.set_xlabel('Mass / AMU', fontsize=8)
 axis3.tick_params(direction='in', length=2, width=1, colors='k',labelsize=8,axis='both',pad=3)
-#xticks = range(0,50,5)
[…]

### 2012-03-16 tick_example.py

@@ -1,24 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-
-
-N = 5
-menMeans   = (20, 35, 30, 35, 27)
-womenMeans = (25, 32, 34, 20, 25)
-menStd     = (2, 3, 4, 1, 2)
-womenStd   = (3, 5, 2, 3, 3)
-ind = np.arange(N)    # the x locations for the groups
-ind2 = np.arange(N)+2
-width = 0.35       # the width of the bars: can also be len(x) sequence
-
-p1 = plt.bar(ind, menMeans,   width, color='r', yerr=womenStd)
-p2 = plt.bar(ind, womenMeans, width, color='y',
-             bottom=menMeans, yerr=menStd)
-
-plt.ylabel('Scores')
-plt.title('Scores by group and gender')
-plt.xticks(ind2+width/2., ('G1', 'G2', 'G3', 'G4', 'G5') )
-plt.yticks(np.arange(0,81,10))
-plt.legend( (p1[0], p2[0]), ('Men', 'Women') )
-
-plt.show()

### 2012-03-16 python_figures/dynamic_range.py
Significant progress on the graph showing dynamic range

@@ -1,0 +1,94 @@
+import matplotlib
+from scipy import optimize
+import math
+#matplotlib.use('svg')
+#matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+import matplotlib.gridspec as gridspec
+import numpy as np
+import MySQLdb
+
+matplotlib.rc('text',usetex=True) # Magic fix for the font warnings
+
+try:
+    db = MySQLdb.connect(host="servcinf", user="cinf_reader",passwd = "cinf_reader", db = "cinfdata")
+except:
+    db = MySQLdb.connect(host="127.0.0.1", port=9995, user="cinf_reader",passwd = "cinf_reader", db = "cinfdata")
+
+
+cursor = db.cursor()
+
+fig = plt.figure()
+fig.subplots_adjust(bottom=0.2) # Make room for x-label
+fig.subplots_adjust(top=0.8) # Make room for extra x-label
+ratio = 0.4                     # This figure should be very wide to span two columns
+fig_width = 10
+fig_width = fig_width /2.54     # width in cm converted to inches
+fig_height = fig_width*ratio
+fig.set_size_inches(fig_width,fig_height)
+
+gs = gridspec.GridSpec(3, 3)
+
+#Relevant time, OH: 12.418, NH3: 12.427
+data = {}
+cursor.execute("SELECT x*1000000,y*1000 FROM xy_values_tof where measurement = 209")
+Data = np.array(cursor.fetchall())
+
+masses = []
+masses.append(['H$_2$O',12.777,8])
+masses.append(['H$_2$',4.387,8])
+masses.append(['O$_2$',16.972,8])
+
+fit = []
+
+#X_range = Data[24600:25000,0]
+#X_range = np.arange(12.405,12.44,0.0001)
+
+i = 0
+
+for mass in masses:
+    i = i + 1
+    axis = plt.subplot(gs[:-1, i-1])
+    
+    center = (int)(mass[1] * 2000) ## Notice... 
+    center_mass = mass[1]
+    Start = center -35 #Display range
+    End = center + 35
+    start = center - mass[2] #Fitting range
+    end = center + mass[2]
+
+    offset = min(Data[Start:End,1])
+    x_values = Data[start:end,0]
+    y_values = Data[start:end,1]-offset
+    X_values = Data[Start:End,0]
+    Y_values = Data[Start:End,1]-offset
+    
+    # Fit the first set
[…]

### 2012-03-17 paper.tex
Started new figure and included two figures in the manuscript
Started on the results section

@@
 
+In Figure \ref{fig:untreated_data} an example spectrum of a methanol and atmospheric air mixture is shown.
+Here both the high resolution is demonstrated by the resolved methanol and molecular which has a mass difference of 43\,milliamu.
+\begin{figure}
+ \includegraphics[width=16cm]{untreated_data.png}%
+ \caption{Raw data acquired from the TOF-MS in a gas mixture of methanol and atmospheric air.
+Subfigures show the three different regions of the spectrum.
+From the first subfigure a delay of the approximately 150\,ns can be seen which is due to delays in cables and rise time of the pulser.
+From the center subfigure it is evident that 1\,amu corresponds to approximately 350\,ns difference in flight time in our system.
+From the last subfigure the a zoom of the methanol and molecular oxygen (43\,milliamu mass difference) region is shown.\label{fig:untreated_data}}%
+\end{figure}
+
 \subsubsection{Ionization of gas}
@@
 
-\section{Test system}
-Ammonia oxidation
+\subsubsection{Data treatment}
+\begin{figure}
+ \includegraphics[width=14cm]{ammonia_OH_gauss_fit.png}%
+ \caption{Example of Gaussion fit to a double peak. Each gaussion yields the area of the respective component.\label{fig:gaussian_fit}}%
+\end{figure}
+
+\section{Oxidation of ammonia}
+To demonstrate the system capability ammonia oxidation on platinum thin films have been used as a test reaction.
+In a stoichiometric mixture of ammonia and molecular oxygen a clean combustion to molecular nitrogen and water is expected.
+\begin{equation}
+4NH_3+3O_2\rightarrow 2N_2 + 6H_2O
+\end{equation}
+This system is, however, difficult to monitor by a QMS due to the overlap of NH$_3$ which is a reactant and OH$^-$ which is a cracking product from H$_2$O which is a product.
+Specifically, hydroxyls (OH$^{+}$) from cracking of trace water in the system and the primary peak of ammonia (NH$_{3}^{+}$) is both detected at approximately m/q = 17.
+The mass resolution of a QMS is typically not adequate to separate the two contributions.
+Often a mass without cracking from either products or residue gas in the system is necessary to be able to detect the amount of ammonia in the system.
+Typically m/q=15 or m/q=8.5 is chosen to detect ammonia.
+The monitoring of other than the primary mass to charge ratio due to mass overlap is generally not wanted due to the lowering of the signal to noise ratio.
+This in turns affect the detection limit of the given mass.
+Due
 

### 2012-03-19 python_figures/dynamic_range.py
Dynamic range figure almost done

@@ -2,7 +2,7 @@ import matplotlib
 from scipy import optimize
 import math
 #matplotlib.use('svg')
-#matplotlib.use('Agg')
+matplotlib.use('Agg')
 import matplotlib.pyplot as plt
 import matplotlib.gridspec as gridspec
 import numpy as np
@@ -19,10 +19,12 @@ except:
 cursor = db.cursor()
 
 fig = plt.figure()
-fig.subplots_adjust(bottom=0.2) # Make room for x-label
-fig.subplots_adjust(top=0.8) # Make room for extra x-label
-ratio = 0.4                     # This figure should be very wide to span two columns
-fig_width = 10
+fig.subplots_adjust(bottom=0.1) # Make room for x-label
+fig.subplots_adjust(top=0.9) # Make room for extra x-label
+fig.subplots_adjust(wspace=0.25)
+fig.subplots_adjust(hspace=0.25)
+ratio = 0.6
+fig_width = 12
 fig_width = fig_width /2.54     # width in cm converted to inches
 fig_height = fig_width*ratio
 fig.set_size_inches(fig_width,fig_height)
@@ -38,6 +40,15 @@ masses = []
 masses.append(['H$_2$O',12.777,8])
 masses.append(['H$_2$',4.387,8])
 masses.append(['O$_2$',16.972,8])
+
+x_ticks = []
+y_ticks = []
+x_ticks.append([12.767,12.777,12.787])
+x_ticks.append([4.377,4.387,4.397])
+x_ticks.append([16.962,16.972,16.982])
+y_ticks.append([100,200,300,400])
+y_ticks.append([5,10,15,20])
+y_ticks.append([0.2,0.4,0.6,0.8])
 
 fit = []
 
@@ -70,25 +81,37 @@ for mass in masses:
     p1, success = optimize.leastsq(errfunc, p0[:], args=(x_values, y_values),maxfev=1000)        
     signal = math.sqrt(math.pi)*p1[0] * math.sqrt(p1[1])    
     
-    axis.plot(X_values,Y_values,'b-',linewidth=1.1)    
-    axis.plot(X_values,fitfunc(p1, X_values),'r--',linewidth=1.1)
+    axis.plot(X_values,Y_values,'bo',linewidth=1.1,markersize=3)    
+    axis.plot(X_values,fitfunc(p1, X_values),'r-',linewidth=1.1)
     axis.ticklabel_format(useOffset=False)
[…]

### 2012-03-19 paper.tex
Included dynamic range figure and wrote on the result section

@@
 \section{Oxidation of ammonia}
-To demonstrate the system capability ammonia oxidation on platinum thin films have been used as a test reaction.
-In a stoichiometric mixture of ammonia and molecular oxygen a clean combustion to molecular nitrogen and water is expected.
+To demonstrate the system capability ammonia oxidation on platinum thin films have been used as a test reaction. The catalytic oxidation of ammonia can proceed in primarily three different routes.
 \begin{equation}
 4NH_3+3O_2\rightarrow 2N_2 + 6H_2O
+\label{eq:Pt_clean_combustion}
 \end{equation}
-This system is, however, difficult to monitor by a QMS due to the overlap of NH$_3$ which is a reactant and OH$^-$ which is a cracking product from H$_2$O which is a product.
-Specifically, hydroxyls (OH$^{+}$) from cracking of trace water in the system and the primary peak of ammonia (NH$_{3}^{+}$) is both detected at approximately m/q = 17.
+\begin{equation}
+2NH_3+2O_2\rightarrow N_2O + 3H_2O
+\end{equation}
+\begin{equation}
+4NH_3+5O_2\rightarrow 4NO + 6H_2O
+\end{equation}
+For a clean combustion reaction pathway \ref{eq:Pt_clean_combustion} is preferred.
+This system is, however, difficult to monitor by a QMS due to the overlap of NH$_3$ and OH$^-$ which is a cracking product from H$_2$O.
+Specifically, hydroxyls (OH$^{+}$) from cracking of trace water in the system and the primary peak of ammonia (NH$_{3}^{+}$) is both detected at m/q = 17 in a QMS.
 The mass resolution of a QMS is typically not adequate to separate the two contributions.
-Often a mass without cracking from either products or residue gas in the system is necessary to be able to detect the amount of ammonia in the system.
-Typically m/q=15 or m/q=8.5 is chosen to detect ammonia.
-The monitoring of other than the primary mass to charge ratio due to mass overlap is generally not wanted due to the lowering of the signal to noise ratio.
+Often a mass without cracking from either products or residue gas in the system is used to be able to detect the amount of ammonia and water.
+In the case of ammonia m/q=15 or m/q=8.5 is typically chosen.
+The monitoring of other than the primary mass to charge ratio due to mass overlap is generally not wanted due to a lower signal to noise ratio of cracking masses.
 This in turns affect the detection limit of the given mass.
-Due
+Due the acquisition of entire mass spectra from mass instead of monitoring of individual masses the TOF-MS does is not limited to cracking masses resulting in higher signal to noise ratio spectra.
+\begin{figure}
+ \includegraphics[width=14cm]{ammonia_reactivity.png}%
+ \caption{Ammonia oxidation as a function of temperature on a Pt thin film.
+As the temperature is increased ammonia is oxidized to H$_2$O and N$_2$.
+Furthermore, the OH and NH$_3$ signal is anticorrelated demonstrating the ability to resolve these masses.\label{fig:ammonia_reactivity}}%
+\end{figure}
+In Figure \ref{fig:ammonia_reactivity} a number of masses as a function of time are shown.
+At experiment start the microreactor is equilibrated with a stoichiometric mix of NH$_3$ and O$_2$ (3:4).
+Hereafter the temperature is increased while TOF spectra are acquired.
+Spectra were acquired from triggering of the acceleration pulse up to 25\,$\mu$s of flight time corresponding to 70 amu in our system.
+
+For ammonia oxidation both N$_2$O (m/q = 44), NO (m/q = 30) and NO$_2$ (m/q = 46) are of interest.
+
+\begin{figure}
+ \includegraphics[width=14cm]{dynamic_range.png}%
+ \caption{Gaussian fits to three different mass to charge ratios from the same mass spectrum.
+As seen from the response a high dynamic range of the TOF-MS all yielding good gaussian fits.
+The TOF-MS can hence be used to monitor both very small and very large signal masses with high time resolution.\label{fig:dynamic_range}}%
+\end{figure}
 

### 2012-03-20 python_figures/ammonia_reactivity.py
Corrected spelling mistake

@@ -113,7 +113,7 @@ axis.set_yticks((0.5,1,1.5,2,2.5))
 
 arrow = dict(facecolor='black',arrowstyle='->')
 font = 8
-axis.annotate('H$_2$0', xy=(25, 2.3),  xycoords='data', xytext=(28, 2.8), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='top',fontsize=font,)
+axis.annotate('H$_2$O', xy=(25, 2.3),  xycoords='data', xytext=(28, 2.8), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='top',fontsize=font,)
 axis.annotate('N$_2$', xy=(20, 1.5),  xycoords='data', xytext=(17, 2), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='top',fontsize=font,)
 axis.annotate('NH$_3$', xy=(14, 0.7),  xycoords='data', xytext=(18, 1.2), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='top',fontsize=font,)
 axis.annotate('OH', xy=(24, 0.4),  xycoords='data', xytext=(23, 0.9), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='top',fontsize=font,)

### 2012-03-26 paper.tex
Changes after first initial readthrough

@@
 \begin{abstract}
-We demonstrate that high resolution time of flight mass spectrometry can be successfully applied to detect gas-phase product in hetrogeneous catalysis.
-Combining the instrument with the highly sensitive microreactors opens the possibility to measure on system that are otherwise difficult due to ....
+We demonstrate a combined microreactor and time of flight system for testing and characterization of heterogeneous catalyst with high resolution mass spectrometry and high sensitivity.
+Catalyst testing is performed in microreactors which have high sensitivity and fast thermal response.
+Gas analysis is performed with a time of flight mass spectrometer with a modified nude Bayard-Alpert ionization gauge as gas ionization source with a mass resolution of $\Delta$m/m$>$2500.
+The system design is superior to conventional batch and flow reactors not only due to the high sensitivity, fast temperature response and high mass resolution but also allows to measure on wide mass ranges (0--5000\,amu in the current configuration).
+As demonstration of the system we here present data from ammonia oxidation on platinum thin films showing resolved spectra of OH$^{-}$ and NH$_{3}^{+}$.
 \end{abstract}
@@
 In heterogeneous catalysis the optimization and development of equipment is important both to minimize the cost of equipment but also to be able to study complicated systems.
-As a platform for testing heterogeneous catalysts microfabricated reactors or microreactors have been found suitable due to both the high surface-to-volume ratio, the fast temperature response and minimization of thermal and concentration gradients.
-Such a platform have among other places been developed in our department \cite{Henriksen2009}.
-However, a suitable reactor platform is only part of the task.
+As a platform for testing heterogeneous catalysts microfabricated reactors or microreactors have been found suitable due to both high surface-to-volume ratio, fast temperature response and minimization of thermal and concentration gradients.
+Such a platform have been developed in our department \cite{Henriksen2009}.
+However, a suitable reactor platform is only part of the task; reactant and product detection and characterization is essential to determine catalyst performance.
 Typically, quadrupole mass spectrometers (QMSs) are used in low pressure regimes to analyze gas composition while gas chromatographs are used for high pressure measurements.
-The QMS, however, suffer from a low mass resolution ($\Delta$m/m$\sim$200) which makes analysis of complicated spectra difficult and cumbersome and a low mass range (typically up to $\sim$500\,amu).
+The QMS, however, suffer from a low mass resolution ($\Delta$m/m$\sim$200) which makes analysis of complicated spectra difficult and cumbersome.
+The QMS is additionally subject to a low mass range (typically up to $\sim$500\,amu) limiting general use.
 Furthermore, QMSs are typically operated by logging a single (or a few) masses as a function of time to increase the time resolution.
-This in turn is on the expense of being unable to acquire full mass spectra continuously.
-Something negative about chromatographs...
-As an alternative time of flight mass spectrometers (TOF-MS) offer both high mass resolution ($\Delta$m/m$>$400) and fast acquisition of full mass spectra ($>$1\,Hz) along with mass range only limited by the detector.
-For a typical microchannel plate (MCP) a mass range of (0--5000\,amu) can be obatined Until now, to our knowlegde, the testing of catalysts in a microreactor with subsequent gas analysis by a TOF-MS have not been demonstrated.
-Here we desribe a microreactor and TOF-MS system which combines the high sensitivity of microreactors and the high mass resolution TOF-MSs for use in heterogeneous catalysis.
+This in turn limits the ability to acquire full mass spectra continuously during the experiment.
+Gas chromatographs have inherently low time resolution which make them unsuitable for fast time response measurements as in the case of microreactors and is in general difficult to use as mass spectrometers.
+As an alternative to the gas chromatography or QMSs, time of flight mass spectrometers (TOF-MS) offer both high mass resolution ($\Delta$m/m$>$400) and fast acquisition of full mass spectra ($>$1\,Hz) along with mass range only limited by the detector.
+For a typical microchannel plate (MCP) a mass range of (0--5000\,amu) can be obtained.
+Until now, to our knowledge, the testing of catalysts in a microreactor with subsequent gas analysis by a TOF-MS have not been demonstrated.
+Here we describe a microreactor and TOF-MS system which combines the high sensitivity of microreactors and the high mass resolution TOF-MSs for testing and characterizing heterogeneous catalysts.
 
 \section{System design}
-The complete system enables high sensitivity reactivity measurements of the catalyst under investigation combined with high resolution mass spectrometry.
-The catalyst under investigation is deposited in a microreactor from where the products are detected with time of flight mass spectrometry.
-A schematic of the entire setup is shown in Figure \ref{fig:TOF_microreactor}
+The microreactor as a reactor and TOF as a mass spectrometer enables high sensitivity reactivity measurements of the catalyst under investigation combined with high resolution mass spectrometry.
+The catalyst under investigation is deposited in the microreactor from where reaction products are detected with time of flight mass spectrometry.
+A schematic of the entire setup is shown in Figure \ref{fig:TOF_microreactor}.
 \begin{figure}
@@
 \end{figure}
-Three setup consists of three main components.
-The microreactor where the catalyst under investigation is deposited, an ionization source which ionizes the gas from the microreactor and the TOF equipment used for gas analysis.
+The setup consists of three main components.
+The microreactor, where the catalyst under investigation is deposited, an ionization source which ionizes the gas from the microreactor and the TOF-MS used for gas analysis.
 
@@
 \subsubsection{The microreactor platform}
-Catalysts testing were performed in a microreactor platform \cite{Henriksen2009}.
+Catalyst characterization and performance evaluation was performed in a microreactor platform \cite{Henriksen2009}.
 The microreactors are fabricated in silicon and measures 20x15\,mm.
 The reactor consists of two gas inlets, a gas outlet, a reactor volume and a capillary used for probing the gas from the reactor volume.
-The reactor volume is 3\,$\mu$m deep and 1 cm in diameter resulting in a 240\,nL volume.
+The reactor volume is 3\,$\mu$m deep and 1 cm in diameter corresponding to a 240\,nL volume.
 The two gas inlets are combined on the chip where the inlet gases mix by diffusion.
-The capillary is designed such that approximately $3\cdot10^{14}$\,molecules$\cdot$s$^{-1}$ is probed from the reactor volume.
-Any surplus of gas from the two inlets that does not enter the reactor volume is directed through the outlet into a turbo pump.
-The design ensures that all molecules entering the reactor volume hence exposed to the catalyst under investigation is detected giving the system high sensitivity.
+The capillary is designed such that approximately $3\cdot10^{14}$\,molecules$\cdot$s$^{-1}$ is probed from the reactor volume when operated at 1\,bar.
+Any surplus of gas from the two inlets that does not enter the reactor volume is directed through the outlet to a turbo pump.
+The design ensures that all molecules or atoms entering the reactor volume, hence exposed to the catalyst under investigation, is detected by mass spectrometry ensuring high sensitivity.
 
@@
 The two gas inlets on the microreactor chip is connected to a gas handling system.
-A total of 6 gases with accompanying flow controllers are used to control the inlet gas.
+A total of 6 gases with accompanying flow controllers are used to control the inlet gas flow to the microreactor.
 Currently, the system is configured in a 4+2 setup where 4 gases are connected to the one inlet and to gases on the other inlet.
@@
 The time of flight equipment used for detection of gas molecules flowed through the capillary of the microreactor is designed as an orthogonal mass spectrometer.
-Ionized ions enter the source through a series of Einzel lenses used for focusing the beam minimizing divergence.
-In the source they are pushed into the flight tube by an the initial push voltage, V$_p$.
+The TOF-MS is assembled from modules purchased from Jordan TOF Products, Inc.
+
+Ionized ions enter the source through a series of entry Einzel lenses used for focusing the beam hence minimizing divergence.
+In the source the beam is pushed into the flight tube by an the initial repelling push voltage, V$_p$.
 The ions are further accelerated from ground potential to the liner potential, V$_L$, which is the drift voltage of the flight tube.
-At the end of the flight tube a reflectron is installed which have two primary purposes.
-The effective drift length is increased hence increasing resolution of the equipment.
+At the end of the flight tube a reflectron is installed which has two primary purposes.
+The effective drift length is increased hence increasing resolution of the TOF-MS.
 The reflectron also works as a focusing lens compensating for any initial velocity dispersion of the ions, i.e.
 ions with an initial higher velocity will have an increased flight length compared to slower ions.
-The microchannel plate (MCP) used for detection is placed in the focal point of the reflectron giving maximum compensation for initial velocity dispersion.
+The microchannel plate (MCP) used for ion detection is placed in the focal point of the reflectron giving maximum compensation for initial velocity dispersion.
 The theoretical resolution of the equipment is $\Delta$m/m$\sim$4000.
@@
 In Figure \ref{fig:untreated_data} an example spectrum of a methanol and atmospheric air mixture is shown.
-Here both the high resolution is demonstrated by the resolved methanol and molecular which has a mass difference of 43\,milliamu.
+Here the high resolution of the TOF-MS is demonstrated by resolution of methanol (CH$_3$OH) and molecular oxygen (O$_2$) which have a mass difference of 43\,milliamu.
 \begin{figure}
@@
 Subfigures show the three different regions of the spectrum.
-From the first subfigure a delay of the approximately 150\,ns can be seen which is due to delays in cables and rise time of the pulser.
+From the first subfigure a delay of the approximately 150\,ns can be seen which is due to delays in cables and the rise time of the repeller pulser.
 From the center subfigure it is evident that 1\,amu corresponds to approximately 350\,ns difference in flight time in our system.
-From the last subfigure the a zoom of the methanol and molecular oxygen (43\,milliamu mass difference) region is shown.\label{fig:untreated_data}}%
+From the last subfigure a zoom of the methanol and molecular oxygen (43\,milliamu mass difference) region is shown.\label{fig:untreated_data}}%
 \end{figure}
@@
 \subsubsection{Ionization of gas}
-As ionization source of the gas flow from the microreactor capillary an modified nude UHV Bayard-Alpert ion gauge is used.
-Approximately 3\,A is run through the filament resulting in approximately 10\,mA emission current.
+As ionization source of the gas flow from the microreactor capillary a modified nude UHV Bayard-Alpert ion gauge is used.
+Approximately 3\,A is run through the filament resulting in 10\,mA emission current.
 The grid is biased approximately 40\,V negative compared to the filament to accelerate electrons emitted from the filament towards the grid.
-Contrary to standard operation of a ion gauge the collector in the center of the grid is short-circuited to grid to ensure homogeneous field distribution within the grid.
-To allow ionized ions to escape from the grid the lid of the grid have been removed.
+Contrary to standard operation of a ion gauge the collector in the center of the grid is short-circuited to the grid ensuring homogeneous field distribution within the grid.
+To allow ionized ions to escape from the gauge the lid of the grid has been removed \cite{Nottingham1955}.
 Using this configuration approximately half of the ionized ions are expected to leave the ionization gauge.
-The entire construction is placed in a nozzle which is differentially pumped.
-Large amounts of gases can hence be dosed locally around the ion gauge while still maintaining a low pressure in the source region of the TOF.
+The entire construction is placed in a nozzle which is differentially pumped by a turbo pump.
+Large amounts of gas can hence be dosed locally around the ion gauge while still maintaining a low pressure in the source region of the TOF-MS.
 The nozzle is essential in the setup to avoid high pressure in the source region resulting in a increase in dead counts on the MCP thus decreasing the noise to signal ratio of the recorded signal.
@@
 \subsubsection{Data treatment}
+A raw data plotted with accompanying gaussian fits are shown in Figure \ref{fig:gaussian_fit}.
 \begin{figure}
  \includegraphics[width=14cm]{ammonia_OH_gauss_fit.png}%
- \caption{Example of Gaussion fit to a double peak. Each gaussion yields the area of the respective component.\label{fig:gaussian_fit}}%
+ \caption{Example of two gaussian fits to a double peak consisting of NH$_{3}^{+}$ and OH$^{-}$ both at approximately 17\,amu demonstrating the resolution of the TOF-MS.
+The entire graph section represents a mass difference of 100\,m-amu.\label{fig:gaussian_fit}}%
+\end{figure}
+The TOF-MS has furthermore the advantage of a high dynamic range compared to eg.
+a QMS.
+In Figure \ref{fig:dynamic_range} raw data from water, hydrogen and oxygen is shown.
+Without changing any the MCP voltage all the peaks are clearly visible although the ratio of the oxygen to water amplitude is roughly a factor of 4000.
+\begin{figure}
+ \includegraphics[width=14cm]{dynamic_range.png}%
+ \caption{Gaussian fits to three different mass to charge ratios from the same mass spectrum.
+As seen from the response a high dynamic range of the TOF-MS all yielding good gaussian fits.
+The TOF-MS can hence be used to monitor both very small and very large signal masses with high time resolution.\label{fig:dynamic_range}}%
 \end{figure}
@@
 \section{Oxidation of ammonia}
-To demonstrate the system capability ammonia oxidation on platinum thin films have been used as a test reaction. The catalytic oxidation of ammonia can proceed in primarily three different routes.
+To demonstrate the system capability ammonia oxidation on platinum thin films has been used as test reaction. The catalytic oxidation of ammonia can proceed along primarily three different routes.
 \begin{equation}
@@
 \end{equation}
-For a clean combustion reaction pathway \ref{eq:Pt_clean_combustion} is preferred.
-This system is, however, difficult to monitor by a QMS due to the overlap of NH$_3$ and OH$^-$ which is a cracking product from H$_2$O.
-Specifically, hydroxyls (OH$^{+}$) from cracking of trace water in the system and the primary peak of ammonia (NH$_{3}^{+}$) is both detected at m/q = 17 in a QMS.
-The mass resolution of a QMS is typically not adequate to separate the two contributions.
-Often a mass without cracking from either products or residue gas in the system is used to be able to detect the amount of ammonia and water.
-In the case of ammonia m/q=15 or m/q=8.5 is typically chosen.
+All of these systems are difficult to analyze both qualitatively and quantitatively by a QMS due to the overlap of NH$_3$, which is a reactant, and OH$^-$ which is a cracking product from H$_2$O, which is a product from the combustion.
+Specifically, hydroxyls (OH$^{+}$) from cracking of trace water in the system and the combustion reaction and the primary peak of ammonia (NH$_{3}^{+}$) is both detected at m/q$\simeq$17 in a QMS.
+The low mass resolution of a QMS is typically not adequate to separate the two contributions resulting i difficult analysis.
+Often a charge to mass ratio without cracking from either products or residue gas in the system is used to be able to detect the amount of ammonia and water.
+In the case of ammonia, m/q=15 or m/q=8.5 is typically chosen.
 The monitoring of other than the primary mass to charge ratio due to mass overlap is generally not wanted due to a lower signal to noise ratio of cracking masses.
 This in turns affect the detection limit of the given mass.
-Due the acquisition of entire mass spectra from mass instead of monitoring of individual masses the TOF-MS does is not limited to cracking masses resulting in higher signal to noise ratio spectra.
+Due the acquisition of entire mass spectra with high time resolution instead of monitoring individual masses by QMS the TOF-MS is not limited to unique signature masses resulting in higher signal to noise ratio spectra.
 \begin{figure}
@@
 Hereafter the temperature is increased while TOF spectra are acquired.
-Spectra were acquired from triggering of the acceleration pulse up to 25\,$\mu$s of flight time corresponding to 70 amu in our system.
+Spectra were acquired from triggering of the acceleration pulse up to 25\,$\mu$s of flight time corresponding to a maximum of 70 amu in our system.
 
 For ammonia oxidation both N$_2$O (m/q = 44), NO (m/q = 30) and NO$_2$ (m/q = 46) are of interest.
-
-\begin{figure}
- \includegraphics[width=14cm]{dynamic_range.png}%
- \caption{Gaussian fits to three different mass to charge ratios from the same mass spectrum.
-As seen from the response a high dynamic range of the TOF-MS all yielding good gaussian fits.
-The TOF-MS can hence be used to monitor both very small and very large signal masses with high time resolution.\label{fig:dynamic_range}}%
-\end{figure}
 

### 2012-03-27 paper.tex
Changes before Robert's first readthrough

@@
 \author{....}
-\affiliation{CINF, Department of Physics...}
+\affiliation{Department of Physics, Danish National Research Foundation's Center for Individual Nanoparticle Functionality (CINF), Technical University of Denmark, Building 312, DK-2800 Kgs.
+Lyngby, Denmark}
 \author{O. Hansen}
-\affiliation{CINF, Department of Micro- and Nanotechnology}
+\affiliation{Department of Micro- and Nanotechnology, Technical University of Denmark, DTU Nanotech Building 345 East, DK-2800 Kgs. Lyngby, Denmark}
 \author{I. Chorkendorff}
 \email[]{ibchork@fysik.dtu.dk}
-\affiliation{CINF, Department of Physics...}
+\affiliation{Department of Physics, Danish National Research Foundation's Center for Individual Nanoparticle Functionality (CINF), Technical University of Denmark, Building 312, DK-2800 Kgs.
+Lyngby, Denmark}
 %\homepage[]{Your web page}
@@
 The system design is superior to conventional batch and flow reactors not only due to the high sensitivity, fast temperature response and high mass resolution but also allows to measure on wide mass ranges (0--5000\,amu in the current configuration).
-As demonstration of the system we here present data from ammonia oxidation on platinum thin films showing resolved spectra of OH$^{-}$ and NH$_{3}^{+}$.
+As demonstration of the system we here present data from ammonia oxidation on platinum thin films showing resolved spectra of OH$^{+}$ and NH$_{3}^{+}$.
 \end{abstract}
@@
 The QMS is additionally subject to a low mass range (typically up to $\sim$500\,amu) limiting general use.
-Furthermore, QMSs are typically operated by logging a single (or a few) masses as a function of time to increase the time resolution.
+Furthermore, QMSs are typically operated by logging a single (or a few) masses as a function of time to increase time resolution.
 This in turn limits the ability to acquire full mass spectra continuously during the experiment.
@@
 
-\subsection{Microreactor and gas handling}
-
 \subsubsection{The microreactor platform}
@@
 
-\subsubsection{Gas handling}
+\subsubsection{Gas handling for the microreactor}
 The two gas inlets on the microreactor chip is connected to a gas handling system.
@@
 \subsubsection{Data treatment}
-A raw data plotted with accompanying gaussian fits are shown in Figure \ref{fig:gaussian_fit}.
+Raw data plotted with accompanying gaussian fits are shown in Figure \ref{fig:gaussian_fit}.
+Here the closely lying peaks from OH$^{+}$ from cracking of both residue water and water as reaction product and uncombusted NH$_3^{+}$ is shown.
+The ability to separate these contributions substantially simplifies quantification of the ammonia and allows for easier characterization of catalysts.
 \begin{figure}
  \includegraphics[width=14cm]{ammonia_OH_gauss_fit.png}%
- \caption{Example of two gaussian fits to a double peak consisting of NH$_{3}^{+}$ and OH$^{-}$ both at approximately 17\,amu demonstrating the resolution of the TOF-MS.
+ \caption{Example of two gaussian fits to a double peak consisting of NH$_{3}^{+}$ and OH$^{+}$ both at approximately 17\,amu demonstrating the resolution of the TOF-MS.
 The entire graph section represents a mass difference of 100\,m-amu.\label{fig:gaussian_fit}}%
 \end{figure}
-The TOF-MS has furthermore the advantage of a high dynamic range compared to eg.
-a QMS.
-In Figure \ref{fig:dynamic_range} raw data from water, hydrogen and oxygen is shown.
-Without changing any the MCP voltage all the peaks are clearly visible although the ratio of the oxygen to water amplitude is roughly a factor of 4000.
+In Figure \ref{fig:dynamic_range} raw data from water, hydrogen and oxygen from three different regions is shown illustrating the dynamic range of the TOF-MS.
+At constant MCP voltage all the peaks are clearly visible although the ratio of the oxygen to water amplitude is $\sim$400.
 \begin{figure}
@@
 \end{figure}
+The dynamic range of the TOF-MS is hence comparable to the dynamic range offered by a QMS at constant preamplifier range.
+From Figure \ref{fig:dynamic_range} the dynamic range is estimated to $\sim$1000.
+Her ville jeg gerne skrive noget mere.
+Nogen ideer...?
 
@@
 \end{equation}
-All of these systems are difficult to analyze both qualitatively and quantitatively by a QMS due to the overlap of NH$_3$, which is a reactant, and OH$^-$ which is a cracking product from H$_2$O, which is a product from the combustion.
-Specifically, hydroxyls (OH$^{+}$) from cracking of trace water in the system and the combustion reaction and the primary peak of ammonia (NH$_{3}^{+}$) is both detected at m/q$\simeq$17 in a QMS.
-The low mass resolution of a QMS is typically not adequate to separate the two contributions resulting i difficult analysis.
-Often a charge to mass ratio without cracking from either products or residue gas in the system is used to be able to detect the amount of ammonia and water.
+All of these systems are difficult to analyze both qualitatively and quantitatively by due to the overlap of NH$_3$, which is a reactant, and OH$^+$ originating from cracking of H$_2$O, which is a product from the combustion, and cracking from water in the residue gas.
+Specifically, hydroxyls (OH$^{+}$) from cracking of trace water in the system and the combustion reaction and the primary peak of ammonia (NH$_{3}^{+}$) is both detected at m/q$\simeq$17.
+Without adequate mass resolution is not possible to separate the two contributions resulting in difficult analysis.
+Often a charge to mass ratio without cracking from either products or residue gas in the system is used to quantify the amount of ammonia and water.
 In the case of ammonia, m/q=15 or m/q=8.5 is typically chosen.
-The monitoring of other than the primary mass to charge ratio due to mass overlap is generally not wanted due to a lower signal to noise ratio of cracking masses.
+The monitoring of other than the primary mass to charge ratio, which in the case of ammonia is m/q=17, due to mass overlap is generally not wanted due to a lower signal to noise ratio of cracking masses.
 This in turns affect the detection limit of the given mass.
-Due the acquisition of entire mass spectra with high time resolution instead of monitoring individual masses by QMS the TOF-MS is not limited to unique signature masses resulting in higher signal to noise ratio spectra.
+Due the acquisition of entire mass spectra with high mass resolution instead of monitoring individual masses by the TOF-MS is not limited to unique signature masses resulting in higher signal to noise ratio spectra.
+
+At experiment start the microreactor is equilibrated with NH$_3$ and O$_2$ in a 5:3 stoichiometry (did we run at stoichiometry??).
+After equilibration the temperature is increased in steps from room temperature til 190\,$^{\circ}$C.
+The gas composition in the microreactor is continuously probed by the TOF-MS which is connected to the capillary of the microreactor.
 \begin{figure}
@@
 As the temperature is increased ammonia is oxidized to H$_2$O and N$_2$.
-Furthermore, the OH and NH$_3$ signal is anticorrelated demonstrating the ability to resolve these masses.\label{fig:ammonia_reactivity}}%
+Furthermore, the OH and NH$_3$ signal is anticorrelated demonstrating the ability to resolve these two close lying masses.\label{fig:ammonia_reactivity}}%
 \end{figure}
-In Figure \ref{fig:ammonia_reactivity} a number of masses as a function of time are shown.
-At experiment start the microreactor is equilibrated with a stoichiometric mix of NH$_3$ and O$_2$ (3:4).
-Hereafter the temperature is increased while TOF spectra are acquired.
-Spectra were acquired from triggering of the acceleration pulse up to 25\,$\mu$s of flight time corresponding to a maximum of 70 amu in our system.
+In Figure \ref{fig:ammonia_reactivity} the integrated N$_2$, NH$_3$, H$_2$O, O$_2$ and OH peaks acquired from the raw TOF-MS spectrum as a function of temperature are shown.
+At each individual temperature step a mass scan is performed from the triggering of the acceleration pulse up to 25\,$\mu$s of flight time corresponding to a maximum of 70 amu.
+As seen from Figure \ref{fig:ammonia_reactivity} the combustion of NH$_3$ increases substantially at approximately 140\,$^{\circ}$C.
+The combustion of ammonia to molecular nitrogen and water at this temperature agrees well with literature \cite{Imbihl2007,Zeng2009}.
+In Figure \ref{fig:ammonia_reactivity} an anticorrelation between OH$^{+}$ and NH$_3^+$ is seen.
+The inverse relation between these two masses suggests that these peaks are resolved in the mass spectrum which is further strengthened by the correlation between H$_2$O$^{+}$.
 
-For ammonia oxidation both N$_2$O (m/q = 44), NO (m/q = 30) and NO$_2$ (m/q = 46) are of interest.
+%For ammonia oxidation both N$_2$O (m/q = 44), NO (m/q = 30) and NO$_2$ (m/q = 46) are of interest.
 
 \section{Summary}
+We have demonstrated a combined microreactor and TOF-MS system which can be employed to test and characterize model heterogeneous catalysts.
+An automated gas handling system is used to flow gas over a catalyst in the reaction chamber of the microreactor from where gases can be probed.
+The reactor gas composition is probed by a microreactor capillary which is analyzed by a TOF-MS combining high sensitivity and high mass resolution.
+
+As a demonstration of the system ammonia oxidation on platinum thin films was performed.
+The ability to resolve OH$^{+}$ and NH$_3^+$ was demonstrated which is separated by 23\,milli-amu.
+The resolution of reactants and products enables simple and straightforward quantification of the ammonia and water signal.
+This greatly simplifies the analysis compared to conventional QMSs used for gas analysis.
+The setup is furthermore superior to conventional QMSs where the mass range is limited to $\sim$500\,amu.
 
@@
 % Create the reference section using BibTeX:
-\bibliographystyle{abbrv}
+%\bibliographystyle{abbrv}
 %\bibliographystyle{alpha}
 %\bibliographystyle{plain}
+%\bibliographystyle{unsrt}
 \bibliography{literature}

### 2012-03-27 paper.tex
Various corrections
A number of suggestions and corrections was put into the
paper. The corrections are not clearly marked, need to
look at the diff.... sorry....

@@
 \author{R. Jensen}
-\author{....}
+\author{M. K. Christensen}
 \affiliation{Department of Physics, Danish National Research Foundation's Center for Individual Nanoparticle Functionality (CINF), Technical University of Denmark, Building 312, DK-2800 Kgs.
 Lyngby, Denmark}
+\author{T. Pedersen}
 \author{O. Hansen}
@@
 Typically, quadrupole mass spectrometers (QMSs) are used in low pressure regimes to analyze gas composition while gas chromatographs are used for high pressure measurements.
-The QMS, however, suffer from a low mass resolution ($\Delta$m/m$\sim$200) which makes analysis of complicated spectra difficult and cumbersome.
-The QMS is additionally subject to a low mass range (typically up to $\sim$500\,amu) limiting general use.
+The QMS, however, suffer from a low mass resolution ($\Delta$m/m$\sim$m up to m$\sim$200) which makes analysis of complicated spectra difficult and cumbersome.
+The QMS is additionally subject to a low mass range (typically $\sim$100-200\,amu) limiting general use.
 Furthermore, QMSs are typically operated by logging a single (or a few) masses as a function of time to increase time resolution.
-This in turn limits the ability to acquire full mass spectra continuously during the experiment.
+This in turn limits the ability to acquire full mass spectra continuously during the experiment and thus the operator before the experiments needs to decide which masses is interesting, and thus might miss interesting features in other masses.
 Gas chromatographs have inherently low time resolution which make them unsuitable for fast time response measurements as in the case of microreactors and is in general difficult to use as mass spectrometers.
-As an alternative to the gas chromatography or QMSs, time of flight mass spectrometers (TOF-MS) offer both high mass resolution ($\Delta$m/m$>$400) and fast acquisition of full mass spectra ($>$1\,Hz) along with mass range only limited by the detector.
-For a typical microchannel plate (MCP) a mass range of (0--5000\,amu) can be obtained.
+As an alternative to the gas chromatography or QMSs, time of flight mass spectrometers (TOF-MS) offer both high mass resolution ($\Delta$m/m$>$1000) and fast acquisition of full mass spectra ($>$1\,Hz) along with mass range only limited by the detector.
+For a reasonobly good microchannel plate (MCP) a mass range of 0--5000\,amu can be obtained.
 Until now, to our knowledge, the testing of catalysts in a microreactor with subsequent gas analysis by a TOF-MS have not been demonstrated.
@@
 The two gas inlets are combined on the chip where the inlet gases mix by diffusion.
-The capillary is designed such that approximately $3\cdot10^{14}$\,molecules$\cdot$s$^{-1}$ is probed from the reactor volume when operated at 1\,bar.
+The capillary is designed such that approximately $3\times10^{14}$\,molecules$\cdot$s$^{-1}$ is probed from the reactor volume when operated at 1\,bar.
 Any surplus of gas from the two inlets that does not enter the reactor volume is directed through the outlet to a turbo pump.
@@
 \subsection{Time of flight}
+SKAL VI SKRIVE LIDT OM SELVE KAMMERET (baggrundstryk, pumpetyper, etc...)
+
 The time of flight equipment used for detection of gas molecules flowed through the capillary of the microreactor is designed as an orthogonal mass spectrometer.
@@
 Ionized ions enter the source through a series of entry Einzel lenses used for focusing the beam hence minimizing divergence.
-In the source the beam is pushed into the flight tube by an the initial repelling push voltage, V$_p$.
-The ions are further accelerated from ground potential to the liner potential, V$_L$, which is the drift voltage of the flight tube.
+In the source the beam is pushed into the flight tube by an the initial repelling push voltage, $V_p$.
+The ions are further accelerated from ground potential to the liner potential, $V_L$, and the drift velocity of an ion starting exactly from the center of the accelration region is thus $V_L + V_p/2$.
 At the end of the flight tube a reflectron is installed which has two primary purposes.
@@
 In Figure \ref{fig:untreated_data} an example spectrum of a methanol and atmospheric air mixture is shown.
-Here the high resolution of the TOF-MS is demonstrated by resolution of methanol (CH$_3$OH) and molecular oxygen (O$_2$) which have a mass difference of 43\,milliamu.
+Here the high resolution of the TOF-MS is demonstrated by resolving of methanol (CH$_3$OH) and molecular oxygen (O$_2$) which have a mass difference of 43\,milliamu.
 \begin{figure}
@@
 Subfigures show the three different regions of the spectrum.
-From the first subfigure a delay of the approximately 150\,ns can be seen which is due to delays in cables and the rise time of the repeller pulser.
-From the center subfigure it is evident that 1\,amu corresponds to approximately 350\,ns difference in flight time in our system.
-From the last subfigure a zoom of the methanol and molecular oxygen (43\,milliamu mass difference) region is shown.\label{fig:untreated_data}}%
+From the first subfigure a delay of approximately 150\,ns can be seen which is due to delays in cables and the rise time of the repeller pulser.
+In the center subfigure the extremely good seperation between seperate masses is shown.
+It is evident that 1\,amu corresponds to approximately 350\,ns difference in flight time in our system in the mass regime around 20\,amu.
+In the last subfigure a zoom of the methanol and molecular oxygen (43\,milliamu mass difference) region is shown.\label{fig:untreated_data}}%
 \end{figure}
@@
 Large amounts of gas can hence be dosed locally around the ion gauge while still maintaining a low pressure in the source region of the TOF-MS.
-The nozzle is essential in the setup to avoid high pressure in the source region resulting in a increase in dead counts on the MCP thus decreasing the noise to signal ratio of the recorded signal.
+The nozzle is essential in the setup to avoid high pressure in the acceleration region and drift tube resulting in an increase in dead counts on the MCP thus decreasing the signal-to-noise ratio of the recorded signal.
 
@@
  \includegraphics[width=14cm]{ammonia_OH_gauss_fit.png}%
- \caption{Example of two gaussian fits to a double peak consisting of NH$_{3}^{+}$ and OH$^{+}$ both at approximately 17\,amu demonstrating the resolution of the TOF-MS.
+ \caption{Example of two gaussian fits (dashed red lines) and the sum of the two fits (green solid line) to a double peak consisting of NH$_{3}^{+}$ and OH$^{+}$ both at approximately 17\,amu demonstrating the resolution of the TOF-MS.
 The entire graph section represents a mass difference of 100\,m-amu.\label{fig:gaussian_fit}}%
@@
  \includegraphics[width=14cm]{dynamic_range.png}%
- \caption{Gaussian fits to three different mass to charge ratios from the same mass spectrum.
+ \caption{Gaussian fits to three different mass to charge ratios from the same mass spectrum (integrated area indicated in each panel).
 As seen from the response a high dynamic range of the TOF-MS all yielding good gaussian fits.
@@
 \end{figure}
-The dynamic range of the TOF-MS is hence comparable to the dynamic range offered by a QMS at constant preamplifier range.
-From Figure \ref{fig:dynamic_range} the dynamic range is estimated to $\sim$1000.
-Her ville jeg gerne skrive noget mere.
-Nogen ideer...?
+In reallity the dynamic range is limited mostly by the data aquisition hardware as well as the quality of the ion-source.
+Even with our very simple home-build ionization source and a rather modest 8-bit digitizer, the dynamic range is from Figure~\ref{fig:dynamic_range} estimated to be $\sim$1000 using an integration time of $\sim5\,$s.
+The dynamic range of the TOF-MS is hence comparable to the dynamic range offered by a QMS at constant preamplifier range, while covering a much larger mass range.
+
+SKAL VI SKRIVE NOGET OM FLYVETID-TIL-MASSE OMREGNING?
 
@@
 \end{equation}
-All of these systems are difficult to analyze both qualitatively and quantitatively by due to the overlap of NH$_3$, which is a reactant, and OH$^+$ originating from cracking of H$_2$O, which is a product from the combustion, and cracking from water in the residue gas.
+All of these systems are difficult to analyze both qualitatively and quantitatively due to the overlap of NH$_3$, which is a reactant, and OH$^+$ originating from cracking of H$_2$O, which is a product from the combustion and is a part of the residue gas.
 Specifically, hydroxyls (OH$^{+}$) from cracking of trace water in the system and the combustion reaction and the primary peak of ammonia (NH$_{3}^{+}$) is both detected at m/q$\simeq$17.
-Without adequate mass resolution is not possible to separate the two contributions resulting in difficult analysis.
+Without adequate mass resolution it is not possible to separate the two contributions resulting in difficult analysis.
 Often a charge to mass ratio without cracking from either products or residue gas in the system is used to quantify the amount of ammonia and water.
-In the case of ammonia, m/q=15 or m/q=8.5 is typically chosen.
-The monitoring of other than the primary mass to charge ratio, which in the case of ammonia is m/q=17, due to mass overlap is generally not wanted due to a lower signal to noise ratio of cracking masses.
-This in turns affect the detection limit of the given mass.
-Due the acquisition of entire mass spectra with high mass resolution instead of monitoring individual masses by the TOF-MS is not limited to unique signature masses resulting in higher signal to noise ratio spectra.
+In the case of ammonia, m/q=15 or m/q=8.5 is typically chosen since water does not contribute to these masses.
+However both of these masses contains only a very small fraction of the main peak, since it involves either the loss of two hydrogen atoms or a double charged ammonia molecule, both processes have very low yields.
+Thus the measurement of these masses have a very poor signal to noise ratio, making measurements on ammonia very difficult with tradition mass spectrometry methods.
 
@@
 In Figure \ref{fig:ammonia_reactivity} an anticorrelation between OH$^{+}$ and NH$_3^+$ is seen.
-The inverse relation between these two masses suggests that these peaks are resolved in the mass spectrum which is further strengthened by the correlation between H$_2$O$^{+}$.
+The inverse relation between these two masses can only be measured because these peaks are resolved in the mass spectrum.
+As expected a strong correlation between H$_2$O$^{+}$ and OH$^+$ is seen.
 
@@
 As a demonstration of the system ammonia oxidation on platinum thin films was performed.
-The ability to resolve OH$^{+}$ and NH$_3^+$ was demonstrated which is separated by 23\,milli-amu.
+The ability to resolve OH$^{+}$ and NH$_3^+$ which is separated by 23\,milli-amu was demonstrated.
 The resolution of reactants and products enables simple and straightforward quantification of the ammonia and water signal.

### 2012-03-28 paper.tex
Incoporation of Robert's changes

@@
 
-\title{High Resolution Time of Flight Mass Spectrometer for Measuring Products in Heterogenous Catalysis in Higly Sensitive Microreactors} %Title of paper
+\title{High Mass Resolution Time of Flight Mass Spectrometer for Measuring Products in Heterogeneous Catalysis in Highly Sensitive Microreactors} %Title of paper
 
@@
 \author{R. Jensen}
-\author{M. K. Christensen}
+\author{M.K. Christensen}
 \affiliation{Department of Physics, Danish National Research Foundation's Center for Individual Nanoparticle Functionality (CINF), Technical University of Denmark, Building 312, DK-2800 Kgs.
@@
 We demonstrate a combined microreactor and time of flight system for testing and characterization of heterogeneous catalyst with high resolution mass spectrometry and high sensitivity.
-Catalyst testing is performed in microreactors which have high sensitivity and fast thermal response.
-Gas analysis is performed with a time of flight mass spectrometer with a modified nude Bayard-Alpert ionization gauge as gas ionization source with a mass resolution of $\Delta$m/m$>$2500.
-The system design is superior to conventional batch and flow reactors not only due to the high sensitivity, fast temperature response and high mass resolution but also allows to measure on wide mass ranges (0--5000\,amu in the current configuration).
+Catalyst testing is performed in silicon-based microreactors which have high sensitivity and fast thermal response.
+Gas analysis is performed with a time of flight mass spectrometer with a modified nude Bayard-Alpert ionization gauge as gas ionization source.
+The mass resolution of the time of flight mass spectrometer using the ion gauge as ionization source is estimated to $\Delta$m/m$>$2500.
+The system design is superior to conventional batch and flow reactors with accompanying product detection by quadrupole mass spectrometry or gas chromatopgraphy not only due to the high sensitivity, fast temperature response, high mass resolution and fast acquisition time but also allows to measure on wide mass ranges (0--5000\,amu in the current configuration).
 As demonstration of the system we here present data from ammonia oxidation on platinum thin films showing resolved spectra of OH$^{+}$ and NH$_{3}^{+}$.
@@
 In heterogeneous catalysis the optimization and development of equipment is important both to minimize the cost of equipment but also to be able to study complicated systems.
-As a platform for testing heterogeneous catalysts microfabricated reactors or microreactors have been found suitable due to both high surface-to-volume ratio, fast temperature response and minimization of thermal and concentration gradients.
-Such a platform have been developed in our department \cite{Henriksen2009}.
+As a platform for testing heterogeneous catalysts microfabricated reactors or microreactors have been found suitable due to both high surface-to-volume ratio, fast temperature response and minimization of thermal and concentration gradients\cite{Jensen2001,Jaehnisch2004}.
+Such a platform have been developed previously to test and characterize model catalysts\cite{Henriksen2009}.
 However, a suitable reactor platform is only part of the task; reactant and product detection and characterization is essential to determine catalyst performance.
@@
 Furthermore, QMSs are typically operated by logging a single (or a few) masses as a function of time to increase time resolution.
-This in turn limits the ability to acquire full mass spectra continuously during the experiment and thus the operator before the experiments needs to decide which masses is interesting, and thus might miss interesting features in other masses.
-Gas chromatographs have inherently low time resolution which make them unsuitable for fast time response measurements as in the case of microreactors and is in general difficult to use as mass spectrometers.
-As an alternative to the gas chromatography or QMSs, time of flight mass spectrometers (TOF-MS) offer both high mass resolution ($\Delta$m/m$>$1000) and fast acquisition of full mass spectra ($>$1\,Hz) along with mass range only limited by the detector.
-For a reasonobly good microchannel plate (MCP) a mass range of 0--5000\,amu can be obtained.
-Until now, to our knowledge, the testing of catalysts in a microreactor with subsequent gas analysis by a TOF-MS have not been demonstrated.
-Here we describe a microreactor and TOF-MS system which combines the high sensitivity of microreactors and the high mass resolution TOF-MSs for testing and characterizing heterogeneous catalysts.
+This is at the expense of acquisition of full mass spectra continuously during the experiment limiting operation by potentially losing interesting features in other masses not monitored.
+Gas chromatographs have inherently low time resolution which make them unsuitable for fast time response measurements as in the case of microreactors and is in general difficult to use as mass spectrometers due to the difficult interpretation of complex mixtures.
+As an alternative to the gas chromatography or QMSs, time of flight mass spectrometers (TOF-MS) offer both high mass resolution ($\Delta$m/m$>$1000), fast acquisition of full mass spectra ($>$1\,Hz) and mass range only limited by the detector.
+For a reasonably good microchannel plate (MCP) a mass range of 0--5000\,amu can be obtained.
+
+Typically TOF-MS in heterogeneous catalysis is used as a surface analytic tool, i.e.
+TOF-SIMS\cite{Benninghoven1994,DeSmet1998,Grams2004,Johnson2010}.
+Measurements of reactants and products on heterogeneous catalysts by TOF-MS have previously been performed\cite{Levy1963,Okumura2007} but, until now, to our knowledge, the testing of catalysts in a microreactor with subsequent gas analysis by a TOF-MS have not been demonstrated.
+Here we describe a microreactor and TOF-MS system which combines the high sensitivity of microreactors and the high mass resolution TOF-MSs for testing and characterizing of heterogeneous catalysts.
 
 \section{System design}
-The microreactor as a reactor and TOF as a mass spectrometer enables high sensitivity reactivity measurements of the catalyst under investigation combined with high resolution mass spectrometry.
-The catalyst under investigation is deposited in the microreactor from where reaction products are detected with time of flight mass spectrometry.
+The microreactor as a reactor platform and TOF-MS as mass spectrometer enables high sensitivity reactivity measurements of the catalyst under investigation combined with high resolution mass spectrometry.
+
+The catalyst under investigation is deposited in the microreactor reactor volume by e.g.
+evaporation\cite{Henriksen2009}, drop casting\cite{Vesborg2010} or gas aggregation formed size-selected nanoparticles.
+The gas composition in the microreactor reactor volume is detected by the TOF-MS which is connected to the microreactor capillary outlet.
 A schematic of the entire setup is shown in Figure \ref{fig:TOF_microreactor}.
@@
 
-\subsubsection{The microreactor platform}
-Catalyst characterization and performance evaluation was performed in a microreactor platform \cite{Henriksen2009}.
-The microreactors are fabricated in silicon and measures 20x15\,mm.
-The reactor consists of two gas inlets, a gas outlet, a reactor volume and a capillary used for probing the gas from the reactor volume.
-The reactor volume is 3\,$\mu$m deep and 1 cm in diameter corresponding to a 240\,nL volume.
+\subsection{The microreactor platform}
+Catalyst characterization and performance evaluation is performed in a microreactor platform \cite{Henriksen2009}.
+The microreactors are silicon-based and measures 20x15\,mm.
+The reactor consists of two gas inlets, a gas outlet, a reactor volume and a capillary used to restrict the gas flow from the reactor volume.
+The reactor volume is 3\,$\mu$m deep and 1 cm in diameter corresponding to a 236\,nL volume.
 The two gas inlets are combined on the chip where the inlet gases mix by diffusion.
 The capillary is designed such that approximately $3\times10^{14}$\,molecules$\cdot$s$^{-1}$ is probed from the reactor volume when operated at 1\,bar.
-Any surplus of gas from the two inlets that does not enter the reactor volume is directed through the outlet to a turbo pump.
+Any surplus of gas from the two inlets that does not enter the reactor volume is directed through an outlet to a turbo pump.
 The design ensures that all molecules or atoms entering the reactor volume, hence exposed to the catalyst under investigation, is detected by mass spectrometry ensuring high sensitivity.
 
-The microreactor is heated by joule heating of a 50 nm platinum strip evaporated through a shadow mask on the backside of the chip.
+The microreactor is heated by joule heating of a 50\,nm platinum strip evaporated through a shadow mask on the backside of the chip.
 The heating element is contacted by two pogo pins which is connected to a power supply.
-Additionally, two extra contacts are placed on the chip which facilitates 4 wire measurement of the resistance of the heating element.
-The heating strip is hence used as a resistance temperature detector (RTD) to monitor the temperature of the chip.
+Additionally, two extra contacts are placed on the chip which facilitates a 4 wire measurement of the resistance of the heating element.
+The heating strip in this way be used as a resistance temperature detector (RTD) to determine the temperature of the chip.
 At the current configuration temperatures from room temperature to approximately 450\,$^{\circ}$C can be reached.
 
-\subsubsection{Gas handling for the microreactor}
+\subsection{Gas handling for the microreactor}
 The two gas inlets on the microreactor chip is connected to a gas handling system.
@@
 Currently, the system is configured in a 4+2 setup where 4 gases are connected to the one inlet and to gases on the other inlet.
-All valves and flow controllers are interfaced to computer enabling remote control of the system and the possibility to run experiments over several days without human intervention.
+All valves and flow controllers are interfaced to computer enabling remote control of the system and the ability to run experiments over several days without human intervention.
 
-\subsection{Time of flight}
-SKAL VI SKRIVE LIDT OM SELVE KAMMERET (baggrundstryk, pumpetyper, etc...)
+\subsection{Time of flight mass spectrometer}
+The time of flight chamber is pumped by a turbo pump and two ion pumps.
+A 120\,l/s ion pump is used to pump the flight tube while a 400\,l/s ion pump and a 450\,l/s turbo pump is used pump down the source region which is mounted on a 8" 4-way cross.
+Opposite the source region of the TOF-MS the pumps are mounted while the two remaining flanges are occupied by the ionization gauge and blanked flange (see Figure~\ref{fig:TOF_microreactor}).
+While idling the pressure in the source region is $\sim1$x$10^{-9}$\,mbar and $\sim2$x$10^{-9}$\,mbar in the flight tube.
 
 The time of flight equipment used for detection of gas molecules flowed through the capillary of the microreactor is designed as an orthogonal mass spectrometer.
-The TOF-MS is assembled from modules purchased from Jordan TOF Products, Inc.
+The TOF-MS is assembled from modules purchased from Jordan TOF Products, Inc and is configured as an orthogonal TOF.
 
@@
 In the source the beam is pushed into the flight tube by an the initial repelling push voltage, $V_p$.
-The ions are further accelerated from ground potential to the liner potential, $V_L$, and the drift velocity of an ion starting exactly from the center of the accelration region is thus $V_L + V_p/2$.
+The ions are further accelerated from ground potential to the liner potential, $V_L$, and the drift velocity of an ion starting exactly from the center of the acceleration region is thus $V_L + V_p/2$.
 At the end of the flight tube a reflectron is installed which has two primary purposes.
@@
 ions with an initial higher velocity will have an increased flight length compared to slower ions.
-The microchannel plate (MCP) used for ion detection is placed in the focal point of the reflectron giving maximum compensation for initial velocity dispersion.
+The MCP used for ion detection is placed in the focal point of the reflectron giving maximum compensation for initial velocity dispersion.
 The theoretical resolution of the equipment is $\Delta$m/m$\sim$4000.
@@
 In Figure \ref{fig:untreated_data} an example spectrum of a methanol and atmospheric air mixture is shown.
-Here the high resolution of the TOF-MS is demonstrated by resolving of methanol (CH$_3$OH) and molecular oxygen (O$_2$) which have a mass difference of 43\,milliamu.
+Here the high resolution of the TOF-MS is demonstrated by resolving methanol (CH$_3$OH) and molecular oxygen (O$_2$) which have a mass difference of 43\,milli-amu.
 \begin{figure}
@@
 Contrary to standard operation of a ion gauge the collector in the center of the grid is short-circuited to the grid ensuring homogeneous field distribution within the grid.
-To allow ionized ions to escape from the gauge the lid of the grid has been removed \cite{Nottingham1955}.
-Using this configuration approximately half of the ionized ions are expected to leave the ionization gauge.
+To allow ionized ions to escape from the gauge the lid of the grid has been removed.
+Using this configuration approximately half of the ionized ions are expected to leave the ionization gauge\cite{Nottingham1955}.
 The entire construction is placed in a nozzle which is differentially pumped by a turbo pump.
@@
 Here the closely lying peaks from OH$^{+}$ from cracking of both residue water and water as reaction product and uncombusted NH$_3^{+}$ is shown.
-The ability to separate these contributions substantially simplifies quantification of the ammonia and allows for easier characterization of catalysts.
+The ability to separate these contributions substantially simplifies quantification of ammonia and allows for easier characterization of catalyst performance.
 \begin{figure}
@@
  \caption{Example of two gaussian fits (dashed red lines) and the sum of the two fits (green solid line) to a double peak consisting of NH$_{3}^{+}$ and OH$^{+}$ both at approximately 17\,amu demonstrating the resolution of the TOF-MS.
-The entire graph section represents a mass difference of 100\,m-amu.\label{fig:gaussian_fit}}%
+The entire graph section represents a mass difference of 100\,milli-amu.\label{fig:gaussian_fit}}%
 \end{figure}
@@
 \end{figure}
-In reallity the dynamic range is limited mostly by the data aquisition hardware as well as the quality of the ion-source.
-Even with our very simple home-build ionization source and a rather modest 8-bit digitizer, the dynamic range is from Figure~\ref{fig:dynamic_range} estimated to be $\sim$1000 using an integration time of $\sim5\,$s.
+In reality the dynamic range is limited mostly by the data acquisition hardware as well as the quality of the ion source.
+Even with our very simple home-built ionization source and a 8-bit digitizer the dynamic range is from Figure~\ref{fig:dynamic_range} estimated to $\sim$1000 using an integration time of $\sim$5\,s.
 The dynamic range of the TOF-MS is hence comparable to the dynamic range offered by a QMS at constant preamplifier range, while covering a much larger mass range.
@@
 In the case of ammonia, m/q=15 or m/q=8.5 is typically chosen since water does not contribute to these masses.
-However both of these masses contains only a very small fraction of the main peak, since it involves either the loss of two hydrogen atoms or a double charged ammonia molecule, both processes have very low yields.
-Thus the measurement of these masses have a very poor signal to noise ratio, making measurements on ammonia very difficult with tradition mass spectrometry methods.
+However, both of these masses contains only a very small fraction of the main peak since it involves either the loss of two hydrogen atoms or a double charged ammonia molecule which are both processes with very low yields.
+The measurement of these masses have a very poor signal to noise ratio making measurements on ammonia very difficult with traditional mass spectrometry methods.
 
@@
 In Figure \ref{fig:ammonia_reactivity} the integrated N$_2$, NH$_3$, H$_2$O, O$_2$ and OH peaks acquired from the raw TOF-MS spectrum as a function of temperature are shown.
-At each individual temperature step a mass scan is performed from the triggering of the acceleration pulse up to 25\,$\mu$s of flight time corresponding to a maximum of 70 amu.
+At each individual temperature step a mass scan is performed from triggering of the acceleration pulse up to 25\,$\mu$s of flight time corresponding to a maximum of 70 amu.
 As seen from Figure \ref{fig:ammonia_reactivity} the combustion of NH$_3$ increases substantially at approximately 140\,$^{\circ}$C.
 The combustion of ammonia to molecular nitrogen and water at this temperature agrees well with literature \cite{Imbihl2007,Zeng2009}.
+
 In Figure \ref{fig:ammonia_reactivity} an anticorrelation between OH$^{+}$ and NH$_3^+$ is seen.
 The inverse relation between these two masses can only be measured because these peaks are resolved in the mass spectrum.
-As expected a strong correlation between H$_2$O$^{+}$ and OH$^+$ is seen.
-
+As expected a strong correlation between H$_2$O$^{+}$ and OH$^+$ is seen as a direct result of water cracking to hydroxyls.
 %For ammonia oxidation both N$_2$O (m/q = 44), NO (m/q = 30) and NO$_2$ (m/q = 46) are of interest.
@@
 %\bibliographystyle{plain}
-%\bibliographystyle{unsrt}
+\bibliographystyle{unsrt}
 \bibliography{literature}

### 2012-03-28 paper.tex
Small corrections

@@
 \begin{abstract}
-We demonstrate a combined microreactor and time of flight system for testing and characterization of heterogeneous catalyst with high resolution mass spectrometry and high sensitivity.
+We demonstrate a combined microreactor and time of flight system for testing and characterization of heterogeneous catalysts with high resolution mass spectrometry and high sensitivity.
 Catalyst testing is performed in silicon-based microreactors which have high sensitivity and fast thermal response.
@@
 The mass resolution of the time of flight mass spectrometer using the ion gauge as ionization source is estimated to $\Delta$m/m$>$2500.
-The system design is superior to conventional batch and flow reactors with accompanying product detection by quadrupole mass spectrometry or gas chromatopgraphy not only due to the high sensitivity, fast temperature response, high mass resolution and fast acquisition time but also allows to measure on wide mass ranges (0--5000\,amu in the current configuration).
+The system design is superior to conventional batch and flow reactors with accompanying product detection by quadrupole mass spectrometry or gas chromatopgraphy not only due to the high sensitivity, fast temperature response, high mass resolution and fast acquisition time of mass spectra but also allows to measure on wide mass ranges (0--5000\,amu in the current configuration).
 As demonstration of the system we here present data from ammonia oxidation on platinum thin films showing resolved spectra of OH$^{+}$ and NH$_{3}^{+}$.
@@
 As a platform for testing heterogeneous catalysts microfabricated reactors or microreactors have been found suitable due to both high surface-to-volume ratio, fast temperature response and minimization of thermal and concentration gradients\cite{Jensen2001,Jaehnisch2004}.
-Such a platform have been developed previously to test and characterize model catalysts\cite{Henriksen2009}.
+Such a platform have been developed previously to test and characterize model catalysts in our department\cite{Henriksen2009}.
 However, a suitable reactor platform is only part of the task; reactant and product detection and characterization is essential to determine catalyst performance.
@@
 Furthermore, QMSs are typically operated by logging a single (or a few) masses as a function of time to increase time resolution.
-This is at the expense of acquisition of full mass spectra continuously during the experiment limiting operation by potentially losing interesting features in other masses not monitored.
+This is at the expense of acquisition of full mass spectra during the experiment limiting operation by potentially losing interesting features in other masses not monitored.
 Gas chromatographs have inherently low time resolution which make them unsuitable for fast time response measurements as in the case of microreactors and is in general difficult to use as mass spectrometers due to the difficult interpretation of complex mixtures.
-As an alternative to the gas chromatography or QMSs, time of flight mass spectrometers (TOF-MS) offer both high mass resolution ($\Delta$m/m$>$1000), fast acquisition of full mass spectra ($>$1\,Hz) and mass range only limited by the detector.
-For a reasonably good microchannel plate (MCP) a mass range of 0--5000\,amu can be obtained.
+As an alternative to gas chromatography or QMSs, time of flight mass spectrometers (TOF-MS) offer both high mass resolution ($\Delta$m/m$>$1000), fast acquisition of full mass spectra ($>$1\,Hz) and mass range only limited by the detector.
+For standard available microchannel plate (MCP) as detector a mass range of 0--5000\,amu can be obtained.
 
@@
 evaporation\cite{Henriksen2009}, drop casting\cite{Vesborg2010} or gas aggregation formed size-selected nanoparticles.
-The gas composition in the microreactor reactor volume is detected by the TOF-MS which is connected to the microreactor capillary outlet.
+The gas composition in the microreactor reactor volume is ionized by the ion gauge and is subsequently detected by the TOF-MS which is connected to the microreactor capillary outlet.
 A schematic of the entire setup is shown in Figure \ref{fig:TOF_microreactor}.
@@
 The microreactor, where the catalyst under investigation is deposited, an ionization source which ionizes the gas from the microreactor and the TOF-MS used for gas analysis.
+A QMS is furthermore connected to the capillary of the microreactor which enables direct comparison between the QMS and TOF-MS.
 
@@
 Additionally, two extra contacts are placed on the chip which facilitates a 4 wire measurement of the resistance of the heating element.
-The heating strip in this way be used as a resistance temperature detector (RTD) to determine the temperature of the chip.
+The heating strip can in this way be used as a resistance temperature detector (RTD) to determine the temperature of the chip.
 At the current configuration temperatures from room temperature to approximately 450\,$^{\circ}$C can be reached.
@@
 A total of 6 gases with accompanying flow controllers are used to control the inlet gas flow to the microreactor.
-Currently, the system is configured in a 4+2 setup where 4 gases are connected to the one inlet and to gases on the other inlet.
+Currently, the system is configured in a 4+2 setup where 4 gases are connected to the first inlet and two gases connected to the secondary inlet.
 All valves and flow controllers are interfaced to computer enabling remote control of the system and the ability to run experiments over several days without human intervention.
@@
 The time of flight chamber is pumped by a turbo pump and two ion pumps.
-A 120\,l/s ion pump is used to pump the flight tube while a 400\,l/s ion pump and a 450\,l/s turbo pump is used pump down the source region which is mounted on a 8" 4-way cross.
-Opposite the source region of the TOF-MS the pumps are mounted while the two remaining flanges are occupied by the ionization gauge and blanked flange (see Figure~\ref{fig:TOF_microreactor}).
+A 120\,l/s ion pump is used to pump the flight tube while a 400\,l/s ion pump and a 450\,l/s turbo pump is used to pump down the source region which is mounted on a 8" 4-way cross.
+Opposite the source region of the TOF-MS the pumps are mounted while the two remaining flanges are occupied by the ionization gauge and a blanked flange (see Figure~\ref{fig:TOF_microreactor}).
 While idling the pressure in the source region is $\sim1$x$10^{-9}$\,mbar and $\sim2$x$10^{-9}$\,mbar in the flight tube.
 
-The time of flight equipment used for detection of gas molecules flowed through the capillary of the microreactor is designed as an orthogonal mass spectrometer.
-The TOF-MS is assembled from modules purchased from Jordan TOF Products, Inc and is configured as an orthogonal TOF.
+The time of flight equipment used for detection of gas molecules flowed through the capillary of the microreactor is designed as an orthogonal mass spectrometer and is assembled from modules purchased from Jordan TOF Products, Inc.
 
-Ionized ions enter the source through a series of entry Einzel lenses used for focusing the beam hence minimizing divergence.
+Ionized ions enter the source of the TOF-MS through a series of entry Einzel lenses used for focusing the beam hence minimizing divergence.
 In the source the beam is pushed into the flight tube by an the initial repelling push voltage, $V_p$.
-The ions are further accelerated from ground potential to the liner potential, $V_L$, and the drift velocity of an ion starting exactly from the center of the acceleration region is thus $V_L + V_p/2$.
+The ions are further accelerated from ground potential to the liner potential, $V_L$.
+Using this setup the drift velocity of an ion starting exactly from the center of the acceleration region is $V_L + V_p/2$.
 At the end of the flight tube a reflectron is installed which has two primary purposes.
@@
 ions with an initial higher velocity will have an increased flight length compared to slower ions.
-The MCP used for ion detection is placed in the focal point of the reflectron giving maximum compensation for initial velocity dispersion.
-The theoretical resolution of the equipment is $\Delta$m/m$\sim$4000.
+The MCP used for ion detection is placed in the focal point of the reflectron giving maximum compensation for initial velocity dispersion giving a theoretical resolution of the equipment of $\Delta$m/m$\sim$4000.
 
@@
 Even with our very simple home-built ionization source and a 8-bit digitizer the dynamic range is from Figure~\ref{fig:dynamic_range} estimated to $\sim$1000 using an integration time of $\sim$5\,s.
-The dynamic range of the TOF-MS is hence comparable to the dynamic range offered by a QMS at constant preamplifier range, while covering a much larger mass range.
+The dynamic range of the TOF-MS is hence comparable to the dynamic range offered by a QMS at constant preamplifier range while covering a much larger mass range.
 
@@
 At experiment start the microreactor is equilibrated with NH$_3$ and O$_2$ in a 5:3 stoichiometry (did we run at stoichiometry??).
-After equilibration the temperature is increased in steps from room temperature til 190\,$^{\circ}$C.
+After equilibration the temperature is increased in steps from room temperature to 190\,$^{\circ}$C.
 The gas composition in the microreactor is continuously probed by the TOF-MS which is connected to the capillary of the microreactor.
@@
 As expected a strong correlation between H$_2$O$^{+}$ and OH$^+$ is seen as a direct result of water cracking to hydroxyls.
+
+BØR VI LAVE ET ARRHENIUS PLOT??
 %For ammonia oxidation both N$_2$O (m/q = 44), NO (m/q = 30) and NO$_2$ (m/q = 46) are of interest.
@@
 We have demonstrated a combined microreactor and TOF-MS system which can be employed to test and characterize model heterogeneous catalysts.
-An automated gas handling system is used to flow gas over a catalyst in the reaction chamber of the microreactor from where gases can be probed.
-The reactor gas composition is probed by a microreactor capillary which is analyzed by a TOF-MS combining high sensitivity and high mass resolution.
+An automated gas handling system is used to flow gas over a catalyst in the microreactor volume from where gases can be probed.
+The reactor gas composition is directed through a flow restriction in the microreactor and subsequently analyzed by a TOF-MS combining high sensitivity and high mass resolution.
 

### 2012-03-29 paper.tex
Small changes and inclusion of initial python model

@@
 SKAL VI SKRIVE NOGET OM FLYVETID-TIL-MASSE OMREGNING?
+The model is bla bla bla and can freely be acquired\cite{ModelGithub}.
+\begin{figure}
+ \includegraphics[width=14cm]{model_error.png}%
+ \caption{In the top panel a plot of the flight time as a function of mass is shown.
+The red full line is fitted to calculated model points (blue dots) to relate mass to flight time in the TOF-MS.
+In the bottom figure the difference between acquired experimental data and data calculated from the model is plotted.
+As seen from the figure a deviation of $\sim$100\,ns at 70\,amu is present.\label{fig:model_error}}%
+\end{figure}
 
@@
 
-At experiment start the microreactor is equilibrated with NH$_3$ and O$_2$ in a 5:3 stoichiometry (did we run at stoichiometry??).
+At experiment start the microreactor is equilibrated with NH$_3$ and O$_2$ in a 4:3 ratio corresponding to stoichiometry for this reaction.
 After equilibration the temperature is increased in steps from room temperature to 190\,$^{\circ}$C.
@@
  \includegraphics[width=14cm]{ammonia_reactivity.png}%
- \caption{Ammonia oxidation as a function of temperature on a Pt thin film.
+ \caption{Ammonia oxidation as a function of temperature on a 10\% geometrical coverage Pt thin film.
 As the temperature is increased ammonia is oxidized to H$_2$O and N$_2$.
@@
 \end{figure}
-In Figure \ref{fig:ammonia_reactivity} the integrated N$_2$, NH$_3$, H$_2$O, O$_2$ and OH peaks acquired from the raw TOF-MS spectrum as a function of temperature are shown.
+In Figure~\ref{fig:ammonia_reactivity} the integrated N$_2$, NH$_3$, H$_2$O, O$_2$ and OH peaks acquired from the raw TOF-MS spectrum as a function of temperature are shown.
 At each individual temperature step a mass scan is performed from triggering of the acceleration pulse up to 25\,$\mu$s of flight time corresponding to a maximum of 70 amu.
-As seen from Figure \ref{fig:ammonia_reactivity} the combustion of NH$_3$ increases substantially at approximately 140\,$^{\circ}$C.
-The combustion of ammonia to molecular nitrogen and water at this temperature agrees well with literature \cite{Imbihl2007,Zeng2009}.
+As seen from Figure~\ref{fig:ammonia_reactivity} the combustion of NH$_3$ increases substantially at approximately 140\,$^{\circ}$C.
+The combustion of ammonia to molecular nitrogen and water at this temperature agrees well with literature\cite{Imbihl2007,Zeng2009}.
 
@@
 As expected a strong correlation between H$_2$O$^{+}$ and OH$^+$ is seen as a direct result of water cracking to hydroxyls.
+The data shown in Figure~\ref{fig:ammonia_reactivity} hence demonstrates the usability of the combined microreactor and TOF-MS setup especially simplifying data analysis of complicated mass spectra while maintaining a high sensitivity from the microreactor platform.
 

### 2012-03-29 paper.tex
Added a small bit about the nummeric model.

@@
 
-SKAL VI SKRIVE NOGET OM FLYVETID-TIL-MASSE OMREGNING?
-The model is bla bla bla and can freely be acquired\cite{ModelGithub}.
+Since the TOF-MS only measures flighttime and not the actual mass of the measured molecules, it is necessary to have a way to calculate back and forth between flight time and mass.
+This can be done by finding known patterns in the mass-spectrum where the masses can be resonably dertimed from experience and then fit these values to get an expression for the flighttime as a function of mass.
+This method works fine, but does have the drawback that it is necessary to have several peaks of well known mass, which is not always necessarily the case.
+For this reason we have also made a small nummeric model of the mass spectrometer, which will calculate the flight time based only on the voltages for the pulser, liner and reflectron and thus provides a dertermination of the time to mass conversion.
+Typically the model is used together with the experimental determination of a single mass, since this will help fix the unkown delay between measurement trigger and the rise of the high-voltage pulse at the repeller plate.
+As seen in Figure~\ref{fig:model_error} the performance of the model is surprisingly good considering its simplicity.
+The model can freely be acquired\cite{ModelGithub}.
 \begin{figure}
  \includegraphics[width=14cm]{model_error.png}%
- \caption{In the top panel a plot of the flight time as a function of mass is shown.
-The red full line is fitted to calculated model points (blue dots) to relate mass to flight time in the TOF-MS.
-In the bottom figure the difference between acquired experimental data and data calculated from the model is plotted.
+ \caption{Comparison of the simulated model (red line, top panel) to actual measured experimental values (blue dots).
+In the bottom panel the difference between acquired experimental data and data calculated from the model is plotted, errorbars represents only the uncertainty in the experimental data.
 As seen from the figure a deviation of $\sim$100\,ns at 70\,amu is present.\label{fig:model_error}}%

### 2012-03-30 paper.tex
Small changes to the text about the Python model

--- 2012-03-29 paper.tex
@@
 Using this setup the drift velocity of an ion starting exactly from the center of the acceleration region is $V_L + V_p/2$.
-At the end of the flight tube a reflectron is installed which has two primary purposes.
-The effective drift length is increased hence increasing resolution of the TOF-MS.
-The reflectron also works as a focusing lens compensating for any initial velocity dispersion of the ions, i.e.
+At the end of the flight tube a reflectron is installed which is controlled by voltages $V_{R1}$ and $V_{R2}$.
+The reflectron has two primary purposes: i) The effective drift length is increased hence increasing resolution of the TOF-MS.
+ii) The reflectron works as a focusing lens compensating for any initial velocity dispersion of the ions, i.e.
 ions with an initial higher velocity will have an increased flight length compared to slower ions.
@@
 
-SKAL VI SKRIVE NOGET OM FLYVETID-TIL-MASSE OMREGNING?
-The model is bla bla bla and can freely be acquired\cite{ModelGithub}.
+Since the TOF-MS only measures flight time and not the actual mass of the measured molecules or atoms it is necessary to determine the relationship between flight time and actual mass.
+This can be done by calibration masses expressing known patterns in the mass spectrum.
+In this way masses can be reasonably determined with subsequent fitting of these values to get an expression for the flight time as a function of mass.
+This approach is in some cases adequate but does have the significant drawback that several peaks of well known mass must be present in the flight spectrum which is not always necessarily the case.
+To determine the relationship between mass and flight time we have made a numeric model of the mass spectrometer which calculates the flight time based only on the voltages for the pulser, $V_p$, liner, $V_L$ and reflectron, $V_{R1}$ and $V_{R2}$, and thus provides a relationship of flight time to mass.
+Typically, the model is used together with the experimental determination of a single mass since this will help fix the unknown delays originating from the measurement trigger, rise time of the high-voltage pulse at the repeller plate and cable delays.
+As seen in Figure~\ref{fig:model_error} the performance of the model is surprisingly good despite its simplicity.
+The model is written in Python and can be acquired online\cite{ModelGithub}.
 \begin{figure}
  \includegraphics[width=14cm]{model_error.png}%
- \caption{In the top panel a plot of the flight time as a function of mass is shown.
-The red full line is fitted to calculated model points (blue dots) to relate mass to flight time in the TOF-MS.
-In the bottom figure the difference between acquired experimental data and data calculated from the model is plotted.
+ \caption{Comparison of the simulated model (red line, top panel) to actual measured experimental values (blue dots).
+In the bottom panel the difference between acquired experimental data and data calculated from the model is plotted, errorbars represents only the uncertainty in the experimental data.
 As seen from the figure a deviation of $\sim$100\,ns at 70\,amu is present.\label{fig:model_error}}%
@@
 
-BØR VI LAVE ET ARRHENIUS PLOT??
+%BØR VI LAVE ET ARRHENIUS PLOT??
 %For ammonia oxidation both N$_2$O (m/q = 44), NO (m/q = 30) and NO$_2$ (m/q = 46) are of interest.

### 2012-03-30 python_figures/ammonia_OH_gauss_fit.py
Correct spelling errors in the figures

@@ -107,7 +107,7 @@ axis3 = axis.twiny()
 axis3.plot(TimeToMass(X_range),X_range*0,'w-',linewidth=0) #Hack to create an invisible set on the extra x-axis
 axis3.set_xlim(TimeToMass(12.405),TimeToMass(12.44))
 #axis3.set_xticks((12.41,12.42,12.43,12.44))    
-axis3.set_xlabel('Mass / AMU', fontsize=8)
+axis3.set_xlabel('Mass / amu', fontsize=8)
 axis3.tick_params(direction='in', length=2, width=1, colors='k',labelsize=8,axis='both',pad=3)
 axis3.ticklabel_format(useOffset=False)
 

### 2012-03-30 python_figures/tof_raw.py

@@ -64,7 +64,7 @@ axis3.set_xlim(0,20)
 print MassToTime(32.0262147)
 axis3.set_xticks(MassToTime(mass_ticks))
 axis3.set_xticklabels(mass_ticks)
-axis3.set_xlabel('Mass / AMU', fontsize=8)
+axis3.set_xlabel('Mass / amu', fontsize=8)
 axis3.tick_params(direction='in', length=2, width=1, colors='k',labelsize=8,axis='both',pad=3)
 #axis3.ticklabel_format(useOffset=False)
 
@@ -106,7 +106,7 @@ axis.set_xlabel('Flight Time / $\mu$s', fontsize=8)
 p = axis.axvspan(11.45, 13, facecolor='#b6fa77', alpha=0.25)
 axis.tick_params(direction='in', length=6, width=1, colors='k',labelsize=8,axis='both',pad=3)
 axis.annotate('H$_2$O', xy=(12.75, 2.3),  xycoords='data', xytext=(12.65, 3.3), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='top',fontsize=font,)
-axis.annotate('OH', xy=(12.4, 1),  xycoords='data', xytext=(12.6, 1.9), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='top',fontsize=font,)
+axis.annotate('OH', xy=(12.4, 1),  xycoords='data', xytext=(12.7, 1.8), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='top',fontsize=font,)
 axis.annotate('O', xy=(12.05, 0.9),  xycoords='data', xytext=(12.26, 1.4), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='top',fontsize=font,)
 
 

### 2012-03-30 paper.tex
Changes before sending to Ib and Ole

@@
 The system design is superior to conventional batch and flow reactors with accompanying product detection by quadrupole mass spectrometry or gas chromatopgraphy not only due to the high sensitivity, fast temperature response, high mass resolution and fast acquisition time of mass spectra but also allows to measure on wide mass ranges (0--5000\,amu in the current configuration).
-As demonstration of the system we here present data from ammonia oxidation on platinum thin films showing resolved spectra of OH$^{+}$ and NH$_{3}^{+}$.
+As a demonstration of the system we here present data from ammonia oxidation on 5\,nm Pt nanoparticles showing resolved spectra of OH$^{+}$ and NH$_{3}^{+}$.
 \end{abstract}
@@
 As a platform for testing heterogeneous catalysts microfabricated reactors or microreactors have been found suitable due to both high surface-to-volume ratio, fast temperature response and minimization of thermal and concentration gradients\cite{Jensen2001,Jaehnisch2004}.
-Such a platform have been developed previously to test and characterize model catalysts in our department\cite{Henriksen2009}.
+Such a platform has been developed to test and characterize model catalysts in our department\cite{Henriksen2009}.
 However, a suitable reactor platform is only part of the task; reactant and product detection and characterization is essential to determine catalyst performance.
@@
 Gas chromatographs have inherently low time resolution which make them unsuitable for fast time response measurements as in the case of microreactors and is in general difficult to use as mass spectrometers due to the difficult interpretation of complex mixtures.
-As an alternative to gas chromatography or QMSs, time of flight mass spectrometers (TOF-MS) offer both high mass resolution ($\Delta$m/m$>$1000), fast acquisition of full mass spectra ($>$1\,Hz) and mass range only limited by the detector.
+As an alternative to gas chromatography or QMSs time of flight mass spectrometers (TOF-MS) offer both high mass resolution ($\Delta$m/m$>$1000), fast acquisition of full mass spectra ($>$1\,Hz) and mass range only limited by the detector.
 For standard available microchannel plate (MCP) as detector a mass range of 0--5000\,amu can be obtained.
@@
 TOF-SIMS\cite{Benninghoven1994,DeSmet1998,Grams2004,Johnson2010}.
-Measurements of reactants and products on heterogeneous catalysts by TOF-MS have previously been performed\cite{Levy1963,Okumura2007} but, until now, to our knowledge, the testing of catalysts in a microreactor with subsequent gas analysis by a TOF-MS have not been demonstrated.
+Measurements of reactants and products on heterogeneous catalysts by TOF-MS have previously been performed\cite{Levy1963,Okumura2007} but, until now, to our knowledge, the testing of catalysts in a microreactor with subsequent gas analysis by a TOF-MS has not been demonstrated.
 Here we describe a microreactor and TOF-MS system which combines the high sensitivity of microreactors and the high mass resolution TOF-MSs for testing and characterizing of heterogeneous catalysts.
@@
 evaporation\cite{Henriksen2009}, drop casting\cite{Vesborg2010} or gas aggregation formed size-selected nanoparticles.
-The gas composition in the microreactor reactor volume is ionized by the ion gauge and is subsequently detected by the TOF-MS which is connected to the microreactor capillary outlet.
+The gas composition in the microreactor reactor volume is ionized by the ion gauge and is subsequently detected by the TOF-MS which is connected to a capillary outlet on the microreactor.
 A schematic of the entire setup is shown in Figure \ref{fig:TOF_microreactor}.
@@
 The reactor consists of two gas inlets, a gas outlet, a reactor volume and a capillary used to restrict the gas flow from the reactor volume.
-The reactor volume is 3\,$\mu$m deep and 1 cm in diameter corresponding to a 236\,nL volume.
+The reactor volume is 3\,$\mu$m deep and 1 cm in diameter corresponding to a 236\,nL.
 The two gas inlets are combined on the chip where the inlet gases mix by diffusion.
@@
 In reality the dynamic range is limited mostly by the data acquisition hardware as well as the quality of the ion source.
-Even with our very simple home-built ionization source and a 8-bit digitizer the dynamic range is from Figure~\ref{fig:dynamic_range} estimated to $\sim$1000 using an integration time of $\sim$5\,s.
+Even with the home-built ionization source and a 8-bit digitizer the dynamic range is from Figure~\ref{fig:dynamic_range} estimated to $\sim$1000 using an integration time of $\sim$5\,s.
 The dynamic range of the TOF-MS is hence comparable to the dynamic range offered by a QMS at constant preamplifier range while covering a much larger mass range.
@@
 In this way masses can be reasonably determined with subsequent fitting of these values to get an expression for the flight time as a function of mass.
-This approach is in some cases adequate but does have the significant drawback that several peaks of well known mass must be present in the flight spectrum which is not always necessarily the case.
-To determine the relationship between mass and flight time we have made a numeric model of the mass spectrometer which calculates the flight time based only on the voltages for the pulser, $V_p$, liner, $V_L$ and reflectron, $V_{R1}$ and $V_{R2}$, and thus provides a relationship of flight time to mass.
+This approach is in some cases adequate but does have the significant drawback that several peaks of well known masses must be present in the flight spectrum which is not always necessarily the case.
+To determine the relationship between mass and flight time we have made a numeric model of the mass spectrometer which calculates the flight time based only on the voltages for the pulser, $V_p$, liner, $V_L$, and reflectron, $V_{R1}$ and $V_{R2}$, and thus provides a relationship of flight time to mass.
 Typically, the model is used together with the experimental determination of a single mass since this will help fix the unknown delays originating from the measurement trigger, rise time of the high-voltage pulse at the repeller plate and cable delays.
-As seen in Figure~\ref{fig:model_error} the performance of the model is surprisingly good despite its simplicity.
+As seen in Figure~\ref{fig:model_error} the performance of the model is good despite its simplicity giving a total error in flight time estimation of $\sim$100\,ns at 70\,amu.
 The model is written in Python and can be acquired online\cite{ModelGithub}.
@@
 \section{Oxidation of ammonia}
-To demonstrate the system capability ammonia oxidation on platinum thin films has been used as test reaction. The catalytic oxidation of ammonia can proceed along primarily three different routes.
+To demonstrate the system capability ammonia oxidation on a 40\,\% geometrical coverage 5\,nm Pt nanoparticles has been used as test reaction.
+The catalytic oxidation of ammonia can proceed along primarily three different routes.
 \begin{equation}
@@
 At experiment start the microreactor is equilibrated with NH$_3$ and O$_2$ in a 4:3 ratio corresponding to stoichiometry for this reaction.
-After equilibration the temperature is increased in steps from room temperature to 190\,$^{\circ}$C.
+After equilibration the temperature is increased in steps of ??
+from room temperature to 190\,$^{\circ}$C.
 The gas composition in the microreactor is continuously probed by the TOF-MS which is connected to the capillary of the microreactor.
@@
  \includegraphics[width=14cm]{ammonia_reactivity.png}%
- \caption{Ammonia oxidation as a function of temperature on a 10\% geometrical coverage Pt thin film.
+ \caption{Ammonia oxidation as a function of temperature on a 40\,\% geometrical coverage 5\,nm Pt nanoparticles.
 As the temperature is increased ammonia is oxidized to H$_2$O and N$_2$.
@@
 In Figure~\ref{fig:ammonia_reactivity} the integrated N$_2$, NH$_3$, H$_2$O, O$_2$ and OH peaks acquired from the raw TOF-MS spectrum as a function of temperature are shown.
-At each individual temperature step a mass scan is performed from triggering of the acceleration pulse up to 25\,$\mu$s of flight time corresponding to a maximum of 70 amu.
+At each individual temperature step a mass scan is performed from triggering of the acceleration pulse up to 25\,$\mu$s of flight time corresponding to 70 amu.
 As seen from Figure~\ref{fig:ammonia_reactivity} the combustion of NH$_3$ increases substantially at approximately 140\,$^{\circ}$C.
@@
 We have demonstrated a combined microreactor and TOF-MS system which can be employed to test and characterize model heterogeneous catalysts.
-An automated gas handling system is used to flow gas over a catalyst in the microreactor volume from where gases can be probed.
+An automated gas handling system is used to flow gas over a catalyst in a microreactor volume from where gases can be probed.
 The reactor gas composition is directed through a flow restriction in the microreactor and subsequently analyzed by a TOF-MS combining high sensitivity and high mass resolution.
 
-As a demonstration of the system ammonia oxidation on platinum thin films was performed.
+As a demonstration of the system ammonia oxidation on 5\,nm Pt nanoparticles was performed.
 The ability to resolve OH$^{+}$ and NH$_3^+$ which is separated by 23\,milli-amu was demonstrated.
@@
 This greatly simplifies the analysis compared to conventional QMSs used for gas analysis.
-The setup is furthermore superior to conventional QMSs where the mass range is limited to $\sim$500\,amu.
+The setup is furthermore superior to conventional QMSs where the mass range is limited to $\sim$500\,amu and can be applied to the study of small amounts of catalysts.
 
-\section{Acknowledgements}
+%\section{Acknowledgements}
 

### 2012-04-11 paper.tex
First dump after initial corrections by Ole and Ib

@@
 Gas analysis is performed with a time of flight mass spectrometer with a modified nude Bayard-Alpert ionization gauge as gas ionization source.
-The mass resolution of the time of flight mass spectrometer using the ion gauge as ionization source is estimated to $\Delta$m/m$>$2500.
-The system design is superior to conventional batch and flow reactors with accompanying product detection by quadrupole mass spectrometry or gas chromatopgraphy not only due to the high sensitivity, fast temperature response, high mass resolution and fast acquisition time of mass spectra but also allows to measure on wide mass ranges (0--5000\,amu in the current configuration).
-As a demonstration of the system we here present data from ammonia oxidation on 5\,nm Pt nanoparticles showing resolved spectra of OH$^{+}$ and NH$_{3}^{+}$.
+The mass resolution of the time of flight mass spectrometer using the ion gauge as ionization source is estimated to m/$\Delta$m$>$2500.
+The system design is superior to conventional batch and flow reactors with accompanying product detection by quadrupole mass spectrometry or gas chromatography not only due to the high sensitivity, fast temperature response, high mass resolution and fast acquisition time of mass spectra but also allows wide mass range (0--5000\,amu in the current configuration).
+As a demonstration of the system we present data from ammonia oxidation on 5\,nm Pt nanoparticles showing resolved spectra of OH$^{+}$ and NH$_{3}^{+}$.
 \end{abstract}
@@
 \section{Introduction}
-In heterogeneous catalysis the optimization and development of equipment is important both to minimize the cost of equipment but also to be able to study complicated systems.
+In heterogeneous catalysis optimization and development of equipment is important both to minimize the cost of equipment but also to be able to study complicated systems.
 As a platform for testing heterogeneous catalysts microfabricated reactors or microreactors have been found suitable due to both high surface-to-volume ratio, fast temperature response and minimization of thermal and concentration gradients\cite{Jensen2001,Jaehnisch2004}.
@@
 However, a suitable reactor platform is only part of the task; reactant and product detection and characterization is essential to determine catalyst performance.
-Typically, quadrupole mass spectrometers (QMSs) are used in low pressure regimes to analyze gas composition while gas chromatographs are used for high pressure measurements.
-The QMS, however, suffer from a low mass resolution ($\Delta$m/m$\sim$m up to m$\sim$200) which makes analysis of complicated spectra difficult and cumbersome.
+Typically, quadrupole mass spectrometers (QMSs) are used in low pressure regimes to analyze gas composition while gas chromatographs (GCs) are used for high pressure measurements.
+The QMS, however, suffer from a low mass resolution (m/$\Delta$m$>\sim$m up to m$\sim$200) which makes analysis of complicated spectra difficult and cumbersome.
 The QMS is additionally subject to a low mass range (typically $\sim$100-200\,amu) limiting general use.
@@
 This is at the expense of acquisition of full mass spectra during the experiment limiting operation by potentially losing interesting features in other masses not monitored.
-Gas chromatographs have inherently low time resolution which make them unsuitable for fast time response measurements as in the case of microreactors and is in general difficult to use as mass spectrometers due to the difficult interpretation of complex mixtures.
-As an alternative to gas chromatography or QMSs time of flight mass spectrometers (TOF-MS) offer both high mass resolution ($\Delta$m/m$>$1000), fast acquisition of full mass spectra ($>$1\,Hz) and mass range only limited by the detector.
+GCs have inherently low time resolution which make them unsuitable for fast time response measurements as in the case of microreactors and is in general difficult to use as mass spectrometers due to the difficult interpretation of complex mixtures.
+Furthermore, GCs samples only a very small part of converted gas making them unsuitable for small amounts of reactant and product gases due to the low sensitivity.
+As an alternative to GCs or QMSs time of flight mass spectrometers (TOF-MS) offer both high mass resolution ($\Delta$m/m$>$1000), fast acquisition of full mass spectra ($>$1\,Hz), high sensitivity making them suitable for very small amounts of catalyst, i.e.
+model systems, and mass range only limited by the detector.
 For standard available microchannel plate (MCP) as detector a mass range of 0--5000\,amu can be obtained.
@@
  \includegraphics[width=14cm]{TOF_microreactor.png}%
- \caption{Schematic of the total system (not to scale)\label{fig:TOF_microreactor}}%
+ \caption{Schematic of the total system (not to scale).
+The capillary outlet from the microreactor can be directed to either a QMS or the TOF-MS.
+For measurements by the TOF-MS the gas is fed into a modified ion gauge which ionizes the gas.
+The ionized gas hereafter enters the TOF through a series of Einzel lenses from where they are pushed into the flight tube by a repelling voltage, V$_p$.
+After the focusing by the reflectron the ions are detected by a MCP.\label{fig:TOF_microreactor}}%
 \end{figure}
@@
 The reactor volume is 3\,$\mu$m deep and 1 cm in diameter corresponding to a 236\,nL.
+The diffusion length of the reactants and products gases in the microreactor reactor volume is almost an order of magnitude longer than the radius of the reactor volume ensuring full contact of the gas with the catalyst.
+This has been proven to hold by reproducible CO oxidation on Pt spots located at different points in the the reactor volume.
 The two gas inlets are combined on the chip where the inlet gases mix by diffusion.
@@
 The heating element is contacted by two pogo pins which is connected to a power supply.
-Additionally, two extra contacts are placed on the chip which facilitates a 4 wire measurement of the resistance of the heating element.
+Additionally, two extra contacts are placed on the chip facilitating a 4 wire measurement of the resistance of the heating element.
 The heating strip can in this way be used as a resistance temperature detector (RTD) to determine the temperature of the chip.
@@
 Currently, the system is configured in a 4+2 setup where 4 gases are connected to the first inlet and two gases connected to the secondary inlet.
+At the time of writing He, CO, O, CH$_4$, NH$_3$ and H$_2$.
+All gases used on the setup are N6 quality gases, i.e.
+99.9999\,\% purity.
 All valves and flow controllers are interfaced to computer enabling remote control of the system and the ability to run experiments over several days without human intervention.
@@
 Opposite the source region of the TOF-MS the pumps are mounted while the two remaining flanges are occupied by the ionization gauge and a blanked flange (see Figure~\ref{fig:TOF_microreactor}).
-While idling the pressure in the source region is $\sim1$x$10^{-9}$\,mbar and $\sim2$x$10^{-9}$\,mbar in the flight tube.
+While idling the pressure in the source region is $\sim1\cdot10^{-9}$\,mbar and $\sim2\cdot10^{-9}$\,mbar in the flight tube.
 
-The time of flight equipment used for detection of gas molecules flowed through the capillary of the microreactor is designed as an orthogonal mass spectrometer and is assembled from modules purchased from Jordan TOF Products, Inc.
+The time of flight equipment used for detection of gas molecules flowed through the capillary of the microreactor is designed as an orthogonal mass spectrometer and is assembled from modules purchased from Jordan TOF Products, Inc\cite{JordanHomepage}.
 
@@
 ions with an initial higher velocity will have an increased flight length compared to slower ions.
-The MCP used for ion detection is placed in the focal point of the reflectron giving maximum compensation for initial velocity dispersion giving a theoretical resolution of the equipment of $\Delta$m/m$\sim$4000.
+The MCP used for ion detection is placed in the focal point of the reflectron giving maximum compensation for initial velocity dispersion.
+According to the manufacturer a resolution m/$\Delta$m$>\sim$4000 of the TOF has been shown.
+
+The prize of the TOF including ionization, 8" 4-way cross, control electronics, data acquisition hardware and MCP detector is estimated to USD80.000 which is comparable to a high quality QMS which is prized at approximately USD85.000.
 
@@
  \caption{Raw data acquired from the TOF-MS in a gas mixture of methanol and atmospheric air.
-Subfigures show the three different regions of the spectrum.
-From the first subfigure a delay of approximately 150\,ns can be seen which is due to delays in cables and the rise time of the repeller pulser.
-In the center subfigure the extremely good seperation between seperate masses is shown.
+Subfigures show three different regions of the spectrum.
+From the first subfigure a delay of approximately 150\,ns can be seen due to delays in cables and the rise time of the repeller pulser.
+In the center subfigure the extremely good seperation between masses is shown.
 It is evident that 1\,amu corresponds to approximately 350\,ns difference in flight time in our system in the mass regime around 20\,amu.
@@
 As ionization source of the gas flow from the microreactor capillary a modified nude UHV Bayard-Alpert ion gauge is used.
-Approximately 3\,A is run through the filament resulting in 10\,mA emission current.
+3\,A is run through the filament resulting in 10\,mA emission current.
 The grid is biased approximately 40\,V negative compared to the filament to accelerate electrons emitted from the filament towards the grid.
-Contrary to standard operation of a ion gauge the collector in the center of the grid is short-circuited to the grid ensuring homogeneous field distribution within the grid.
+Contrary to standard operation of an ion gauge the collector in the center of the grid is short-circuited to the grid ensuring homogeneous field distribution within the grid.
 To allow ionized ions to escape from the gauge the lid of the grid has been removed.
@@
 All of these systems are difficult to analyze both qualitatively and quantitatively due to the overlap of NH$_3$, which is a reactant, and OH$^+$ originating from cracking of H$_2$O, which is a product from the combustion and is a part of the residue gas.
-Specifically, hydroxyls (OH$^{+}$) from cracking of trace water in the system and the combustion reaction and the primary peak of ammonia (NH$_{3}^{+}$) is both detected at m/q$\simeq$17.
+Specifically, hydroxyls (OH$^{+}$) from cracking of trace water in the system and the combustion reaction and the primary peak of ammonia (NH$_{3}^{+}$) are both detected at m/q$\simeq$17.
 Without adequate mass resolution it is not possible to separate the two contributions resulting in difficult analysis.
@@
 In the case of ammonia, m/q=15 or m/q=8.5 is typically chosen since water does not contribute to these masses.
-However, both of these masses contains only a very small fraction of the main peak since it involves either the loss of two hydrogen atoms or a double charged ammonia molecule which are both processes with very low yields.
+However, both of these masses contains only a very small fraction of the main peak since it involves either the loss of two hydrogen atoms or a double charged ammonia molecule which are processes with very low yields.
 The measurement of these masses have a very poor signal to noise ratio making measurements on ammonia very difficult with traditional mass spectrometry methods.
@@
 As the temperature is increased ammonia is oxidized to H$_2$O and N$_2$.
-Furthermore, the OH and NH$_3$ signal is anticorrelated demonstrating the ability to resolve these two close lying masses.\label{fig:ammonia_reactivity}}%
+Furthermore, the OH and NH$_3$ signal is anticorrelated demonstrating the ability to resolve these two close lying masses as shown in Figure \ref{fig:gaussian_fit}.\label{fig:ammonia_reactivity}}%
 \end{figure}

### 2012-04-12 paper.tex
Incorporated most if Ib and Oles corrections.

@@
 The mass resolution of the time of flight mass spectrometer using the ion gauge as ionization source is estimated to m/$\Delta$m$>$2500.
-The system design is superior to conventional batch and flow reactors with accompanying product detection by quadrupole mass spectrometry or gas chromatography not only due to the high sensitivity, fast temperature response, high mass resolution and fast acquisition time of mass spectra but also allows wide mass range (0--5000\,amu in the current configuration).
+The system design is superior to conventional batch and flow reactors with accompanying product detection by quadrupole mass spectrometry or gas chromatography not only due to the high sensitivity, fast temperature response, high mass resolution and fast acquisition time of mass spectra but it also allows wide mass range (0--5000\,amu in the current configuration).
 As a demonstration of the system we present data from ammonia oxidation on 5\,nm Pt nanoparticles showing resolved spectra of OH$^{+}$ and NH$_{3}^{+}$.
@@
 \section{Introduction}
-In heterogeneous catalysis optimization and development of equipment is important both to minimize the cost of equipment but also to be able to study complicated systems.
+In heterogeneous catalysis optimization and development of analytic equipment is important both to minimize the cost of equipment but also to be able to experimentally study complicated systems.
 As a platform for testing heterogeneous catalysts microfabricated reactors or microreactors have been found suitable due to both high surface-to-volume ratio, fast temperature response and minimization of thermal and concentration gradients\cite{Jensen2001,Jaehnisch2004}.
@@
 Typically, quadrupole mass spectrometers (QMSs) are used in low pressure regimes to analyze gas composition while gas chromatographs (GCs) are used for high pressure measurements.
-The QMS, however, suffer from a low mass resolution (m/$\Delta$m$>\sim$m up to m$\sim$200) which makes analysis of complicated spectra difficult and cumbersome.
+The QMS, however, suffers from a low mass resolution (m/$\Delta$m$>\sim$m up to m$\sim$200) which makes analysis of complicated spectra difficult and cumbersome.
 The QMS is additionally subject to a low mass range (typically $\sim$100-200\,amu) limiting general use.
@@
 GCs have inherently low time resolution which make them unsuitable for fast time response measurements as in the case of microreactors and is in general difficult to use as mass spectrometers due to the difficult interpretation of complex mixtures.
-Furthermore, GCs samples only a very small part of converted gas making them unsuitable for small amounts of reactant and product gases due to the low sensitivity.
+Furthermore, GCs only sample a very small part of converted gas making them unsuitable for small amounts of reactant and product gases due to the low sensitivity.
 As an alternative to GCs or QMSs time of flight mass spectrometers (TOF-MS) offer both high mass resolution ($\Delta$m/m$>$1000), fast acquisition of full mass spectra ($>$1\,Hz), high sensitivity making them suitable for very small amounts of catalyst, i.e.
 model systems, and mass range only limited by the detector.
-For standard available microchannel plate (MCP) as detector a mass range of 0--5000\,amu can be obtained.
+For a standard available microchannel plate (MCP) used as detector a mass range of 0--5000\,amu can be obtained.
 
@@
 \section{System design}
-The microreactor as a reactor platform and TOF-MS as mass spectrometer enables high sensitivity reactivity measurements of the catalyst under investigation combined with high resolution mass spectrometry.
+The setup consists of three main components.
+The microreactor, where the catalyst under investigation is deposited, an ionization source which ionizes the gas from the microreactor and the TOF-MS used for gas analysis.
+A QMS is furthermore connected to the capillary of the microreactor which enables direct comparison between the QMS and TOF-MS.
 
@@
 evaporation\cite{Henriksen2009}, drop casting\cite{Vesborg2010} or gas aggregation formed size-selected nanoparticles.
-The gas composition in the microreactor reactor volume is ionized by the ion gauge and is subsequently detected by the TOF-MS which is connected to a capillary outlet on the microreactor.
+The gas composition in the microreactor reactor volume is ionized by the modified ion gauge  and is subsequently focused by the Einzel lenses into the source region.
+From the source region the ions are pushed into the flight tube by a repelling voltage pulse and is after mass separation in the flight tube detected by a MCP.
 A schematic of the entire setup is shown in Figure \ref{fig:TOF_microreactor}.
@@
 For measurements by the TOF-MS the gas is fed into a modified ion gauge which ionizes the gas.
-The ionized gas hereafter enters the TOF through a series of Einzel lenses from where they are pushed into the flight tube by a repelling voltage, V$_p$.
-After the focusing by the reflectron the ions are detected by a MCP.\label{fig:TOF_microreactor}}%
+The ionized gas hereafter enters the TOF-MS through a series of Einzel lenses from where they are pushed into the flight tube by a repelling voltage, V$_p$.
+Ions are separated in the field free region and focused by the reflectron.
+Subsequently the ions are detected by the MCP.\label{fig:TOF_microreactor}}%
 \end{figure}
-The setup consists of three main components.
-The microreactor, where the catalyst under investigation is deposited, an ionization source which ionizes the gas from the microreactor and the TOF-MS used for gas analysis.
-A QMS is furthermore connected to the capillary of the microreactor which enables direct comparison between the QMS and TOF-MS.
 
@@
 Catalyst characterization and performance evaluation is performed in a microreactor platform \cite{Henriksen2009}.
-The microreactors are silicon-based and measures 20x15\,mm.
+The microreactors are silicon-based and measures 20x16\,mm.
 The reactor consists of two gas inlets, a gas outlet, a reactor volume and a capillary used to restrict the gas flow from the reactor volume.
@@
 Any surplus of gas from the two inlets that does not enter the reactor volume is directed through an outlet to a turbo pump.
-The design ensures that all molecules or atoms entering the reactor volume, hence exposed to the catalyst under investigation, is detected by mass spectrometry ensuring high sensitivity.
+The design ensures that all molecules or atoms entering the reactor volume, hence exposed to the catalyst under investigation, are detected by mass spectrometry ensuring high sensitivity.
 
 The microreactor is heated by joule heating of a 50\,nm platinum strip evaporated through a shadow mask on the backside of the chip.
-The heating element is contacted by two pogo pins which is connected to a power supply.
-Additionally, two extra contacts are placed on the chip facilitating a 4 wire measurement of the resistance of the heating element.
+The heating element is contacted by two pogo pins which are connected to a power supply.
+Two additional contacts are placed on the chip facilitating a 4 wire measurement of the resistance of the heating element.
 The heating strip can in this way be used as a resistance temperature detector (RTD) to determine the temperature of the chip.
-At the current configuration temperatures from room temperature to approximately 450\,$^{\circ}$C can be reached.
+In the current configuration temperatures from room temperature to approximately 450\,$^{\circ}$C can be reached.
 
 \subsection{Gas handling for the microreactor}
-The two gas inlets on the microreactor chip is connected to a gas handling system.
+The two gas inlets on the microreactor chip is connected to a macroscopic gas handling system which is constructed entirely from UHV compatible elements to ensure extremely clean gas handling.
 A total of 6 gases with accompanying flow controllers are used to control the inlet gas flow to the microreactor.
 Currently, the system is configured in a 4+2 setup where 4 gases are connected to the first inlet and two gases connected to the secondary inlet.
-At the time of writing He, CO, O, CH$_4$, NH$_3$ and H$_2$.
+At the time of writing He, CO, O, CH$_4$, NH$_3$ and H$_2$ are connected to the setup.
 All gases used on the setup are N6 quality gases, i.e.
 99.9999\,\% purity.
-All valves and flow controllers are interfaced to computer enabling remote control of the system and the ability to run experiments over several days without human intervention.
+All valves and flow controllers are interfaced to a computer enabling remote control of the system and the ability to run experiments over several days without human intervention.
 
@@
 Opposite the source region of the TOF-MS the pumps are mounted while the two remaining flanges are occupied by the ionization gauge and a blanked flange (see Figure~\ref{fig:TOF_microreactor}).
-While idling the pressure in the source region is $\sim1\cdot10^{-9}$\,mbar and $\sim2\cdot10^{-9}$\,mbar in the flight tube.
+While idling the pressure in the source region is $\sim1\times10^{-9}$\,mbar and $\sim2\times10^{-9}$\,mbar in the flight tube.
 
-The time of flight equipment used for detection of gas molecules flowed through the capillary of the microreactor is designed as an orthogonal mass spectrometer and is assembled from modules purchased from Jordan TOF Products, Inc\cite{JordanHomepage}.
+The time of flight equipment used for detection of gas molecules flown through the capillary of the microreactor is designed as an orthogonal mass spectrometer and is assembled from modules purchased from Jordan TOF Products, Inc\cite{JordanHomepage}.
 
@@
 At the end of the flight tube a reflectron is installed which is controlled by voltages $V_{R1}$ and $V_{R2}$.
-The reflectron has two primary purposes: i) The effective drift length is increased hence increasing resolution of the TOF-MS.
+The reflectron has two primary purposes: i) The effective drift length is increased hence increasing the resolution of the TOF-MS.
 ii) The reflectron works as a focusing lens compensating for any initial velocity dispersion of the ions, i.e.
@@
 
-The prize of the TOF including ionization, 8" 4-way cross, control electronics, data acquisition hardware and MCP detector is estimated to USD80.000 which is comparable to a high quality QMS which is prized at approximately USD85.000.
+The prize of the TOF including ionization, 8" 4-way cross, control electronics, data acquisition hardware and MCP detector is estimated to USD80000 which is comparable to a high quality QMS which is prized at approximately USD85000.
 
@@
 Subfigures show three different regions of the spectrum.
-From the first subfigure a delay of approximately 150\,ns can be seen due to delays in cables and the rise time of the repeller pulser.
-In the center subfigure the extremely good seperation between masses is shown.
+From the first subfigure a delay between the acquisition trigger and the noise signal from the rise of the high voltage pulser of approximately 150\,ns can be seen.
+This is due to delays in cables and the repeller pulser.
+In the center subfigure the extremely good separation between individual masses is shown.
 It is evident that 1\,amu corresponds to approximately 350\,ns difference in flight time in our system in the mass regime around 20\,amu.
@@
 
-\subsubsection{Ionization of gas}
+\subsubsection{Gas ionization}
 As ionization source of the gas flow from the microreactor capillary a modified nude UHV Bayard-Alpert ion gauge is used.
-3\,A is run through the filament resulting in 10\,mA emission current.
+A current approximately 3\,A is run through the filament resulting in 10\,mA emission current.
 The grid is biased approximately 40\,V negative compared to the filament to accelerate electrons emitted from the filament towards the grid.
-Contrary to standard operation of an ion gauge the collector in the center of the grid is short-circuited to the grid ensuring homogeneous field distribution within the grid.
+Contrary to standard operation of an ion gauge the collector in the center of the grid is short-circuited to the grid ensuring a homogeneous field distribution within the grid.
 To allow ionized ions to escape from the gauge the lid of the grid has been removed.
 Using this configuration approximately half of the ionized ions are expected to leave the ionization gauge\cite{Nottingham1955}.
-The entire construction is placed in a nozzle which is differentially pumped by a turbo pump.
+The entire construction is placed in a small orifice which is differentially pumped by a turbo pump.
 Large amounts of gas can hence be dosed locally around the ion gauge while still maintaining a low pressure in the source region of the TOF-MS.
-The nozzle is essential in the setup to avoid high pressure in the acceleration region and drift tube resulting in an increase in dead counts on the MCP thus decreasing the signal-to-noise ratio of the recorded signal.
+The small orifice is essential in the setup to avoid high pressure in the acceleration region and drift tube of the TOF-MS which would cause an increase in dead counts on the MCP thus decrease the signal-to-noise ratio of the recorded signal.
 
@@
 As seen from the response a high dynamic range of the TOF-MS all yielding good gaussian fits.
-The TOF-MS can hence be used to monitor both very small and very large signal masses with high time resolution.\label{fig:dynamic_range}}%
+The TOF-MS can hence be used to monitor both very small and very large signal masses.
+At the bottom panel the area normalized error for each fit shows that the relative fit error is independent of the total peak area.\label{fig:dynamic_range}}%
 \end{figure}
@@
 The dynamic range of the TOF-MS is hence comparable to the dynamic range offered by a QMS at constant preamplifier range while covering a much larger mass range.
+The TOF-MS, however, acquires mass spectra (0--5000\,amu) with high frequency ($>1$\,Hz) which is impossible with a QMS where only a few masses can be followed as a function of time to increase time resolution.
+The possibility of fast acquisition of complete mass spectra by the TOF-MS thus ensures that all masses are monitored simultaneously during the experiment.
+The problem of selecting appropriate masses for logging by the QMS is hence eliminated.
 
@@
 In this way masses can be reasonably determined with subsequent fitting of these values to get an expression for the flight time as a function of mass.
-This approach is in some cases adequate but does have the significant drawback that several peaks of well known masses must be present in the flight spectrum which is not always necessarily the case.
+This approach is in some cases adequate but does have the significant drawback that several peaks of well known masses must be present in the flight spectrum which is not always necessarily feasible.
 To determine the relationship between mass and flight time we have made a numeric model of the mass spectrometer which calculates the flight time based only on the voltages for the pulser, $V_p$, liner, $V_L$, and reflectron, $V_{R1}$ and $V_{R2}$, and thus provides a relationship of flight time to mass.
@@
 To demonstrate the system capability ammonia oxidation on a 40\,\% geometrical coverage 5\,nm Pt nanoparticles has been used as test reaction.
-The catalytic oxidation of ammonia can proceed along primarily three different routes.
+The catalytic oxidation of ammonia can proceed along primarily three different routes\cite{Imbihl2007}.
 \begin{equation}
-4NH_3+3O_2\rightarrow 2N_2 + 6H_2O
+4\mathrm{NH}_3+3\mathrm{O}_2\rightarrow 2\mathrm{N}_2 + 6\mathrm{H}_2\mathrm{O}
 \label{eq:Pt_clean_combustion}
@@
 \begin{equation}
-2NH_3+2O_2\rightarrow N_2O + 3H_2O
+2\mathrm{NH}_3+2\mathrm{O}_2\rightarrow \mathrm{N}_2\mathrm{O} + 3\mathrm{H}_2\mathrm{O}
 \end{equation}
 \begin{equation}
-4NH_3+5O_2\rightarrow 4NO + 6H_2O
+4\mathrm{NH}_3+5\mathrm{O}_2\rightarrow 4\mathrm{NO} + 6\mathrm{H}_2\mathrm{O}
 \end{equation}
@@
 Without adequate mass resolution it is not possible to separate the two contributions resulting in difficult analysis.
-Often a charge to mass ratio without cracking from either products or residue gas in the system is used to quantify the amount of ammonia and water.
+Often a charge to mass ratio without cracking from either products or residual gas in the system is used to quantify the amount of ammonia and water.
 In the case of ammonia, m/q=15 or m/q=8.5 is typically chosen since water does not contribute to these masses.
-However, both of these masses contains only a very small fraction of the main peak since it involves either the loss of two hydrogen atoms or a double charged ammonia molecule which are processes with very low yields.
+However, both of these masses contains only a very small fraction of the main peak since it involves either the loss of two hydrogen atoms or a double charged ammonia molecule which are both processes with very low yields.
 The measurement of these masses have a very poor signal to noise ratio making measurements on ammonia very difficult with traditional mass spectrometry methods.
@@
 At experiment start the microreactor is equilibrated with NH$_3$ and O$_2$ in a 4:3 ratio corresponding to stoichiometry for this reaction.
-After equilibration the temperature is increased in steps of ??
-from room temperature to 190\,$^{\circ}$C.
+After equilibration the temperature is increased in steps of 2.5\,$^{\circ}$C from 150\,$^{\circ}$C to 215\,$^{\circ}$C.
 The gas composition in the microreactor is continuously probed by the TOF-MS which is connected to the capillary of the microreactor.

### 2012-04-15 python_figures/ammonia_OH_gauss_fit.py
Started to update the figures for the thin-film sample

@@ -9,9 +9,8 @@ import MySQLdb
 import sys
 
 def TimeToMass(time):
-    #time = 2.97277909899 * mass^0.499352719883
-    corr_time = time - 0.183  #Approximate delay
-    mass = (corr_time / 2.97277909899)**(1.0/0.499352719883)
+    corr_time = time - 0.181  #Approximate delay
+    mass = (corr_time / 2.98660484819)**(1.0/0.4977024241071)
     return mass
 
 matplotlib.rc('text',usetex=True) # Magic fix for the font warnings
@@ -36,12 +35,13 @@ fig.set_size_inches(fig_width,fig_height)
 
 #Relevant time, OH: 12.418, NH3: 12.427
 data = {}
-cursor.execute("SELECT x*1000000,y*1000 FROM xy_values_tof where measurement = 245")
+#cursor.execute("SELECT x*1000000,y*1000 FROM xy_values_tof where measurement = 245")
+cursor.execute("SELECT x*1000000,y*1000 FROM xy_values_tof where measurement = 427")
 Data = np.array(cursor.fetchall())
 
 masses = []
-masses.append(['OH',12.418,6])
-masses.append(['NH3',12.427,6])
+masses.append(['OH',12.413,6])
+masses.append(['NH3',12.424,6])
 
 fit = []
 
@@ -91,15 +91,15 @@ axis.tick_params(direction='in', length=2, width=1, colors='k',labelsize=8,axis=
 axis.set_yticks((20,40,60))    
 axis.set_xticks((12.41,12.42,12.43,12.44))    
 axis.ticklabel_format(useOffset=False)
-axis.set_xlim(12.405,12.44)
+axis.set_xlim(12.405,12.435)
 axis.set_ylabel('Response / mV', fontsize=8)
 axis.set_xlabel('Flight Time / $\mu$s', fontsize=8)
 
 
 arrow = dict(facecolor='black',arrowstyle='->')
 font = 8
-axis.annotate('OH', xy=(12.416, 60),  xycoords='data', xytext=(12.41, 50), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='top',fontsize=font,)
-axis.annotate('NH$_3$', xy=(12.428, 40),  xycoords='data', xytext=(12.433, 50), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='top',fontsize=font,)
[…]

### 2012-04-15 python_figures/ammonia_reactivity.py

@@ -33,7 +33,7 @@ for i in range(0,len(config.temperatures)):
 treated_data = {}
 #Prepare the list that will hold the (temp,intensity) values
 for mass in config.masses:
-    treated_data[mass[0]] = np.zeros((len(config.temperatures),2))
+    treated_data[mass[0]] = np.zeros((len(config.temperatures),3))
 
 
 pp = PdfPages('multipage.pdf')
@@ -63,27 +63,28 @@ for j in range(0,len(config.temperatures)):
         errfunc = lambda p, x, y: fitfunc(p, x) - y # Distance to the target function
         p0 = [50,0.00001,0] # Initial guess for the parameters
         p1, success = optimize.leastsq(errfunc, p0[:], args=(x_values, y_values),maxfev=1000)        
-
+        
         if (success > 4) or p1[1]>0.01:
             p0 = [5,0.00001,0]
             p1, success = optimize.leastsq(errfunc, p0[:], args=(x_values[2:5], y_values[2:5]))
-       
+        
         if success > 4 or p1[1]>0.01 or p1[1]<0:
             print "p1:" + str(p1[0]) + " p1:" + str(p1[1]) + " p2:" + str(p1[2]) + " j: " + str(j)
             p1[1] = 0
 
-        axis.plot(X_values,Y_values,'b-')
-        axis.plot([Data[start,0],Data[start,0]],[0,max(y_values)],'k-')
-        axis.plot([Data[end,0],Data[end,0]],[0,max(y_values)],'k-')
+        #axis.plot(X_values,Y_values,'b-')
+        #axis.plot([Data[start,0],Data[start,0]],[0,max(y_values)],'k-')
+        #axis.plot([Data[end,0],Data[end,0]],[0,max(y_values)],'k-')
 
-        axis.plot(X_values,fitfunc(p1, X_values),'r-')
-        axis.tick_params(direction='in', length=2, width=1, colors='k',labelsize=8,axis='both',pad=5)
-        axis.annotate(mass[0], xy=(.05,.85), xycoords='axes fraction',fontsize=8)
-        axis.set_xticks(())
+        #axis.plot(X_values,fitfunc(p1, X_values),'r-')
+        #axis.tick_params(direction='in', length=2, width=1, colors='k',labelsize=8,axis='both',pad=5)
[…]

### 2012-04-15 python_figures/thin_film_config.py

@@ -1,33 +1,36 @@
+import MySQLdb
+
+try:
+    db = MySQLdb.connect(host="servcinf", user="cinf_reader",passwd = "cinf_reader", db = "cinfdata")
+except:
+    db = MySQLdb.connect(host="127.0.0.1", port=9995, user="cinf_reader",passwd = "cinf_reader", db = "cinfdata")
+
+cursor = db.cursor()
+
+initial_db = 403
+number_of_spectrums = 57
+
+times = []
 temperatures = []
+init_time = 0
+for i in range(initial_db,initial_db+number_of_spectrums):
+    cursor.execute("select sample_temperature, unix_timestamp(time) from measurements_tof where id = " + str(i))
+    fetch = (cursor.fetchall())
+    temperatures = temperatures + [fetch[0][0]]
+    if init_time == 0:
+        init_time = fetch[0][1]
+        times = times + [0]
+    else:
+        times = times + [fetch[0][1]-init_time]
 
-"""
-temperatures = temperatures + [40,60,80]
-
-for i in range(100,195,5): #Note last value is not included
-    temperatures = temperatures + [i]
-
-for i in range(180,105,-5): #Note last value is not included
-    temperatures = temperatures + [i]
-
-print len(temperatures)
-"""
-
-for i in range(100,185,5): #Note last value is not included
-    temperatures = temperatures + [i]
-
-temperatures = temperatures + [190]
-
-for i in range(180,95,-5): #Note last value is not included
-    temperatures = temperatures + [i]
-
-initial_db = 189+38
 
 masses = []
 #masses.append(['H2',4.387,8])
-masses.append(['OH',12.418,6])
-masses.append(['NH3',12.427,6])
-masses.append(['H2O',12.777,8])
-masses.append(['N2',15.89,8])
-masses.append(['O2',16.972,8])
-#masses.append(['N2O',19.874,10])
+masses.append(['OH',12.413,5])
+masses.append(['NH3',12.424,6])
+masses.append(['H2O',12.770,8])
+masses.append(['N2',15.8818,8])
+#masses.append(['NO',16.438,10])
+masses.append(['O2',16.967,8])
+#masses.append(['N2O',19.8699,10])
 

### 2012-04-15 python_figures/tof_raw.py

@@ -16,19 +16,19 @@ except:
 
 cursor = db.cursor()
 
-#SOMETHING WRONG WITH THE X-SCALE!!!!
+#Mass of NH3: 17.0265491
+#Mass of OH: 17.0027397
 
-#Mass of methanol: 32.0262147
-#Mass of oxygen: 31.9898292
+#Correct this expression to spectrum 403
 def MassToTime(mass):
-    time = 2.9870925856 * (mass**0.497621653202)
-    corr_time = time + 0.207
-    return corr_time
+    time = 2.98660484819 * (mass**0.4977024241071)
+    corr_time = time + 0.153
+    return corr_time 
 
 
 data = {}
 #Methanol + oxygen
-cursor.execute("SELECT x*1000000,y*1000 FROM xy_values_tof where measurement = 170")
+cursor.execute("SELECT x*1000000,y*1000 FROM xy_values_tof where measurement = 427")
 data['ch'] = np.array(cursor.fetchall())
 
 axis_array = []
@@ -61,20 +61,18 @@ mass_ticks = np.array([1,5,10,15,20,25,30,35,40])
 axis3 = axis.twiny()
 #axis3.plot(data['ch'][:,0],data['ch'][:,0]*0,'w-',linewidth=0) #Hack to create an invisible set on the extra x-axis
 axis3.set_xlim(0,20)
-print MassToTime(32.0262147)
+print MassToTime(2*1.0078250320)
 axis3.set_xticks(MassToTime(mass_ticks))
 axis3.set_xticklabels(mass_ticks)
 axis3.set_xlabel('Mass / amu', fontsize=8)
 axis3.tick_params(direction='in', length=2, width=1, colors='k',labelsize=8,axis='both',pad=3)
 #axis3.ticklabel_format(useOffset=False)
 
-axis.set_ylim(0,20)
-axis3.set_ylim(0,20)
-
+axis.set_ylim(0,150)
 
 p = axis.axvspan(0, 1, facecolor='#26aaf7', alpha=0.25)
-p = axis.axvspan(12, 13, facecolor='#b6fa77', alpha=0.25)
-p = axis.axvspan(16.9, 17, facecolor='#4599a7', alpha=0.25)
+p = axis.axvspan(12.4, 12.45, facecolor='#b6fa77', alpha=0.25)
+p = axis.axvspan(15.75, 17.1, facecolor='#25dd37', alpha=0.25)
 
[…]

### 2012-04-16 python_figures/ammonia_reactivity.py
Various bug-fixing and improvements to figures

@@ -106,7 +106,7 @@ for mass in config.masses:
     axis.plot(treated_data[mass[0]][:,2],treated_data[mass[0]][:,1], colors[i],label=mass[0],markersize=0.75)
     i = i + 1
 
-axis.set_xlabel('Time / min', fontsize=8)
+axis.set_xlabel('Time / min.', fontsize=8)
 axis.set_ylabel('Response / mV$\cdot$s', fontsize=8)
 
 
@@ -117,13 +117,13 @@ font = 8
 axis.annotate('H$_2$O', xy=(165, 2.3),  xycoords='data', xytext=(220, 2.8), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='top',fontsize=font,)
 axis.annotate('N$_2$', xy=(205, 1.5),  xycoords='data', xytext=(190, 2.1), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='top',fontsize=font,)
 axis.annotate('NH$_3$', xy=(50, 2.45),  xycoords='data', xytext=(55, 3), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='top',fontsize=font,)
-axis.annotate('OH', xy=(105, 0.16),  xycoords='data', xytext=(145, 0.4), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='top',fontsize=font,)
+axis.annotate('OH', xy=(95, 0.16),  xycoords='data', xytext=(145, 0.4), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='top',fontsize=font,)
 axis.annotate('O$_2$', xy=(105, 1.0),  xycoords='data', xytext=(95, 1.55), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='top',fontsize=font,)
-axis.annotate('Temp', xy=(150, 3.1),  xycoords='data', xytext=(140, 3.6), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='top',fontsize=font,)
+axis.annotate('Temp.', xy=(150, 3.1),  xycoords='data', xytext=(140, 3.6), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='top',fontsize=font,)
 
 axis2 = axis.twinx()
[…]

### 2012-04-16 python_figures/tof_raw.py

@@ -56,7 +56,7 @@ axis.set_ylim(0,20)
 axis.set_xlim(0,20)
 axis.set_xticks([2.5,5,7.5,10,12.5,15,17.5,20])
 
-mass_ticks = np.array([1,5,10,15,20,25,30,35,40])
+mass_ticks = np.array([1,2,5,10,15,20,25,30,35,40])
 
 axis3 = axis.twiny()
 #axis3.plot(data['ch'][:,0],data['ch'][:,0]*0,'w-',linewidth=0) #Hack to create an invisible set on the extra x-axis
@@ -67,12 +67,13 @@ axis3.set_xticklabels(mass_ticks)
 axis3.set_xlabel('Mass / amu', fontsize=8)
 axis3.tick_params(direction='in', length=2, width=1, colors='k',labelsize=8,axis='both',pad=3)
 #axis3.ticklabel_format(useOffset=False)
-
+axis.set_yticks((25,50,75,100,125))
 axis.set_ylim(0,150)
 
 p = axis.axvspan(0, 1, facecolor='#26aaf7', alpha=0.25)
-p = axis.axvspan(12.4, 12.45, facecolor='#b6fa77', alpha=0.25)
-p = axis.axvspan(15.75, 17.1, facecolor='#25dd37', alpha=0.25)
+p = axis.axvspan(3, 4.5, facecolor='#25dd37', alpha=0.25)
+p = axis.axvspan(12, 12.45, facecolor='#b6fa77', alpha=0.25)
+
 
 axis.tick_params(direction='in', length=6, width=1, colors='k',labelsize=8,axis='both',pad=3)
 axis.set_ylabel('Response / mV', fontsize=8)
@@ -87,39 +88,41 @@ axis.set_yticks((0,10,20,30,40))
 axis.plot(data['ch'][:,0], data['ch'][:,1], 'r-',linewidth=LINEWIDTH)
 p = axis.axvspan(0, 1, facecolor='#26aaf7', alpha=0.25)
 axis.set_xlim(0,1)
-axis.set_ylim(0,150)
+axis.set_ylim(0,50)
 axis.set_xticks([0.2,0.4,0.6,0.8])
 axis.tick_params(direction='in', length=6, width=1, colors='k',labelsize=8,axis='both',pad=3)
 
 
 axis = plt.subplot(gs[1,1])
 axis.set_ylabel('')
-axis.set_yticks((25,50,75,100,125))
[…]

### 2012-04-16 paper.tex
Adapted to new figures

@@
 The system design is superior to conventional batch and flow reactors with accompanying product detection by quadrupole mass spectrometry or gas chromatography not only due to the high sensitivity, fast temperature response, high mass resolution and fast acquisition time of mass spectra but it also allows wide mass range (0--5000\,amu in the current configuration).
-As a demonstration of the system we present data from ammonia oxidation on 5\,nm Pt nanoparticles showing resolved spectra of OH$^{+}$ and NH$_{3}^{+}$.
+As a demonstration of the system we present data from ammonia oxidation on a Pt thin film showing resolved spectra of OH$^{+}$ and NH$_{3}^{+}$.
 \end{abstract}
@@
 
-In Figure \ref{fig:untreated_data} an example spectrum of a methanol and atmospheric air mixture is shown.
-Here the high resolution of the TOF-MS is demonstrated by resolving methanol (CH$_3$OH) and molecular oxygen (O$_2$) which have a mass difference of 43\,milli-amu.
+In Figure \ref{fig:untreated_data} an example spectrum of ammonia oxidation (NH$_3$:O$_2$ 4:3, 195\,$^{circ}$C) is shown.
+Here the high resolution of the TOF-MS is demonstrated by resolving ammonia (NH$_3$) and molecular oxygen (O$_2$) which have a mass difference of 23\,milli-amu.
 \begin{figure}
  \includegraphics[width=16cm]{untreated_data.png}%
- \caption{Raw data acquired from the TOF-MS in a gas mixture of methanol and atmospheric air.
+ \caption{Raw data acquired from the TOF-MS during NH$_3$ oxidation by O$_2$ (NH$_3$:O$_2$ 4:3, 195\,$^{circ}$C).
 Subfigures show three different regions of the spectrum.
@@
 In the center subfigure the extremely good separation between individual masses is shown.
-It is evident that 1\,amu corresponds to approximately 350\,ns difference in flight time in our system in the mass regime around 20\,amu.
-In the last subfigure a zoom of the methanol and molecular oxygen (43\,milliamu mass difference) region is shown.\label{fig:untreated_data}}%
+It is evident that 1\,amu corresponds to approximately 850\,ns difference in flight time in our system in the mass regime around 1\,amu.
+In the last subfigure a zoom of the ammonia and hydroxyl peaks region shows separation between OH and NH$_3$ as well as O and NH$_2$  (23\,milliamu mass difference).\label{fig:untreated_data}}%
 \end{figure}
@@
 Typically, the model is used together with the experimental determination of a single mass since this will help fix the unknown delays originating from the measurement trigger, rise time of the high-voltage pulse at the repeller plate and cable delays.
-As seen in Figure~\ref{fig:model_error} the performance of the model is good despite its simplicity giving a total error in flight time estimation of $\sim$100\,ns at 70\,amu.
+As seen in Figure~\ref{fig:model_error} the performance of the model is good despite its simplicity giving a total error in flight time estimation of $\sim$10\,ns corresponding to $\sim$50\,milli-amu at 70\,amu.
 The model is written in Python and can be acquired online\cite{ModelGithub}.
@@
  \caption{Comparison of the simulated model (red line, top panel) to actual measured experimental values (blue dots).
-In the bottom panel the difference between acquired experimental data and data calculated from the model is plotted, errorbars represents only the uncertainty in the experimental data.
-As seen from the figure a deviation of $\sim$100\,ns at 70\,amu is present.\label{fig:model_error}}%
+In the lower panels the difference between acquired experimental data and data calculated from the model in time and mass units are shown.
+Error bars represents only the uncertainty in the experimental data.
+As seen from the lower panels a deviation of $\sim$10\,ns corresponding to $\sim$50\,milli-amu at 70\,amu is present.\label{fig:model_error}}%
 \end{figure}
@@
 \section{Oxidation of ammonia}
-To demonstrate the system capability ammonia oxidation on a 40\,\% geometrical coverage 5\,nm Pt nanoparticles has been used as test reaction.
+To demonstrate the system capability ammonia oxidation on a 1\,\% geometrical coverage Pt thin film has been used as test reaction.
 The catalytic oxidation of ammonia can proceed along primarily three different routes\cite{Imbihl2007}.
@@
 All of these systems are difficult to analyze both qualitatively and quantitatively due to the overlap of NH$_3$, which is a reactant, and OH$^+$ originating from cracking of H$_2$O, which is a product from the combustion and is a part of the residue gas.
-Specifically, hydroxyls (OH$^{+}$) from cracking of trace water in the system and the combustion reaction and the primary peak of ammonia (NH$_{3}^{+}$) are both detected at m/q$\simeq$17.
+Specifically, hydroxyls (OH$^{+}$) from cracking of trace water in the system and the combustion reaction and the primary peak of ammonia (NH$_{3}^{+}$) are both detected at $m/q\simeq17$.
 Without adequate mass resolution it is not possible to separate the two contributions resulting in difficult analysis.
 Often a charge to mass ratio without cracking from either products or residual gas in the system is used to quantify the amount of ammonia and water.
-In the case of ammonia, m/q=15 or m/q=8.5 is typically chosen since water does not contribute to these masses.
+In the case of ammonia, $m/q=15$ or $m/q=8.5$ is typically chosen since water does not contribute to these masses.
 However, both of these masses contains only a very small fraction of the main peak since it involves either the loss of two hydrogen atoms or a double charged ammonia molecule which are both processes with very low yields.

### 2012-04-17 paper.tex
Small corrections before sending to Ole and Ib second time

@@
 \usepackage{graphicx}
+%\usepackage{amssymb}
 %\documentclass[aip,reprint]{revtex4-1}
@@
 Gas analysis is performed with a time of flight mass spectrometer with a modified nude Bayard-Alpert ionization gauge as gas ionization source.
-The mass resolution of the time of flight mass spectrometer using the ion gauge as ionization source is estimated to m/$\Delta$m$>$2500.
-The system design is superior to conventional batch and flow reactors with accompanying product detection by quadrupole mass spectrometry or gas chromatography not only due to the high sensitivity, fast temperature response, high mass resolution and fast acquisition time of mass spectra but it also allows wide mass range (0--5000\,amu in the current configuration).
-As a demonstration of the system we present data from ammonia oxidation on a Pt thin film showing resolved spectra of OH$^{+}$ and NH$_{3}^{+}$.
+The mass resolution of the time of flight mass spectrometer using the ion gauge as ionization source is estimated to $m/\Delta m>2500$.
+The system design is superior to conventional batch and flow reactors with accompanying product detection by quadrupole mass spectrometry or gas chromatography not only due to the high sensitivity, fast temperature response, high mass resolution and fast acquisition time of mass spectra but it also allows wide mass range (\mbox{0--5000}\,amu in the current configuration).
+As a demonstration of the system we present data from ammonia oxidation on a Pt thin film showing resolved spectra of OH and NH$_{3}$.
 \end{abstract}
@@
 Typically, quadrupole mass spectrometers (QMSs) are used in low pressure regimes to analyze gas composition while gas chromatographs (GCs) are used for high pressure measurements.
-The QMS, however, suffers from a low mass resolution (m/$\Delta$m$>\sim$m up to m$\sim$200) which makes analysis of complicated spectra difficult and cumbersome.
-The QMS is additionally subject to a low mass range (typically $\sim$100-200\,amu) limiting general use.
+The QMS, however, suffers from a low mass resolution ($m/\Delta m>\sim m$ up to $m\sim200$) which makes analysis of complicated spectra difficult and cumbersome.
+The QMS is additionally subject to a low mass range (typically $\sim$\mbox{100--200}\,amu) limiting general use.
 Furthermore, QMSs are typically operated by logging a single (or a few) masses as a function of time to increase time resolution.
@@
 GCs have inherently low time resolution which make them unsuitable for fast time response measurements as in the case of microreactors and is in general difficult to use as mass spectrometers due to the difficult interpretation of complex mixtures.
-Furthermore, GCs only sample a very small part of converted gas making them unsuitable for small amounts of reactant and product gases due to the low sensitivity.
-As an alternative to GCs or QMSs time of flight mass spectrometers (TOF-MS) offer both high mass resolution ($\Delta$m/m$>$1000), fast acquisition of full mass spectra ($>$1\,Hz), high sensitivity making them suitable for very small amounts of catalyst, i.e.
+Furthermore, GCs only sample a very small part of the converted gas making them unsuitable for small amounts of reactant and product gases due to the low sensitivity.
+As an alternative to GCs or QMSs time of flight mass spectrometers (TOF-MS) offer both high mass resolution ($m/\Delta m>1000$), fast acquisition of full mass spectra ($>$1\,Hz), high sensitivity making them suitable for very small amounts of catalyst, i.e.
 model systems, and mass range only limited by the detector.
-For a standard available microchannel plate (MCP) used as detector a mass range of 0--5000\,amu can be obtained.
+For a standard available microchannel plate (MCP) used as detector a mass range of \mbox{0--5000}\,amu can be obtained.
 
-Typically TOF-MS in heterogeneous catalysis is used as a surface analytic tool, i.e.
+Typically, TOF-MS in heterogeneous catalysis is used as a surface analytic tool, i.e.
 TOF-SIMS\cite{Benninghoven1994,DeSmet1998,Grams2004,Johnson2010}.
@@
 The setup consists of three main components.
-The microreactor, where the catalyst under investigation is deposited, an ionization source which ionizes the gas from the microreactor and the TOF-MS used for gas analysis.
+The microreactor, where the catalyst under investigation is deposited an ionization source which ionizes the gas from the microreactor and TOF-MS used for gas analysis.
 A QMS is furthermore connected to the capillary of the microreactor which enables direct comparison between the QMS and TOF-MS.
@@
 From the source region the ions are pushed into the flight tube by a repelling voltage pulse and is after mass separation in the flight tube detected by a MCP.
-A schematic of the entire setup is shown in Figure \ref{fig:TOF_microreactor}.
+A schematic of the entire setup is shown in Figure~\ref{fig:TOF_microreactor}.
 \begin{figure}
@@
 \subsection{The microreactor platform}
-Catalyst characterization and performance evaluation is performed in a microreactor platform \cite{Henriksen2009}.
+Catalyst characterization and performance evaluation is performed in a microreactor\cite{Henriksen2009}.
 The microreactors are silicon-based and measures 20x16\,mm.
 The reactor consists of two gas inlets, a gas outlet, a reactor volume and a capillary used to restrict the gas flow from the reactor volume.
-The reactor volume is 3\,$\mu$m deep and 1 cm in diameter corresponding to a 236\,nL.
+The reactor volume is 3\,$\mu$m deep and 1 cm in diameter corresponding to a 236\,nL volume.
 The diffusion length of the reactants and products gases in the microreactor reactor volume is almost an order of magnitude longer than the radius of the reactor volume ensuring full contact of the gas with the catalyst.
@@
 The design ensures that all molecules or atoms entering the reactor volume, hence exposed to the catalyst under investigation, are detected by mass spectrometry ensuring high sensitivity.
+This feature makes the microreactors especially suited for characterization of model systems where small amounts of catalyst are typically used.
 
@@
 Currently, the system is configured in a 4+2 setup where 4 gases are connected to the first inlet and two gases connected to the secondary inlet.
-At the time of writing He, CO, O, CH$_4$, NH$_3$ and H$_2$ are connected to the setup.
+At the time of writing He, CO, O$_2$, CH$_4$, NH$_3$ and H$_2$ are connected to the setup.
 All gases used on the setup are N6 quality gases, i.e.
@@
 
-The time of flight equipment used for detection of gas molecules flown through the capillary of the microreactor is designed as an orthogonal mass spectrometer and is assembled from modules purchased from Jordan TOF Products, Inc\cite{JordanHomepage}.
+The time of flight equipment used for detection of gas molecules flown through the capillary of the microreactor is designed as an orthogonal mass spectrometer and is assembled from modules purchased from Jordan TOF Products, Inc.\cite{JordanHomepage}.
 
-Ionized ions enter the source of the TOF-MS through a series of entry Einzel lenses used for focusing the beam hence minimizing divergence.
+Ionized ions enter the source region of the TOF-MS through a series of entry Einzel lenses used for focusing the beam hence minimizing divergence.
 In the source the beam is pushed into the flight tube by an the initial repelling push voltage, $V_p$.
-The ions are further accelerated from ground potential to the liner potential, $V_L$.
+The ions are hereafter further accelerated from ground potential to the liner potential, $V_L$.
 Using this setup the drift velocity of an ion starting exactly from the center of the acceleration region is $V_L + V_p/2$.
@@
 The MCP used for ion detection is placed in the focal point of the reflectron giving maximum compensation for initial velocity dispersion.
-According to the manufacturer a resolution m/$\Delta$m$>\sim$4000 of the TOF has been shown.
+According to the manufacturer a resolution $m/\Delta m>\sim4000$ of the TOF-MS has been shown.
 
-The prize of the TOF including ionization, 8" 4-way cross, control electronics, data acquisition hardware and MCP detector is estimated to USD80000 which is comparable to a high quality QMS which is prized at approximately USD85000.
+The prize of the TOF including ionization gauge, 8" 4-way cross, control electronics, data acquisition hardware and MCP detector is estimated to USD80000 which is comparable to a high quality QMS which is prized at approximately USD85000.
 
-In Figure \ref{fig:untreated_data} an example spectrum of ammonia oxidation (NH$_3$:O$_2$ 4:3, 195\,$^{circ}$C) is shown.
+In Figure~\ref{fig:untreated_data} an example spectrum of ammonia oxidation (NH$_3$:O$_2$ 4:3, 195\,$^{\circ}$C) is shown.
 Here the high resolution of the TOF-MS is demonstrated by resolving ammonia (NH$_3$) and molecular oxygen (O$_2$) which have a mass difference of 23\,milli-amu.
@@
  \includegraphics[width=16cm]{untreated_data.png}%
- \caption{Raw data acquired from the TOF-MS during NH$_3$ oxidation by O$_2$ (NH$_3$:O$_2$ 4:3, 195\,$^{circ}$C).
+ \caption{Raw data acquired from the TOF-MS during NH$_3$ oxidation by O$_2$ (NH$_3$:O$_2$ 4:3, 195\,$^{\circ}$C).
 Subfigures show three different regions of the spectrum.
-From the first subfigure a delay between the acquisition trigger and the noise signal from the rise of the high voltage pulser of approximately 150\,ns can be seen.
+From the first subfigure in the lower panel a delay between the acquisition trigger and the noise signal from the rise of the high voltage pulser of approximately 150\,ns can be seen.
 This is due to delays in cables and the repeller pulser.
@@
 It is evident that 1\,amu corresponds to approximately 850\,ns difference in flight time in our system in the mass regime around 1\,amu.
-In the last subfigure a zoom of the ammonia and hydroxyl peaks region shows separation between OH and NH$_3$ as well as O and NH$_2$  (23\,milliamu mass difference).\label{fig:untreated_data}}%
+In the last subfigure a zoom of the ammonia and hydroxyl peaks region shows separation between OH and NH$_3$ as well as O and NH$_2$  (23\,milli-amu mass difference).\label{fig:untreated_data}}%
 \end{figure}
@@
 As ionization source of the gas flow from the microreactor capillary a modified nude UHV Bayard-Alpert ion gauge is used.
-A current approximately 3\,A is run through the filament resulting in 10\,mA emission current.
+A current of approximately 3\,A is run through the filament resulting in 10\,mA emission current.
 The grid is biased approximately 40\,V negative compared to the filament to accelerate electrons emitted from the filament towards the grid.
@@
 Using this configuration approximately half of the ionized ions are expected to leave the ionization gauge\cite{Nottingham1955}.
-The entire construction is placed in a small orifice which is differentially pumped by a turbo pump.
+The entire construction is placed in a flange with a small orifice which is differentially pumped by a turbo pump.
 Large amounts of gas can hence be dosed locally around the ion gauge while still maintaining a low pressure in the source region of the TOF-MS.
-The small orifice is essential in the setup to avoid high pressure in the acceleration region and drift tube of the TOF-MS which would cause an increase in dead counts on the MCP thus decrease the signal-to-noise ratio of the recorded signal.
+The small orifice is essential in the setup to avoid high pressure in the acceleration region and drift tube of the TOF-MS which would cause an increase in dead counts on the MCP thus decreasing the signal-to-noise ratio of the recorded signal.
 
 \subsubsection{Data treatment}
-Raw data plotted with accompanying gaussian fits are shown in Figure \ref{fig:gaussian_fit}.
-Here the closely lying peaks from OH$^{+}$ from cracking of both residue water and water as reaction product and uncombusted NH$_3^{+}$ is shown.
+Raw data plotted with accompanying gaussian fits are shown in Figure~\ref{fig:gaussian_fit}.
+Here the closely lying peaks from OH from cracking of both residue water and water as reaction product and uncombusted NH$_3$ is shown.
 The ability to separate these contributions substantially simplifies quantification of ammonia and allows for easier characterization of catalyst performance.
@@
  \includegraphics[width=14cm]{ammonia_OH_gauss_fit.png}%
- \caption{Example of two gaussian fits (dashed red lines) and the sum of the two fits (green solid line) to a double peak consisting of NH$_{3}^{+}$ and OH$^{+}$ both at approximately 17\,amu demonstrating the resolution of the TOF-MS.
+ \caption{Example of two gaussian fits (dashed red lines) and the sum of the two fits (green solid line) to a double peak consisting of NH$_{3}$ and OH both at approximately 17\,amu demonstrating the resolution of the TOF-MS.
 The entire graph section represents a mass difference of 100\,milli-amu.\label{fig:gaussian_fit}}%
 \end{figure}
-In Figure \ref{fig:dynamic_range} raw data from water, hydrogen and oxygen from three different regions is shown illustrating the dynamic range of the TOF-MS.
+
+In Figure~\ref{fig:dynamic_range} raw data from water, hydrogen and oxygen from three different regions is shown illustrating the dynamic range of the TOF-MS.
 At constant MCP voltage all the peaks are clearly visible although the ratio of the oxygen to water amplitude is $\sim$400.
@@
 In reality the dynamic range is limited mostly by the data acquisition hardware as well as the quality of the ion source.
-Even with the home-built ionization source and a 8-bit digitizer the dynamic range is from Figure~\ref{fig:dynamic_range} estimated to $\sim$1000 using an integration time of $\sim$5\,s.
+Even with the home-built ionization source and a 8-bit digitizer the dynamic range is from Figure~\ref{fig:dynamic_range} estimated to $\sim1000$ using an integration time of $\sim5$\,s.
 The dynamic range of the TOF-MS is hence comparable to the dynamic range offered by a QMS at constant preamplifier range while covering a much larger mass range.
-The TOF-MS, however, acquires mass spectra (0--5000\,amu) with high frequency ($>1$\,Hz) which is impossible with a QMS where only a few masses can be followed as a function of time to increase time resolution.
+The TOF-MS, however, acquires mass spectra (\mbox{0--5000}\,amu) with high frequency ($>1$\,Hz) which is impossible with a QMS where only a few masses can be followed as a function of time to increase time resolution.
 The possibility of fast acquisition of complete mass spectra by the TOF-MS thus ensures that all masses are monitored simultaneously during the experiment.
@@
 This approach is in some cases adequate but does have the significant drawback that several peaks of well known masses must be present in the flight spectrum which is not always necessarily feasible.
-To determine the relationship between mass and flight time we have made a numeric model of the mass spectrometer which calculates the flight time based only on the voltages for the pulser, $V_p$, liner, $V_L$, and reflectron, $V_{R1}$ and $V_{R2}$, and thus provides a relationship of flight time to mass.
+To determine the relationship between mass and flight time we have made a numeric model of the TOF-MS which calculates the flight time based only on the voltages for the pulser, $V_p$, liner, $V_L$, and reflectron, $V_{R1}$ and $V_{R2}$, and thus provides a relationship of flight time to mass.
 Typically, the model is used together with the experimental determination of a single mass since this will help fix the unknown delays originating from the measurement trigger, rise time of the high-voltage pulse at the repeller plate and cable delays.
@@
 \end{equation}
-All of these systems are difficult to analyze both qualitatively and quantitatively due to the overlap of NH$_3$, which is a reactant, and OH$^+$ originating from cracking of H$_2$O, which is a product from the combustion and is a part of the residue gas.
-Specifically, hydroxyls (OH$^{+}$) from cracking of trace water in the system and the combustion reaction and the primary peak of ammonia (NH$_{3}^{+}$) are both detected at $m/q\simeq17$.
+All of these systems are difficult to analyze both qualitatively and quantitatively due to the overlap of NH$_3$, which is a reactant, and OH originating from cracking of H$_2$O, which is a product from the combustion and is a part of the residue gas.
+Specifically, hydroxyls (OH) from cracking of trace water in the system and the combustion reaction and the primary peak of ammonia (NH$_{3}$) are both detected at $m/q\simeq17$.
 Without adequate mass resolution it is not possible to separate the two contributions resulting in difficult analysis.
@@
  \includegraphics[width=14cm]{ammonia_reactivity.png}%
- \caption{Ammonia oxidation as a function of temperature on a 40\,\% geometrical coverage 5\,nm Pt nanoparticles.
+ \caption{Ammonia oxidation as a function of temperature on a 1\,\% geometrical coverage Pt thin film.
 As the temperature is increased ammonia is oxidized to H$_2$O and N$_2$.
-Furthermore, the OH and NH$_3$ signal is anticorrelated demonstrating the ability to resolve these two close lying masses as shown in Figure \ref{fig:gaussian_fit}.\label{fig:ammonia_reactivity}}%
+Furthermore, the OH and NH$_3$ signal is anticorrelated demonstrating the ability to resolve these two close lying masses as shown in Figure~\ref{fig:gaussian_fit}.\label{fig:ammonia_reactivity}}%
 \end{figure}
 In Figure~\ref{fig:ammonia_reactivity} the integrated N$_2$, NH$_3$, H$_2$O, O$_2$ and OH peaks acquired from the raw TOF-MS spectrum as a function of temperature are shown.
-At each individual temperature step a mass scan is performed from triggering of the acceleration pulse up to 25\,$\mu$s of flight time corresponding to 70 amu.
-As seen from Figure~\ref{fig:ammonia_reactivity} the combustion of NH$_3$ increases substantially at approximately 140\,$^{\circ}$C.
+At each individual temperature step a mass scan is performed from triggering of the acceleration pulse up to 25\,$\mu$s of flight time corresponding to 70\,amu.
+As seen from Figure~\ref{fig:ammonia_reactivity} the combustion of NH$_3$ increases substantially at approximately 200\,$^{\circ}$C and drops again at approximately 175\,$^{\circ}$C.
 The combustion of ammonia to molecular nitrogen and water at this temperature agrees well with literature\cite{Imbihl2007,Zeng2009}.
 
-In Figure \ref{fig:ammonia_reactivity} an anticorrelation between OH$^{+}$ and NH$_3^+$ is seen.
+In Figure~\ref{fig:ammonia_reactivity} an anticorrelation between OH and NH$_3$ is seen.
 The inverse relation between these two masses can only be measured because these peaks are resolved in the mass spectrum.
-As expected a strong correlation between H$_2$O$^{+}$ and OH$^+$ is seen as a direct result of water cracking to hydroxyls.
+As expected a strong correlation between H$_2$O and OH is seen as a direct result of water cracking to hydroxyls.
 The data shown in Figure~\ref{fig:ammonia_reactivity} hence demonstrates the usability of the combined microreactor and TOF-MS setup especially simplifying data analysis of complicated mass spectra while maintaining a high sensitivity from the microreactor platform.
@@
 
-As a demonstration of the system ammonia oxidation on 5\,nm Pt nanoparticles was performed.
-The ability to resolve OH$^{+}$ and NH$_3^+$ which is separated by 23\,milli-amu was demonstrated.
+As a demonstration of the system ammonia oxidation on 1\,\% geometrical coverage Pt thin film was performed.
+The ability to resolve OH and NH$_3$ which is separated by 23\,milli-amu was demonstrated.
 The resolution of reactants and products enables simple and straightforward quantification of the ammonia and water signal.
 This greatly simplifies the analysis compared to conventional QMSs used for gas analysis.
-The setup is furthermore superior to conventional QMSs where the mass range is limited to $\sim$500\,amu and can be applied to the study of small amounts of catalysts.
+The setup is furthermore superior to conventional QMSs where the mass range is limited to $\sim500$\,amu and can be applied to the study of small amounts of catalysts.
 

### 2012-04-17 paper.tex
Small corrections, typos etc.

@@
 Ions are separated in the field free region and focused by the reflectron.
-Subsequently the ions are detected by the MCP.\label{fig:TOF_microreactor}}%
+The ions are subsequently detected by the MCP.\label{fig:TOF_microreactor}}%
 \end{figure}
@@
 The reactor consists of two gas inlets, a gas outlet, a reactor volume and a capillary used to restrict the gas flow from the reactor volume.
-The reactor volume is 3\,$\mu$m deep and 1 cm in diameter corresponding to a 236\,nL volume.
+The reactor volume is 3\,$\mu m$ deep and 1\,cm in diameter corresponding to a 236\,nL volume.
 The diffusion length of the reactants and products gases in the microreactor reactor volume is almost an order of magnitude longer than the radius of the reactor volume ensuring full contact of the gas with the catalyst.
@@
  \includegraphics[width=14cm]{dynamic_range.png}%
- \caption{Gaussian fits to three different mass to charge ratios from the same mass spectrum (integrated area indicated in each panel).
+ \caption{Gaussian fits (red solid line) to three different mass to charge ratios (blue points) from the same mass spectrum (integrated area indicated in each panel).
 As seen from the response a high dynamic range of the TOF-MS all yielding good gaussian fits.
@@
 In Figure~\ref{fig:ammonia_reactivity} the integrated N$_2$, NH$_3$, H$_2$O, O$_2$ and OH peaks acquired from the raw TOF-MS spectrum as a function of temperature are shown.
-At each individual temperature step a mass scan is performed from triggering of the acceleration pulse up to 25\,$\mu$s of flight time corresponding to 70\,amu.
+At each individual temperature step a mass scan is performed from triggering of the acceleration pulse up to 25\,$\mu s$ of flight time corresponding to 70\,amu.
 As seen from Figure~\ref{fig:ammonia_reactivity} the combustion of NH$_3$ increases substantially at approximately 200\,$^{\circ}$C and drops again at approximately 175\,$^{\circ}$C.

### 2012-04-17 paper.tex
Included small corrections from Thomas Pedersen

@@
 
-The microreactor is heated by joule heating of a 50\,nm platinum strip evaporated through a shadow mask on the backside of the chip.
+The microreactor is heated by joule heating of a 100\,nm platinum strip (on top of a 3\,nm Ti adhesion layer) evaporated through a shadow mask on the backside of the chip .
 The heating element is contacted by two pogo pins which are connected to a power supply.

### 2012-04-18 paper.tex
Incorporated Ole's corrections

@@
 \usepackage{graphicx}
-%\usepackage{amssymb}
+\usepackage{amssymb}
 %\documentclass[aip,reprint]{revtex4-1}
@@
 The system design is superior to conventional batch and flow reactors with accompanying product detection by quadrupole mass spectrometry or gas chromatography not only due to the high sensitivity, fast temperature response, high mass resolution and fast acquisition time of mass spectra but it also allows wide mass range (\mbox{0--5000}\,amu in the current configuration).
-As a demonstration of the system we present data from ammonia oxidation on a Pt thin film showing resolved spectra of OH and NH$_{3}$.
+As a demonstration of the system performance we present data from ammonia oxidation on a Pt thin film showing resolved spectra of OH and NH$_{3}$.
 \end{abstract}
@@
 Typically, quadrupole mass spectrometers (QMSs) are used in low pressure regimes to analyze gas composition while gas chromatographs (GCs) are used for high pressure measurements.
-The QMS, however, suffers from a low mass resolution ($m/\Delta m>\sim m$ up to $m\sim200$) which makes analysis of complicated spectra difficult and cumbersome.
+The QMS, however, suffers from a low mass resolution ($m/\Delta m\gtrsim m$ up to $m\sim200$) which makes analysis of complicated spectra difficult and cumbersome.
 The QMS is additionally subject to a low mass range (typically $\sim$\mbox{100--200}\,amu) limiting general use.
@@
 This is at the expense of acquisition of full mass spectra during the experiment limiting operation by potentially losing interesting features in other masses not monitored.
-GCs have inherently low time resolution which make them unsuitable for fast time response measurements as in the case of microreactors and is in general difficult to use as mass spectrometers due to the difficult interpretation of complex mixtures.
+GCs have inherently low time resolution which make them unsuitable for fast time response measurements as in the case of microreactors and are in general difficult to use as mass spectrometers due to the difficult interpretation of measurements on complex mixtures.
 Furthermore, GCs only sample a very small part of the converted gas making them unsuitable for small amounts of reactant and product gases due to the low sensitivity.
-As an alternative to GCs or QMSs time of flight mass spectrometers (TOF-MS) offer both high mass resolution ($m/\Delta m>1000$), fast acquisition of full mass spectra ($>$1\,Hz), high sensitivity making them suitable for very small amounts of catalyst, i.e.
-model systems, and mass range only limited by the detector.
-For a standard available microchannel plate (MCP) used as detector a mass range of \mbox{0--5000}\,amu can be obtained.
+As an alternative to GCs or QMSs time of flight mass spectrometers (TOF-MS) offer both high mass resolution ($m/\Delta m>1000$), fast acquisition of full mass spectra ($>$1\,Hz) and high sensitivity making them suitable for characterization of very small amounts of catalyst, i.e.
+model systems, and a mass range only limited by the detector.
+With a standard available microchannel plate (MCP) used as detector a mass range of \mbox{0--5000}\,amu can be obtained.
 
@@
 The setup consists of three main components.
-The microreactor, where the catalyst under investigation is deposited an ionization source which ionizes the gas from the microreactor and TOF-MS used for gas analysis.
-A QMS is furthermore connected to the capillary of the microreactor which enables direct comparison between the QMS and TOF-MS.
+The microreactor, where the catalyst under investigation is deposited, an ionization source which ionizes the gas from the microreactor and a TOF-MS used for gas analysis.
+In addition a QMS is connected to the capillary of the microreactor which enables direct comparison between the QMS and TOF-MS.
 
@@
 The reactor consists of two gas inlets, a gas outlet, a reactor volume and a capillary used to restrict the gas flow from the reactor volume.
-The reactor volume is 3\,$\mu m$ deep and 1\,cm in diameter corresponding to a 236\,nL volume.
+The reactor volume is 3\,$\mu$m deep and 1\,cm in diameter corresponding to a 236\,nL volume.
 The diffusion length of the reactants and products gases in the microreactor reactor volume is almost an order of magnitude longer than the radius of the reactor volume ensuring full contact of the gas with the catalyst.
-This has been proven to hold by reproducible CO oxidation on Pt spots located at different points in the the reactor volume.
+This has been proven to hold by reproducible CO oxidation measurements on small Pt spots located at different points in the the reactor volume.
 The two gas inlets are combined on the chip where the inlet gases mix by diffusion.
-The capillary is designed such that approximately $3\times10^{14}$\,molecules$\cdot$s$^{-1}$ is probed from the reactor volume when operated at 1\,bar.
+The capillary is designed such that approximately $3\times10^{14}$\,molecules$\cdot$s$^{-1}$ are probed from the reactor volume when operated at 1\,bar.
 Any surplus of gas from the two inlets that does not enter the reactor volume is directed through an outlet to a turbo pump.
-The design ensures that all molecules or atoms entering the reactor volume, hence exposed to the catalyst under investigation, are detected by mass spectrometry ensuring high sensitivity.
-This feature makes the microreactors especially suited for characterization of model systems where small amounts of catalyst are typically used.
+The design ensures that all molecules or atoms entering the reactor volume, and hence exposed to the catalyst under investigation, are detected by mass spectrometry ensuring high sensitivity.
+This feature makes the microreactors especially well suited for characterization of model systems where small amounts of catalyst are typically used.
 
@@
 \subsection{Gas handling for the microreactor}
-The two gas inlets on the microreactor chip is connected to a macroscopic gas handling system which is constructed entirely from UHV compatible elements to ensure extremely clean gas handling.
+The two gas inlets on the microreactor chip are connected to a macroscopic gas handling system which is constructed entirely from UHV compatible elements to ensure extremely clean gas handling.
 A total of 6 gases with accompanying flow controllers are used to control the inlet gas flow to the microreactor.
@@
 The time of flight chamber is pumped by a turbo pump and two ion pumps.
-A 120\,l/s ion pump is used to pump the flight tube while a 400\,l/s ion pump and a 450\,l/s turbo pump is used to pump down the source region which is mounted on a 8" 4-way cross.
-Opposite the source region of the TOF-MS the pumps are mounted while the two remaining flanges are occupied by the ionization gauge and a blanked flange (see Figure~\ref{fig:TOF_microreactor}).
+A 120\,l/s ion pump is used to pump the flight tube while a 400\,l/s ion pump and a 450\,l/s turbo pump are used to pump down the source region which is mounted on a 8" 4-way cross.
+Opposite to the source region of the TOF-MS the pumps are mounted while the two remaining flanges are occupied by the ionization gauge and a blanked flange (see Figure~\ref{fig:TOF_microreactor}).
 While idling the pressure in the source region is $\sim1\times10^{-9}$\,mbar and $\sim2\times10^{-9}$\,mbar in the flight tube.
@@
 
-Ionized ions enter the source region of the TOF-MS through a series of entry Einzel lenses used for focusing the beam hence minimizing divergence.
-In the source the beam is pushed into the flight tube by an the initial repelling push voltage, $V_p$.
+Ions enter the source region of the TOF-MS through a series of entry Einzel lenses used for focusing the beam hence minimizing divergence.
+In the source the beam is pushed into the flight tube by an initial repelling push voltage, $V_p$.
 The ions are hereafter further accelerated from ground potential to the liner potential, $V_L$.
-Using this setup the drift velocity of an ion starting exactly from the center of the acceleration region is $V_L + V_p/2$.
-At the end of the flight tube a reflectron is installed which is controlled by voltages $V_{R1}$ and $V_{R2}$.
+Using this setup the drift velocity of an ion starting exactly from the center of the acceleration region corresponds to an energy of $Ze\left(V_L + V_p/2\right)$ where $Ze$ is the charge of the ion.
+At the end of the flight tube a reflectron is installed.
+The reflectron is controlled by voltages $V_{R1}$ and $V_{R2}$.
 The reflectron has two primary purposes: i) The effective drift length is increased hence increasing the resolution of the TOF-MS.
@@
 The MCP used for ion detection is placed in the focal point of the reflectron giving maximum compensation for initial velocity dispersion.
-According to the manufacturer a resolution $m/\Delta m>\sim4000$ of the TOF-MS has been shown.
+According to the manufacturer a resolution $m/\Delta m\gtrsim4000$ of the TOF-MS has been shown.
 
@@
 In Figure~\ref{fig:untreated_data} an example spectrum of ammonia oxidation (NH$_3$:O$_2$ 4:3, 195\,$^{\circ}$C) is shown.
-Here the high resolution of the TOF-MS is demonstrated by resolving ammonia (NH$_3$) and molecular oxygen (O$_2$) which have a mass difference of 23\,milli-amu.
+Here the high resolution of the TOF-MS is demonstrated by resolving ammonia (NH$_3$) and hydroxyl (OH) which have a mass difference of 23\,milli-amu.
 \begin{figure}
@@
 Raw data plotted with accompanying gaussian fits are shown in Figure~\ref{fig:gaussian_fit}.
-Here the closely lying peaks from OH from cracking of both residue water and water as reaction product and uncombusted NH$_3$ is shown.
+Here the closely lying peaks from OH due to cracking of both residue water and water as reaction product and uncombusted NH$_3$ is shown.
 The ability to separate these contributions substantially simplifies quantification of ammonia and allows for easier characterization of catalyst performance.
@@
  \includegraphics[width=14cm]{ammonia_OH_gauss_fit.png}%
- \caption{Example of two gaussian fits (dashed red lines) and the sum of the two fits (green solid line) to a double peak consisting of NH$_{3}$ and OH both at approximately 17\,amu demonstrating the resolution of the TOF-MS.
+ \caption{Example of two gaussian fits (dashed red lines) and the sum of the two fits (green solid line) to a double peak (blue dots) consisting of NH$_{3}$ and OH both at approximately 17\,amu demonstrating the resolution of the TOF-MS.
 The entire graph section represents a mass difference of 100\,milli-amu.\label{fig:gaussian_fit}}%
@@
 
-In Figure~\ref{fig:dynamic_range} raw data from water, hydrogen and oxygen from three different regions is shown illustrating the dynamic range of the TOF-MS.
+In Figure~\ref{fig:dynamic_range} raw data from water, hydrogen and oxygen from three different regions are shown illustrating the dynamic range of the TOF-MS.
 At constant MCP voltage all the peaks are clearly visible although the ratio of the oxygen to water amplitude is $\sim$400.
@@
  \caption{Gaussian fits (red solid line) to three different mass to charge ratios (blue points) from the same mass spectrum (integrated area indicated in each panel).
-As seen from the response a high dynamic range of the TOF-MS all yielding good gaussian fits.
+As seen from the response a high dynamic range of the TOF-MS is demonstrated by good gaussian fits to all peaks.
 The TOF-MS can hence be used to monitor both very small and very large signal masses.
@@
 In reality the dynamic range is limited mostly by the data acquisition hardware as well as the quality of the ion source.
-Even with the home-built ionization source and a 8-bit digitizer the dynamic range is from Figure~\ref{fig:dynamic_range} estimated to $\sim1000$ using an integration time of $\sim5$\,s.
+Even with the home-built ionization source and a 8-bit digitizer the dynamic range is, from Figure~\ref{fig:dynamic_range}, estimated to $\sim1000$ using an integration time of $\sim5$\,s.
 The dynamic range of the TOF-MS is hence comparable to the dynamic range offered by a QMS at constant preamplifier range while covering a much larger mass range.
-The TOF-MS, however, acquires mass spectra (\mbox{0--5000}\,amu) with high frequency ($>1$\,Hz) which is impossible with a QMS where only a few masses can be followed as a function of time to increase time resolution.
+The TOF-MS, however, acquires mass spectra (\mbox{0--5000}\,amu) at high frequency ($>1$\,Hz) which is impossible with a QMS where only a few masses can be followed as a function of time to increase time resolution.
 The possibility of fast acquisition of complete mass spectra by the TOF-MS thus ensures that all masses are monitored simultaneously during the experiment.
@@
 
-Since the TOF-MS only measures flight time and not the actual mass of the measured molecules or atoms it is necessary to determine the relationship between flight time and actual mass.
+Since the TOF-MS only measures flight time and not the actual mass of the measured ions it is necessary to determine the relationship between flight time and actual mass.
 This can be done by calibration masses expressing known patterns in the mass spectrum.
-In this way masses can be reasonably determined with subsequent fitting of these values to get an expression for the flight time as a function of mass.
-This approach is in some cases adequate but does have the significant drawback that several peaks of well known masses must be present in the flight spectrum which is not always necessarily feasible.
+In this way masses can be reasonably well determined with subsequent fitting of these values to get an expression for the flight time as a function of mass.
+This approach is in some cases adequate but has the significant drawback that several peaks of well known masses must be present in the flight spectrum which is not always necessarily feasible.
 To determine the relationship between mass and flight time we have made a numeric model of the TOF-MS which calculates the flight time based only on the voltages for the pulser, $V_p$, liner, $V_L$, and reflectron, $V_{R1}$ and $V_{R2}$, and thus provides a relationship of flight time to mass.
@@
  \includegraphics[width=14cm]{model_error.png}%
- \caption{Comparison of the simulated model (red line, top panel) to actual measured experimental values (blue dots).
+ \caption{Comparison of the simulated model (red curve, top panel) to actual measured experimental values (blue dots) of flight time as a function of mass.
 In the lower panels the difference between acquired experimental data and data calculated from the model in time and mass units are shown.
@@
 Without adequate mass resolution it is not possible to separate the two contributions resulting in difficult analysis.
-Often a charge to mass ratio without cracking from either products or residual gas in the system is used to quantify the amount of ammonia and water.
+Often a charge to mass ratio without cracking from both products and residual gas in the system is used to quantify the amount of ammonia and water.
 In the case of ammonia, $m/q=15$ or $m/q=8.5$ is typically chosen since water does not contribute to these masses.
-However, both of these masses contains only a very small fraction of the main peak since it involves either the loss of two hydrogen atoms or a double charged ammonia molecule which are both processes with very low yields.
+However, both of these masses contains only a very small fraction of the main peak since it involves either the loss of two hydrogen atoms or a double charged ammonia ion which are both formed in processes with very low yields.
 The measurement of these masses have a very poor signal to noise ratio making measurements on ammonia very difficult with traditional mass spectrometry methods.
@@
 As the temperature is increased ammonia is oxidized to H$_2$O and N$_2$.
-Furthermore, the OH and NH$_3$ signal is anticorrelated demonstrating the ability to resolve these two close lying masses as shown in Figure~\ref{fig:gaussian_fit}.\label{fig:ammonia_reactivity}}%
+Furthermore, the OH and NH$_3$ signals are anticorrelated demonstrating the ability to resolve these two close lying masses as shown in Figure~\ref{fig:gaussian_fit}.\label{fig:ammonia_reactivity}}%
 \end{figure}
@@
 As seen from Figure~\ref{fig:ammonia_reactivity} the combustion of NH$_3$ increases substantially at approximately 200\,$^{\circ}$C and drops again at approximately 175\,$^{\circ}$C.
-The combustion of ammonia to molecular nitrogen and water at this temperature agrees well with literature\cite{Imbihl2007,Zeng2009}.
+The combustion of ammonia to molecular nitrogen and water in this temperature range agrees well with literature\cite{Imbihl2007,Zeng2009}.
 
@@
 
-%BØR VI LAVE ET ARRHENIUS PLOT??
-%For ammonia oxidation both N$_2$O (m/q = 44), NO (m/q = 30) and NO$_2$ (m/q = 46) are of interest.
-
-\section{Summary}
+\section{Conclusion}
 We have demonstrated a combined microreactor and TOF-MS system which can be employed to test and characterize model heterogeneous catalysts.
@@
 
-As a demonstration of the system ammonia oxidation on 1\,\% geometrical coverage Pt thin film was performed.
+As a demonstration of the system performance ammonia oxidation on 1\,\% geometrical coverage Pt thin film was performed.
 The ability to resolve OH and NH$_3$ which is separated by 23\,milli-amu was demonstrated.
-The resolution of reactants and products enables simple and straightforward quantification of the ammonia and water signal.
+The resolution of reactants and products enables simple and straightforward quantification of the ammonia and water signals.
 This greatly simplifies the analysis compared to conventional QMSs used for gas analysis.

### 2012-04-18 python_figures/tof_raw.py

@@ -72,7 +72,7 @@ axis.set_ylim(0,150)
 
 p = axis.axvspan(0, 1, facecolor='#26aaf7', alpha=0.25)
 p = axis.axvspan(3, 4.5, facecolor='#25dd37', alpha=0.25)
-p = axis.axvspan(12, 12.45, facecolor='#b6fa77', alpha=0.25)
+p = axis.axvspan(12, 12.46, facecolor='#b6fa77', alpha=0.25)
 
 
 axis.tick_params(direction='in', length=6, width=1, colors='k',labelsize=8,axis='both',pad=3)
@@ -113,11 +113,11 @@ axis.set_ylabel('')
 axis.set_yticks((25,50,75,100,125))
 #axis.set_xticks((12,12.5))
 axis.plot(data['ch'][:,0], data['ch'][:,1], 'r-',linewidth=LINEWIDTH)
-axis.set_xlim(12,12.45)
+axis.set_xlim(12,12.46)
 axis.set_ylim(0,150)
 axis.set_xticks([12.1,12.2,12.3,12.4])
 axis.ticklabel_format(useOffset=False)
-p = axis.axvspan(12, 12.45, facecolor='#b6fa77', alpha=0.25)
+p = axis.axvspan(12, 12.46, facecolor='#b6fa77', alpha=0.25)
 axis.tick_params(direction='in', length=6, width=1, colors='k',labelsize=8,axis='both',pad=3)
 axis.annotate('O', xy=(12.04, 10),  xycoords='data', xytext=(12.04, 67), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='top',fontsize=font,)
 axis.annotate('NH$_2$', xy=(12.055, 47),  xycoords='data', xytext=(12.2, 75), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='top',fontsize=font,)

### 2012-04-18 paper.tex
Added trajectory.png to the paper

@@
 The reflectron has two primary purposes: i) The effective drift length is increased hence increasing the resolution of the TOF-MS.
-ii) The reflectron works as a focusing lens compensating for any initial velocity dispersion of the ions, i.e.
+ii) The reflectron works as a focusing lens (cf.
+Figure~\ref{fig:trajectory}) compensating for any initial velocity dispersion of the ions, i.e.
 ions with an initial higher velocity will have an increased flight length compared to slower ions.
@@
 According to the manufacturer a resolution $m/\Delta m\gtrsim4000$ of the TOF-MS has been shown.
+\begin{figure}
+ \includegraphics[width=16cm]{trajectory.png}%
+ \caption{Simulated trajectories of ions with initial position variations in the source region illustrating the focusing effect of the reflectron.
+Red curve corresponds to ions with an initial position in the center of the source region while blue and green curves illustrate trajectories of ions with non-ideal initial positions displaced 6.3\,mm towards and further away from the repelling plate, respectively.
+Insert shows the difference between displaced ions and the center positioned ion.
+The models does not include initial velocity dispersion of the ions.\label{fig:trajectory}}%
+\end{figure}
 

### 2012-04-22 paper.tex
Incorporated corrections from Ib except changing system overview figure

@@
 The QMS, however, suffers from a low mass resolution ($m/\Delta m\gtrsim m$ up to $m\sim200$) which makes analysis of complicated spectra difficult and cumbersome.
-The QMS is additionally subject to a low mass range (typically $\sim$\mbox{100--200}\,amu) limiting general use.
+The QMS is additionally subject to a mass dependent transmission (typically $\propto m^{-1}$ ) limiting general use.
 Furthermore, QMSs are typically operated by logging a single (or a few) masses as a function of time to increase time resolution.
@@
 The heating strip can in this way be used as a resistance temperature detector (RTD) to determine the temperature of the chip.
-In the current configuration temperatures from room temperature to approximately 450\,$^{\circ}$C can be reached.
+Currently, temperatures from room temperature to approximately 450\,$^{\circ}$C can be reached due to apparatus limitations.
+The high temperature limit is expected to be $\sim600$\,$^{\circ}$C where the pyrex lid used for sealing the reactor will melt.
 
@@
 
-The prize of the TOF including ionization gauge, 8" 4-way cross, control electronics, data acquisition hardware and MCP detector is estimated to USD80000 which is comparable to a high quality QMS which is prized at approximately USD85000.
+The prize of the TOF including ionization gauge, 8" 4-way cross, control electronics, data acquisition hardware and MCP detector is comparable to the prize of a high quality QMS with electronics making the TOF-MS a serious alternative to a QMS.
 
@@
 In the center subfigure the extremely good separation between individual masses is shown.
-It is evident that 1\,amu corresponds to approximately 850\,ns difference in flight time in our system in the mass regime around 1\,amu.
+It is evident that 1\,amu corresponds to approximately 1.4\,$\mu$s difference in flight time in our system in the mass regime around 1\,amu.
 In the last subfigure a zoom of the ammonia and hydroxyl peaks region shows separation between OH and NH$_3$ as well as O and NH$_2$  (23\,milli-amu mass difference).\label{fig:untreated_data}}%
@@
 This greatly simplifies the analysis compared to conventional QMSs used for gas analysis.
-The setup is furthermore superior to conventional QMSs where the mass range is limited to $\sim500$\,amu and can be applied to the study of small amounts of catalysts.
+The setup is furthermore superior to conventional QMSs where only a limited mass resolution at high masses can be obtained and can be applied to the study of small amounts of catalysts.
 
-%\section{Acknowledgements}
+\section{Acknowledgements}
+This work was carried out as part of the Catalysis for Sustainable Energy initiative, which is funded by the Danish Ministry of Science, Technology and Innovation.
+The Center for Individual Nanoparticle Functionality is funded by the Danish National Research Foundation.
 

### 2012-04-23 python_figures/ammonia_OH_gauss_fit.py
Checked in Ibs corrections and fixed some figure-sizes

@@ -27,7 +27,7 @@ fig = plt.figure()
 fig.subplots_adjust(bottom=0.2) # Make room for x-label
 fig.subplots_adjust(top=0.8) # Make room for extra x-label
 ratio = 0.4                     # This figure should be very wide to span two columns
-fig_width = 10
+fig_width = 14
 fig_width = fig_width /2.54     # width in cm converted to inches
 fig_height = fig_width*ratio
 fig.set_size_inches(fig_width,fig_height)

### 2012-04-23 python_figures/dynamic_range.py

@@ -24,7 +24,7 @@ fig.subplots_adjust(top=0.9) # Make room for extra x-label
 fig.subplots_adjust(wspace=0.25)
 fig.subplots_adjust(hspace=0.25)
 ratio = 0.6
-fig_width = 12
+fig_width = 14
 fig_width = fig_width /2.54     # width in cm converted to inches
 fig_height = fig_width*ratio
 fig.set_size_inches(fig_width,fig_height)

### 2012-04-23 python_figures/tof_raw.py

@@ -41,7 +41,7 @@ arrow = dict(facecolor='black',arrowstyle='->')
 font = 8
 
 ratio = 0.4                     # This figure should be very wide to span two columns
-fig_width = 17
+fig_width = 16
 fig_width = fig_width /2.54     # width in cm converted to inches
 fig_height = fig_width*ratio
 fig.set_size_inches(fig_width,fig_height)

### 2012-04-23 python_figures/ammonia_OH_gauss_fit.py
Changed figure sizes

@@ -27,7 +27,7 @@ fig = plt.figure()
 fig.subplots_adjust(bottom=0.2) # Make room for x-label
 fig.subplots_adjust(top=0.8) # Make room for extra x-label
 ratio = 0.4                     # This figure should be very wide to span two columns
-fig_width = 14
+fig_width = 8.5
 fig_width = fig_width /2.54     # width in cm converted to inches
 fig_height = fig_width*ratio
 fig.set_size_inches(fig_width,fig_height)

### 2012-04-23 python_figures/ammonia_reactivity.py

@@ -94,7 +94,7 @@ fig = plt.figure()
 fig.subplots_adjust(bottom=0.15) # Make room for x-label
 fig.subplots_adjust(right=0.85) # Make room for x-label
 ratio = 0.7                     # This figure should be very wide to span two columns
-fig_width = 9
+fig_width = 8.5
 fig_width = fig_width /2.54     # width in cm converted to inches
 fig_height = fig_width*ratio
 fig.set_size_inches(fig_width,fig_height)

### 2012-04-23 python_figures/dynamic_range.py

@@ -24,7 +24,7 @@ fig.subplots_adjust(top=0.9) # Make room for extra x-label
 fig.subplots_adjust(wspace=0.25)
 fig.subplots_adjust(hspace=0.25)
 ratio = 0.6
-fig_width = 14
+fig_width = 8.5
 fig_width = fig_width /2.54     # width in cm converted to inches
 fig_height = fig_width*ratio
 fig.set_size_inches(fig_width,fig_height)

### 2012-04-23 python_figures/ammonia_OH_gauss_fit.py
Changed figure sizes

@@ -24,7 +24,7 @@ except:
 cursor = db.cursor()
 
 fig = plt.figure()
-fig.subplots_adjust(bottom=0.2) # Make room for x-label
+fig.subplots_adjust(bottom=0.22) # Make room for x-label
 fig.subplots_adjust(top=0.8) # Make room for extra x-label
 ratio = 0.4                     # This figure should be very wide to span two columns
 fig_width = 8.5
@@ -114,4 +114,4 @@ axis3.ticklabel_format(useOffset=False)
 
 #plt.tight_layout()
 #plt.show()
-plt.savefig('../ammonia_OH_gauss_fit.png',dpi=300)
+plt.savefig('../ammonia_OH_gauss_fit.png',dpi=600)

### 2012-04-23 python_figures/dynamic_range.py

@@ -19,7 +19,7 @@ except:
 cursor = db.cursor()
 
 fig = plt.figure()
-fig.subplots_adjust(bottom=0.1) # Make room for x-label
+fig.subplots_adjust(bottom=0.2) # Make room for x-label
 fig.subplots_adjust(top=0.9) # Make room for extra x-label
 fig.subplots_adjust(wspace=0.25)
 fig.subplots_adjust(hspace=0.25)
@@ -47,8 +47,8 @@ x_ticks.append([12.767,12.777,12.787])
 x_ticks.append([4.377,4.387,4.397])
 x_ticks.append([16.962,16.972,16.982])
 y_ticks.append([100,200,300,400])
-y_ticks.append([5,10,15,20])
-y_ticks.append([0.2,0.4,0.6,0.8])
+y_ticks.append([5,10,15])
+y_ticks.append([0.2,0.4,0.6])
 
 fit = []
 

### 2012-04-23 python_figures/tof_raw.py

@@ -41,7 +41,7 @@ arrow = dict(facecolor='black',arrowstyle='->')
 font = 8
 
 ratio = 0.4                     # This figure should be very wide to span two columns
-fig_width = 16
+fig_width = 17
 fig_width = fig_width /2.54     # width in cm converted to inches
 fig_height = fig_width*ratio
 fig.set_size_inches(fig_width,fig_height)

### 2012-04-24 python_figures/ammonia_OH_gauss_fit.py
Changed figure sizes and resolutions

@@ -25,7 +25,7 @@ cursor = db.cursor()
 
 fig = plt.figure()
 fig.subplots_adjust(bottom=0.22) # Make room for x-label
-fig.subplots_adjust(top=0.8) # Make room for extra x-label
+fig.subplots_adjust(top=0.79) # Make room for extra x-label
 ratio = 0.4                     # This figure should be very wide to span two columns
 fig_width = 8.5
 fig_width = fig_width /2.54     # width in cm converted to inches

### 2012-04-24 python_figures/ammonia_reactivity.py

@@ -133,4 +133,4 @@ axis2.tick_params(direction='in', length=6, width=1, colors='k',labelsize=8,axis
 
 #plt.tight_layout()
 plt.show()
-plt.savefig('../ammonia_reactivity.png',dpi=300)
+plt.savefig('../ammonia_reactivity.png',dpi=600)

### 2012-04-24 python_figures/dynamic_range.py

@@ -21,7 +21,7 @@ cursor = db.cursor()
 fig = plt.figure()
 fig.subplots_adjust(bottom=0.2) # Make room for x-label
 fig.subplots_adjust(top=0.9) # Make room for extra x-label
-fig.subplots_adjust(wspace=0.25)
+fig.subplots_adjust(wspace=0.4)
 fig.subplots_adjust(hspace=0.25)
 ratio = 0.6
 fig_width = 8.5
@@ -43,12 +43,15 @@ masses.append(['O$_2$',16.972,8])
 
 x_ticks = []
 y_ticks = []
-x_ticks.append([12.767,12.777,12.787])
-x_ticks.append([4.377,4.387,4.397])
-x_ticks.append([16.962,16.972,16.982])
-y_ticks.append([100,200,300,400])
-y_ticks.append([5,10,15])
-y_ticks.append([0.2,0.4,0.6])
+#x_ticks.append([12.767,12.777,12.787])
+#x_ticks.append([4.377,4.387,4.397])
+#x_ticks.append([16.962,16.972,16.982])
+x_ticks.append([12.767,12.787])
+x_ticks.append([4.377,4.397])
+x_ticks.append([16.962,16.982])
+y_ticks.append([0,100,200,300,400])
+y_ticks.append([0,5,10,15])
+y_ticks.append([0,0.2,0.4,0.6])
 
 fit = []
 
@@ -113,5 +116,5 @@ for mass in masses:
 
 #plt.tight_layout()
 #plt.show()
-plt.savefig('../dynamic_range.png',dpi=300)
+plt.savefig('../dynamic_range.png',dpi=600)
 

### 2012-04-24 python_figures/tof_raw.py

@@ -128,4 +128,4 @@ axis.annotate('NH$_3$', xy=(12.425, 85),  xycoords='data', xytext=(12.35, 130), 
 
 #plt.tight_layout()
 plt.show()
-plt.savefig('../untreated_data.png',dpi=300)
+plt.savefig('../untreated_data.png',dpi=600)

### 2012-04-24 paper.tex
Checked in Ibs corrections and fixed some figure-sizes
Final version to be submitted. Before adapting to rsi-guidelines

@@
 The QMS, however, suffers from a low mass resolution ($m/\Delta m\gtrsim m$ up to $m\sim200$) which makes analysis of complicated spectra difficult and cumbersome.
-The QMS is additionally subject to a mass dependent transmission (typically $\propto m^{-1}$ ) limiting general use.
 Furthermore, QMSs are typically operated by logging a single (or a few) masses as a function of time to increase time resolution.
@@
 \begin{figure}
- \includegraphics[width=14cm]{TOF_microreactor.png}%
+ \includegraphics[width=17cm]{TOF_microreactor.png}%
  \caption{Schematic of the total system (not to scale).
@@
 \begin{figure}
- \includegraphics[width=16cm]{trajectory.png}%
- \caption{Simulated trajectories of ions with initial position variations in the source region illustrating the focusing effect of the reflectron.
+ \includegraphics[width=8.5cm]{trajectory.png}%
+ \caption{Simulated trajectories of ions ($m/q=50$) with initial position variations in the source region illustrating the focusing effect of the reflectron.
 Red curve corresponds to ions with an initial position in the center of the source region while blue and green curves illustrate trajectories of ions with non-ideal initial positions displaced 6.3\,mm towards and further away from the repelling plate, respectively.
@@
 \begin{figure}
- \includegraphics[width=16cm]{untreated_data.png}%
+ \includegraphics[width=17cm]{untreated_data.png}%
  \caption{Raw data acquired from the TOF-MS during NH$_3$ oxidation by O$_2$ (NH$_3$:O$_2$ 4:3, 195\,$^{\circ}$C).
@@
 \begin{figure}
- \includegraphics[width=14cm]{ammonia_OH_gauss_fit.png}%
+ \includegraphics[width=8.5cm]{ammonia_OH_gauss_fit.png}%
  \caption{Example of two gaussian fits (dashed red lines) and the sum of the two fits (green solid line) to a double peak (blue dots) consisting of NH$_{3}$ and OH both at approximately 17\,amu demonstrating the resolution of the TOF-MS.
@@
 \begin{figure}
- \includegraphics[width=14cm]{dynamic_range.png}%
- \caption{Gaussian fits (red solid line) to three different mass to charge ratios (blue points) from the same mass spectrum (integrated area indicated in each panel).
-As seen from the response a high dynamic range of the TOF-MS is demonstrated by good gaussian fits to all peaks.
-The TOF-MS can hence be used to monitor both very small and very large signal masses.
-At the bottom panel the area normalized error for each fit shows that the relative fit error is independent of the total peak area.\label{fig:dynamic_range}}%
+ \includegraphics[width=8.5cm]{dynamic_range.png}%
+ \caption{Gaussian fits (red solid line) to three different mass to charge
+ ratios (blue points) from the same mass spectrum.
+In panels a), b) and c) the H$_2$O (peak area: 2.35\,mV$\cdot\mu$s), H$_2$ (peak area: $5.43\times10^{-2}$\,mV$\cdot\mu$s) and O$_2$ (peak area: $4.24\times10^{-3}$\,mV$\cdot\mu$s) signals are shown, respectively.
+As seen from the
+ response a high dynamic range of the TOF-MS is demonstrated by good gaussian
+ fits to all peaks. The TOF-MS can hence be used to monitor both very small and
+ very large signal masses. At the bottom panel the area normalized error for
+ each fit shows that the relative fit error is independent of the total peak
+ area.\label{fig:dynamic_range}}%
+
 \end{figure}
@@
 \begin{figure}
- \includegraphics[width=14cm]{model_error.png}%
+ \includegraphics[width=8.5cm]{model_error.png}%
  \caption{Comparison of the simulated model (red curve, top panel) to actual measured experimental values (blue dots) of flight time as a function of mass.
@@
 \begin{figure}
- \includegraphics[width=14cm]{ammonia_reactivity.png}%
+ \includegraphics[width=8.5cm]{ammonia_reactivity.png}%
  \caption{Ammonia oxidation as a function of temperature on a 1\,\% geometrical coverage Pt thin film.

### 2012-04-24 python_figures/ammonia_OH_gauss_fit.py

@@ -88,7 +88,6 @@ for mass in masses:
 axis.plot(X_range,fit[0]+fit[1],'g-',linewidth=0.5)
 axis.plot(X_values,Y_values,'b.',markersize=1.5)
 axis.tick_params(direction='in', length=2, width=1, colors='k',labelsize=8,axis='both',pad=3)
-axis.set_yticks((20,40,60))    
 axis.set_xticks((12.41,12.42,12.43,12.44))    
 axis.ticklabel_format(useOffset=False)
 axis.set_xlim(12.405,12.435)
@@ -111,6 +110,8 @@ axis3.set_xlabel('Mass / amu', fontsize=8)
 axis3.tick_params(direction='in', length=2, width=1, colors='k',labelsize=8,axis='both',pad=3)
 axis3.ticklabel_format(useOffset=False)
 
+axis.set_yticks((25,50,75,100,125))    
+#axis3.set_yticks((20,40,60))    
 
 #plt.tight_layout()
 #plt.show()

### 2012-04-24 python_figures/ammonia_reactivity.py

@@ -107,7 +107,7 @@ for mass in config.masses:
     i = i + 1
 
 axis.set_xlabel('Time / min.', fontsize=8)
-axis.set_ylabel('Response / mV$\cdot$s', fontsize=8)
+axis.set_ylabel('Response / mV$\cdot\mu$s', fontsize=8)
 
 
 axis.set_yticks((0.5,1,1.5,2,2.5,3,3.5))

### 2012-04-24 python_figures/dynamic_range.py

@@ -37,9 +37,9 @@ cursor.execute("SELECT x*1000000,y*1000 FROM xy_values_tof where measurement = 2
 Data = np.array(cursor.fetchall())
 
 masses = []
-masses.append(['H$_2$O',12.777,8])
-masses.append(['H$_2$',4.387,8])
-masses.append(['O$_2$',16.972,8])
+masses.append(['H$_2$O',12.777,8,'a)'])
+masses.append(['H$_2$',4.387,8,'b)'])
+masses.append(['O$_2$',16.972,8,'c)'])
 
 x_ticks = []
 y_ticks = []
@@ -93,8 +93,10 @@ for mass in masses:
     axis.set_xticks([])
     axis.set_yticks(y_ticks[i-1])
     axis.set_xlim(mass[1]-0.013,mass[1]+0.013)
-    axis.annotate(mass[0], (0.13,0.9),xycoords='axes fraction',fontsize=8)
-    axis.annotate(str(round(signal,3)), (0.13,0.8),xycoords='axes fraction',fontsize=8)
+    #axis.annotate(mass[0], (0.13,0.9),xycoords='axes fraction',fontsize=8)
+    axis.annotate(mass[3], (0.13,0.9),xycoords='axes fraction',fontsize=8)
+    #axis.annotate(str(round(signal,3)), (0.13,0.8),xycoords='axes fraction',fontsize=8)
+    print signal
     if i==1:
         axis.set_ylabel('Response / mV', fontsize=8)    
 
@@ -107,7 +109,7 @@ for mass in masses:
     axis.set_yticks([-15,0,15,30])
     axis.set_xlim(mass[1]-0.013,mass[1]+0.013)
     if i==1:
-        axis.set_ylabel('Normalized Error', fontsize=8)    
+        axis.set_ylabel('Norm. Error', fontsize=8)    
     if i==2:
         axis.set_xlabel('Flight Time / $\mu$s', fontsize=8)    
     axis.tick_params(direction='in', length=2, width=1, colors='k',labelsize=8,axis='both',pad=3)

### 2012-04-24 paper.tex
Final version submitted to RSI

@@
 \usepackage{amssymb}
-%\documentclass[aip,reprint]{revtex4-1}
-
-%\draft % marks overfull lines with a black rule on the right
 
@@
 
-% Use the \preprint command to place your local institutional report number 
-% on the title page in preprint mode.
-% Multiple \preprint commands are allowed.
-%\preprint{}
-
-\title{High Mass Resolution Time of Flight Mass Spectrometer for Measuring Products in Heterogeneous Catalysis in Highly Sensitive Microreactors} %Title of paper
-
-% repeat the \author .. \affiliation  etc. as needed
-% \email, \thanks, \homepage, \altaffiliation all apply to the current author.
-% Explanatory text should go in the []'s, 
-% actual e-mail address or url should go in the {}'s for \email and \homepage.
-% Please use the appropriate macro for the type of information
-
-% \affiliation command applies to all authors since the last \affiliation command. 
-% The \affiliation command should follow the other information.
+\title{High Mass Resolution Time of Flight Mass Spectrometer for Measuring Products in Heterogeneous Catalysis in Highly Sensitive Microreactors}
 
@@
 Lyngby, Denmark}
-%\homepage[]{Your web page}
-%\thanks{}
-%\altaffiliation{}
-%\affiliation{}
-
-% Collaboration name, if desired (requires use of superscriptaddress option in \documentclass). 
-% \noaffiliation is required (may also be used with the \author command).
-%\collaboration{}
-%\noaffiliation
 
@@
 
-\maketitle %\maketitle must follow title, authors, abstract and \pacs
+\maketitle
 
-% Body of paper goes here. Use proper sectioning commands. 
-% References should be done using the \cite, \ref, and \label commands
 \section{Introduction}
@@
 \begin{figure}
- \includegraphics[width=17cm]{TOF_microreactor.png}%
+ \includegraphics[width=17cm]{TOF_microreactor.eps}
  \caption{Schematic of the total system (not to scale).
@@
 Ions are separated in the field free region and focused by the reflectron.
-The ions are subsequently detected by the MCP.\label{fig:TOF_microreactor}}%
+The ions are subsequently detected by the MCP.\label{fig:TOF_microreactor}}
 \end{figure}
@@
 \begin{figure}
- \includegraphics[width=8.5cm]{trajectory.png}%
+ \includegraphics[width=8.5cm]{trajectory.eps}%
  \caption{Simulated trajectories of ions ($m/q=50$) with initial position variations in the source region illustrating the focusing effect of the reflectron.
@@
 \begin{figure}
- \includegraphics[width=17cm]{untreated_data.png}%
+ \includegraphics[width=17cm]{untreated_data.eps}%
  \caption{Raw data acquired from the TOF-MS during NH$_3$ oxidation by O$_2$ (NH$_3$:O$_2$ 4:3, 195\,$^{\circ}$C).
@@
 \begin{figure}
- \includegraphics[width=8.5cm]{ammonia_OH_gauss_fit.png}%
+ \includegraphics[width=8.5cm]{ammonia_OH_gauss_fit.eps}%
  \caption{Example of two gaussian fits (dashed red lines) and the sum of the two fits (green solid line) to a double peak (blue dots) consisting of NH$_{3}$ and OH both at approximately 17\,amu demonstrating the resolution of the TOF-MS.
@@
 \begin{figure}
- \includegraphics[width=8.5cm]{dynamic_range.png}%
+ \includegraphics[width=8.5cm]{dynamic_range.eps}
  \caption{Gaussian fits (red solid line) to three different mass to charge
@@
  each fit shows that the relative fit error is independent of the total peak
- area.\label{fig:dynamic_range}}%
+ area.\label{fig:dynamic_range}}
 
@@
 \begin{figure}
- \includegraphics[width=8.5cm]{model_error.png}%
+ \includegraphics[width=8.5cm]{model_error.eps}
  \caption{Comparison of the simulated model (red curve, top panel) to actual measured experimental values (blue dots) of flight time as a function of mass.
@@
 Error bars represents only the uncertainty in the experimental data.
-As seen from the lower panels a deviation of $\sim$10\,ns corresponding to $\sim$50\,milli-amu at 70\,amu is present.\label{fig:model_error}}%
+As seen from the lower panels a deviation of $\sim$10\,ns corresponding to $\sim$50\,milli-amu at 70\,amu is present.\label{fig:model_error}}
 \end{figure}
@@
 \begin{figure}
- \includegraphics[width=8.5cm]{ammonia_reactivity.png}%
+ \includegraphics[width=8.5cm]{ammonia_reactivity.eps}
  \caption{Ammonia oxidation as a function of temperature on a 1\,\% geometrical coverage Pt thin film.
 As the temperature is increased ammonia is oxidized to H$_2$O and N$_2$.
-Furthermore, the OH and NH$_3$ signals are anticorrelated demonstrating the ability to resolve these two close lying masses as shown in Figure~\ref{fig:gaussian_fit}.\label{fig:ammonia_reactivity}}%
+Furthermore, the OH and NH$_3$ signals are anticorrelated demonstrating the ability to resolve these two close lying masses as shown in Figure~\ref{fig:gaussian_fit}.\label{fig:ammonia_reactivity}}
 \end{figure}
@@
 
-% If in two-column mode, this environment will change to single-column format so that long equations can be displayed. 
-% Use only when necessary.
-%\begin{widetext}
-%$$\mbox{put long equation here}$$
-%\end{widetext}
+\bibliographystyle{unsrt}
 
-% Figures should be put into the text as floats. 
-% Use the graphics or graphicx packages (distributed with LaTeX2e).
-% See the LaTeX Graphics Companion by Michel Goosens, Sebastian Rahtz, and Frank Mittelbach for examples. 
-%
-% Here is an example of the general form of a figure:
-% Fill in the caption in the braces of the \caption{} command. 
-% Put the label that you will use with \ref{} command in the braces of the \label{} command.
-%
-% \begin{figure}
-% \includegraphics{}%
-% \caption{\label{}}%
-% \end{figure}
+\begin{thebibliography}{10}
 
-% Tables may be be put in the text as floats.
-% Here is an example of the general form of a table:
-% Fill in the caption in the braces of the \caption{} command. Put the label
-% that you will use with \ref{} command in the braces of the \label{} command.
-% Insert the column specifiers (l, r, c, d, etc.) in the empty braces of the
-% \begin{tabular}{} command.
-%
-% \begin{table}
-% \caption{\label{} }
-% \begin{tabular}{}
-% \end{tabular}
-% \end{table}
+\bibitem{Jensen2001}
+K.F. Jensen.
+\newblock Microreaction engineering -- is small better?
+\newblock {\em Chemical Engineering Science}, 56(2):293--303, January 2001.
 
-% If you have acknowledgments, this puts in the proper section head.
-%\begin{acknowledgments}
-% Put your acknowledgments here.
-%\end{acknowledgments}
+\bibitem{Jaehnisch2004}
+K.~J\"{a}hnisch, V.~Hessel, H.~L\"{o}we, and M.~Baerns.
+\newblock Chemistry in microstructured reactors.
+\newblock {\em Angewandte Chemie International Edition}, 43(4):406--446, 2004.
 
-% Create the reference section using BibTeX:
-%\bibliographystyle{abbrv}
-%\bibliographystyle{alpha}
-%\bibliographystyle{plain}
-\bibliographystyle{unsrt}
-\bibliography{literature}
+\bibitem{Henriksen2009}
+T.R. Henriksen, J.L. Olsen, P.~Vesborg, I.~Chorkendorff, and O.~Hansen.
+\newblock Highly sensitive silicon microreactor for catalyst testing.
+\newblock {\em Review of Scientific Instruments}, 80(12):124101, December 2009.
+
+\bibitem{Benninghoven1994}
+A.~Benninghoven.
+\newblock Chemical-analysis of inorganic and organic-surfaces and thin-films by
+  static time-of-flight secondary-ion mass-spectrometry ({TOF}-{SIMS}).
+\newblock {\em Angewandte Chemie-international Edition In English},
+  33(10):1023--1043, June 1994.
+
+\bibitem{DeSmet1998}
+F.~De~Smet, M.~Devillers, C.~Poleunis, and P.~Bertrand.
+\newblock Time-of-flight sims study of heterogeneous catalysts based on
+  praseodymium and molybdenum oxides.
+\newblock {\em Journal of the Chemical Society-faraday Transactions},
+  94(7):941--947, April 1998.
+
+\bibitem{Grams2004}
+J.~Grams, J.~Goralski, and T.~Paryjczak.
+\newblock High resolution surface imaging of {C}o/{Z}r{O}$_2$ catalyst by
+  {TOF}-{SIMS}.
+\newblock {\em Surface Science}, 549(1):L21--L26, January 2004.
+
+\bibitem{Johnson2010}
+G.~E. Johnson, M.~Lysonski, and J.~Laskin.
+\newblock In situ reactivity and tof-sims analysis of surfaces prepared by soft
+  and reactive landing of mass-selected ions.
+\newblock {\em Analytical Chemistry}, 82(13):5718--5727, July 2010.
+
+\bibitem{Levy1963}
+E.J. Levy, E.D. Miller, and W.S. Beggs.
+\newblock Application of time of flight mass spectrometry and gas
+  chromatography to reaction studies.
+\newblock {\em Analytical Chemistry}, 35(8):946--949, 1963.
+
+\bibitem{Okumura2007}
+K.~Okumura, Y.~Sakamoto, T.~Kayama, Y.~Kizaki, H.~Shinjoh, and T.~Motohiro.
+\newblock Quantitative analysis of transient surface reactions on planar
+  catalyst with time-resolved time-of-flight mass spectrometry.
+\newblock {\em Review of Scientific Instruments}, 78(10):104102, October 2007.
+
+\bibitem{Vesborg2010}
+P.C.K. Vesborg, J.L. Olsen, T.R. Henriksen, I.~Chorkendorff, and O.~Hansen.
+\newblock Gas-phase photocatalysis in mu-reactors.
+\newblock {\em Chemical Engineering Journal}, 160(2):738--741, June 2010.
+
+\bibitem{JordanHomepage}
+\url{http://www.rmjordan.com/OrthogoTOF/orthogotof.html}.
+
+\bibitem{Nottingham1955}
+W.B. Nottingham.
+\newblock {\em Vacuum Symposium Transactions}.
+\newblock Committee on Vacuum Techniques, Bostion, 1955.
+
+\bibitem{ModelGithub}
+\url{https://github.com/robertjensen/FlightTime}.
+
+\bibitem{Imbihl2007}
+R.~Imbihl, A.~Scheibe, Y.F. Zeng, S.~Gunther, R.~Kraehnert, V.A. Kondratenko,
+  M.~Baerns, W.K. Offermans, A.P.J. Jansen, and R.A. van Santen.
+\newblock Catalytic ammonia oxidation on platinum: mechanism and catalyst
+  restructuring at high and low pressure.
+\newblock {\em Phys. Chem. Chem. Phys.}, 9(27):3522--3540, 2007.
+
+\bibitem{Zeng2009}
+Y.F. Zeng and R.~Imbihl.
+\newblock Structure sensitivity of ammonia oxidation over platinum.
+\newblock {\em Journal of Catalysis}, 261(2):129--136, January 2009.
+
+\end{thebibliography}
 

### 2012-04-24 python_figures/ammonia_OH_gauss_fit.py

@@ -115,4 +115,4 @@ axis.set_yticks((25,50,75,100,125))
 
 #plt.tight_layout()
 #plt.show()
-plt.savefig('../ammonia_OH_gauss_fit.png',dpi=600)
+plt.savefig('../ammonia_OH_gauss_fit.eps',dpi=600)

### 2012-04-24 python_figures/ammonia_reactivity.py

@@ -133,4 +133,4 @@ axis2.tick_params(direction='in', length=6, width=1, colors='k',labelsize=8,axis
 
 #plt.tight_layout()
 plt.show()
-plt.savefig('../ammonia_reactivity.png',dpi=600)
+plt.savefig('../ammonia_reactivity.eps',dpi=600)

### 2012-04-24 python_figures/dynamic_range.py

@@ -118,5 +118,5 @@ for mass in masses:
 
 #plt.tight_layout()
 #plt.show()
-plt.savefig('../dynamic_range.png',dpi=600)
+plt.savefig('../dynamic_range.eps',dpi=600)
 

### 2012-04-24 python_figures/tof_raw.py

@@ -128,4 +128,4 @@ axis.annotate('NH$_3$', xy=(12.425, 85),  xycoords='data', xytext=(12.35, 130), 
 
 #plt.tight_layout()
 plt.show()
-plt.savefig('../untreated_data.png',dpi=600)
+plt.savefig('../untreated_data.eps',dpi=600)
